---
title: "NKC(S)"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_knit$set(root.dir = "~/OneDrive - Universitaet Bern/NKC_project/R_scripts/") # set directory
```

### Set up workspace
```{r libraries}
rm (list = ls())

library(ggplot2) # for plotting
library(gtools) # permutations to get all possible genotype combinations
library(dplyr) # for constructing the data sets
library(gghalves) # for plotting mixed boxplots with points

```

### The NKC(S) model
code for NK model based on explanations from Welch & Waxman (2005) and supported by python code from Maciej Workiewicz (https://github.com/Mac13kW/NK_model)
the NK model was introduced by Kauffman & Weinberger (1989) and the NKC(S) model was introduced by Kauffman & Johnson (1991)

## 1) Variable explanations
n = nb. of haploid loci
a = nb. of possible alleles per locus
k = nb. of loci that epistatically influence a given focal locus; k <= n-1
s = nb. of species that are linked through intergenomic epistasis
s_tot = total nb. of species in the system
c = nb. of loci in each of s species epistatically influencing a given focal locus
W = fitness
h = fitness contributions of each locus
IM = interaction matrix; determines how the loci are linked epistatically

(for now we will assume full symmetry; i.e. all species have the same n, a, k, s, c, and h)

## 2) Interaction matrix (IM)
the fitness contribution of a locus i depends on the allelic value itself (position i) and the allelic values at k other loci; the interaction matrix defines *which* loci are epistatically connected
here I define functions for different types of interaction matrices

# 2.1) random matrix
any locus can be influenced by any locus - interactions are not necessarily reciprocal

```{r random interaction matrix}
IM_random <- function(n, k){
  
  if (n == 2 & k == 1){
    
    IM_random <- matrix(n, n, data = rep(1, n^2))
    
  } else {
  
  IM_random <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_random[row(IM_random) == col(IM_random)] <- 1 # fitness value at locus i always depends on allele at locus i itself for within species genetic interactions
  
  for (i in 1:n) { # for each row we assign random indices that we assign as interacting loci
    
    interacting_loci <- sample(c(1:nrow(IM_random))[-i], k) # draw random non-diagonal loci that epistatically interact with locus i
    IM_random[i, interacting_loci] <- 1
    
  }
  
  }
  
  return(IM_random)
  
}

IM_random_c <- function(n, c){
  
  IM_random <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

  for (i in 1:n) { # for each row we assign random indices that we assign as interacting loci
    
    interacting_loci <- sample(c(1:nrow(IM_random)), c) # draw random loci that epistatically interact with locus i
    IM_random[i, interacting_loci] <- 1
    
  }
  
  return(IM_random)
  
}
```

# 2.2) modular matrix
epistatic connections are arranged in blocks of k+1 reciprocally interacting loci ("block-diagonal" matrix);
n needs to be divisible by k+1

```{r modular interaction matrix}
IM_modular <- function(n, k){
  
  if (n%%(k+1) != 0){
    
    print("n needs to be divisible by k+1") # prints message if genome string cannot be divided into equal blocks
    
  }
  
  else{
  
  IM_modular <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  
  i <- 1
  while (i <= n) {# we assign blocks of interacting loci
    
    IM_modular[i:(i+k), i:(i+k)] <- 1
    
    i <- i+k+1
    
  }
  
  return(IM_modular)
  
  }
  
}

IM_modular_c <- function(n, c){
  
  if (n%%(c) != 0){
    
    print("n needs to be divisible by c") # prints message if genome string cannot be divided into equal blocks
    
  }
  
  else{
  
  IM_modular <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  
  i <- 1
  while (i <= n) {# we assign blocks of interacting loci
    
    IM_modular[i:(i+c-1), i:(i+c-1)] <- 1
    
    i <- i+c
    
  }
  
  return(IM_modular)
  
  }
  
}
```

# 2.3) Nearest neighbour 
the genome is circular and each locus reciprocally interacts with its k neighbours ("local" interactions); 
k needs to be divisible by 2 for symmetry reasons -> interactions with k/2 neighbours to either side

```{r nearest neighbour interaction matrix}
IM_neighbour <- function(n, k){
  
  if (k%%(2) != 0){
    
    print("k needs to be divisible by 2") # prints message
    
  }
  
  else{
    
    IM_neighbour <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

    for (i in 1:n){ # assign neighbours in each row (= i +/- k/2)
      
     if (i-k/2 < 1) { # to avoid going out of bounds (negative indeces)
       
       out_bounds <- 1 - (i-k/2) # these are the loci that "wrap around" in the circular genome
       
       IM_neighbour[i, i:(i+k/2)] <- 1 # normal assignment of "downstream" loci 
       IM_neighbour[i, (i-k/2+out_bounds):i] <- 1
       IM_neighbour[i, (n-out_bounds+1):n] <- 1 
       
     }
      
      else if (i+k/2 > n) { # to avoid going out of bounds (indeces exceeding n)
        
        out_bounds <- (i+k/2) - n # these are the loci that "wrap around" in the circular genome
       
        IM_neighbour[i, (i-k/2):i] <- 1 # normal assignment of "upstream" loci 
        IM_neighbour[i, i:(i+k/2-out_bounds)] <- 1
        IM_neighbour[i, 1:out_bounds] <- 1
       
      }
      
      else {
        
        IM_neighbour[i, (i-k/2):(i+k/2)] <- 1
        
      }
      
    }
    
    return(IM_neighbour)
    
  }
  
}
```

# 2.4) Preferential attachment (Rivkin & Siggelkow, 2007)
loci that already have many interactions are more likely to add a further interaction than loci that have few interactions; total of n*k interactions among loci

```{r preferential interaction matrix}
IM_preferential <- function(n, k){
  
  IM_preferential <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_preferential[row(IM_preferential) == col(IM_preferential)] <- 1 # fitness value at locus i always depends on allele at locus i itself
  
  while (sum(IM_preferential) < n*(k+1)) {
    
    # pick a random row
    row <- sample(n ,1)
    
    # pick a column (weighted by how many '1's the column already contains)
    column <- sample(n, 1, prob = colSums(IM_preferential))
    
    IM_preferential[row, column] <- 1
    
    
  }
  
  return(IM_preferential)
  
}

IM_preferential_c <- function(n, c){
  
  IM_preferential <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

  while (sum(IM_preferential) < n*c) {
    
    # pick a random row
    row <- sample(n ,1)
    
    # pick a column (weighted by how many '1's the column already contains)
    column <- sample(n, 1, prob = colSums(IM_preferential))
    
    IM_preferential[row, column] <- 1
    
    
  }
  
  return(IM_preferential)
  
}
  
```

# 2.5) Hierarchical (Rivkin & Siggelkow, 2007)
few loci influence all other loci; the matrix consists of '1's below the diagonal, starting with the ﬁrst column, continuing with the second column, etc., until there are n*k interactions among loci

```{r hierarchical interaction matrix}
IM_hierarchical <- function(n, k){
  
  IM_hierarchical <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_hierarchical[row(IM_hierarchical) == col(IM_hierarchical)] <- 1 # fitness value at locus i always depends on allele at locus i itself
    
    for (i in 1:n){# for each column
      
      for (j in 1:n){# for each row
        
        if (sum(IM_hierarchical) < n*(k+1) & j>i) { # below the diagonal until we get to n*k interactions among loci
          
          IM_hierarchical[j,i] <- 1
        
      }
      
    }
    
  }
  
  return(IM_hierarchical)
  
}

IM_hierarchical_c <- function(n, c){
  
  IM_hierarchical <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

    for (i in 1:n){# for each column
      
      for (j in 1:n){# for each row
        
        if (sum(IM_hierarchical) < n*c & j>=i) { # below and including the diagonal until we get to n*c interactions among loci
          
          IM_hierarchical[j,i] <- 1
        
      }
      
    }
    
  }
  
  return(IM_hierarchical)
  
}

```

# 2.6) Dependent (Rivkin & Siggelkow, 2007)
few loci are dependent on all other loci

```{r dependent interaction matrix}
IM_dependent <- function(n, k){
  
  IM_dependent <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_dependent[row(IM_dependent) == col(IM_dependent)] <- 1 # fitness value at locus i always depends on allele at locus i itself
  
for (i in n:1){# for each row
      
      for (j in n:1){# for each column
        
        if (sum(IM_dependent) < n*(k+1) & i>j) { # below the diagonal until we get to n*k interactions among loci
          
          IM_dependent[i,j] <- 1
        
      }
      
    }
    
  }
  
  
  return(IM_dependent)
  
}

IM_dependent_c <- function(n, c){
  
  IM_dependent <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

for (i in n:1){# for each row
      
      for (j in n:1){# for each column
        
        if (sum(IM_dependent) < n*c & i>=j) { # below and including the diagonal until we get to n*c interactions among loci
          
          IM_dependent[i,j] <- 1
        
      }
      
    }
    
  }
  
  
  return(IM_dependent)
  
}

```

## 3) Creating the landscape
# 3.1) generate genotypes
generate all possible genotypes; alleles are encoded by numbers (1, 2, ..., a)

```{r generate genotypes}
generate_genotypes <- function(a, n){
  
  genotypes <- gtools::permutations(a, n, c(1:a), repeats = TRUE)
  return(genotypes)
  
}
```

# 3.2) generate fitness contributions
a^(k+1+c*s) different allele combinations per locus for each locus

```{r draw fitness contributions}

# Welch & Waxman drew from a normal distribution
generate_alleles <- function(n, k, a, c, s, fit_mean, fit_sd){
  
  allelic_vals <- matrix(c(rnorm(n*a^(k+1+c*s), fit_mean, fit_sd)), ncol = n) 
  return(allelic_vals)
  
}

# Kauffman drew from a uniform distribution
generate_alleles_unif <- function(n, k, a, c, s, fit_min, fit_max){
  
  allelic_vals <- matrix(c(runif(n*a^(k+1+c*s), fit_min, fit_max)), ncol = n)
  return(allelic_vals)
  
}
```

# 3.3) Calculate the genotype fitness
```{r calculate genotype fitness}

# fitness calaculation like Kauffman & Weinberger (1989) and Kauffman & Johnson (1991)
fitness_calc <- function(gene_vector){
  
  W = (1/length(gene_vector))*sum(gene_vector) 
  return(W)
  
}

# Welch & Waxman used a multiplicative model of fitness (ln fitness)
fitness_calc_mult <- function(gene_vector){
  
  W = exp(sum(gene_vector))
  return(W)
  
}

```

# 3.4) Generate intergenomic interaction matrices
```{r IM_c}

build_IMc <- function(IM = c("R", "M", "P", "H", "D"),
                      n,
                      c,
                      s,
                      s_tot){
  
  # determine how to construct the intergenomic epistatic interactions and what kind of interaction matrix (IM) to use 
  if (IM == "R"){# for Random matrix
    
    matrix_c <- IM_random_c
     
  } else if (IM == "M"){# for Modular matrix
    
    matrix_c <- IM_modular_c
    
  } else if (IM == "N"){# for nearest neighbour matrix
    
    matrix_c <- IM_neighbour_c
    
  } else if (IM == "P"){# for preferential interaction matrix
    
    matrix_c <- IM_preferential_c
    
  } else if (IM == "H"){# for hierarchical interaction matrix
    
    matrix_c <- IM_hierarchical_c
    
  } else if (IM == "D"){# for dependent interaction matrix
    
    matrix_c <- IM_dependent_c
    
  }
  
  matrix_c_species <- list()
  
  # for each species in the system
  for (i in 1:s_tot){
    
    # I need IM to describe the interaction between a focal species and each of its interaction partners
    matrix_temp <- list() # I collect this in a temporary list
    
    # so, for each interaction partner:
    for (j in 1:s){
      
      # generation intergenomic interaction matrix
      matrix_temp[[j]] <- matrix_c(n,c)
      
    }
    
    matrix_merged <- do.call(cbind, matrix_temp) # merge all IM by column (rows = loci in focal genome and then columns = all the loci in all the interacting species)
     matrix_c_species[[i]] <- matrix_merged
    
  }
  
  return(matrix_c_species)
  
}

```

# 3.4) Generate intragenomic interaction matrices
```{r IM_k}

build_IMk <- function(IM = c("R", "M", "N", "P", "H", "D"),
                      n,
                      k,
                      s,
                      s_tot){

  # determine how to construct the intragenomic epistatic interactions and what kind of interaction matrix (IM) to use 
  if (IM == "R"){# for Random matrix
    
    matrix_k <- IM_random
     
  } else if (IM == "M"){# for Modular matrix
    
    matrix_k <- IM_modular
    
  } else if (IM == "N"){# for nearest neighbour matrix
    
    matrix_k <- IM_neighbour
    
  } else if (IM == "P"){# for preferential interaction matrix
    
    matrix_k <- IM_preferential
    
  } else if (IM == "H"){# for hierarchical interaction matrix
    
    matrix_k <- IM_hierarchical
    
  } else if (IM == "D"){# for dependent interaction matrix
    
    matrix_k <- IM_dependent
    
  }
  
  matrix_k_species <- list()
  
  # for each species in the system
  for (i in 1:s_tot){
    
      # generation intragenomic interaction matrix
      matrix_k_species[[i]] <- matrix_k(n,k)

  }
  
  return(matrix_k_species)

}


```

# 3.5) Generate NKC(S) landscape
```{r generate landscape}
build_landscape <- function(IM_k, # intragenomic epistasis matrices
                            IM_c, # intergenomic epistasis matrices
                            fitness_contrib = c("N", "U"), # way to draw fitness contributions (normal vs. uniform distribution)
                            fitness_calculation = c("KJ", "WW"), # way to calculate fitness (according to Kauffman & Johnson or Welch & Waxman) 
                            n, # nb of loci
                            k, # nb of interacting loci within a species
                            a, # nb of alleles per locus
                            c, # nb of interacting loci between species
                            s, # nb of species interacting
                            s_tot, # total number of species in the species
                            fit_mean, # mean of fintess distribution when drawing from a normal distribution, or min fitness when drawing from a uniform distribution
                            fit_sd) # sd of fintess distribution when drawing from a normal distribution, or max fitness when drawing from a uniform distribution
  {
  

  # how to generate allelic values? (normal distribution vs uniform distribution)
  if (fitness_contrib == "N"){# for drawing from a normal distribution
    
    alleles_generate <- generate_alleles
    
  } else if (fitness_contrib == "U") {
    
    alleles_generate <- generate_alleles_unif
    
  }
  
  # how to calculate fitness?
  if (fitness_calculation == "KJ"){
    
    fitness_calculate <- fitness_calc 
    
  } else if (fitness_calculation == "WW"){
    
    fitness_calculate <- fitness_calc_mult 
    
  }
  
  # generate all possible genotypes (this is the same for all species here, since we assume that all species have the same n, a and c)
  genotypes <- generate_genotypes(a,n+(s*n)) # I generate "extended genotypes" to include the s*n sites in other species that are relevant for calculating fitness (but only n sites actually contribute to a genotype's fitness, if that makes sense?)
  
  # generate all possible fitness contributions depending on k epistatic interactions within species and c epistatic interactions with s other species
  h_table_species <- list() # a list with all look up tables for each of the s_tot species; each list item is a look-up table of dimension n x a^(k+1+c*s) for all possible allelic values
  
  # for each species:
  for (i in 1:s_tot){
    
    # generate look-up table with all possible allelic values (dependent on k+1+c*s loci within and between species); dimension n x a^(k+1+c*s) for all possible allelic values
    # each column = 1 locus, each row = different genetic background
    h_table_species[[i]] <- alleles_generate(n, k, a, c, s, fit_mean, fit_sd)
    
  }
  
  # now that we generated all the fitness contributions and know all the genetic interactions in the system
  
  # keeping track of "extended" genotypes, their fitness contributions and total calculated fitness
  genotype_table_species <- list()
  
  # for each species:
  for (i in 1:s_tot){
    
    # table to keep track of all fitness vectors
    fitnesses <- NULL
    
    # for each genotype (remember, all species have the same genotype encoding; it's just the fitness values and epistatic interactions that differ)
    for (j in 1:nrow(genotypes)){
      
      # keep track of fitness contribution at each locus (h)
      h_vector <- NULL # vector of fitness contributions per locus for each genotype
      
      # for each genotype we look up the fitness contribution (h) at each locus; h depends on k+1+c*s loci 
      # for each locus:
      for (l in 1:n) { # skipping "k" to iterate over, since k is used as a variable
        
        # which loci determine the fitness contribution at this locus?
        interesting_loci_k <- which(IM_k[[i]][l, ] != 0) # based on the intragenomic IM
        interesting_loci_c <- which(IM_c[[i]][l,] != 0) # based on intergenomic IM
        
        interesting_loci <- c(interesting_loci_k, interesting_loci_c+n) # list of all loci that have an affect on the fitness contribution

        # what are the alleles present at the loci we're interested in for this given genotype?
        alleles <- genotypes[j, interesting_loci]
        
        # let's access the fitness contributions associated with the genetic background
        index <- 1
      
        # for all loci contributing to h:
        for (m in 1:(k+1+(s*c))) {
        
        index <- index + (a^((k+1+(s*c))-m))*(alleles[m]-1)
        
        }
      
        # store the fitness contributions in a vector
        h_vector <- cbind(h_vector, h_table_species[[i]][index,l])
      
      }
      
      # construct a table with all information relating to the fitness contributions etc.
      fitness_genotype <- cbind(h_vector, fitness_calculate(h_vector)) # calculate the total fitness (W) for each genotype
      fitnesses <- rbind(fitnesses, fitness_genotype) # compilation of individual fitness contributions (h) and calculated fitness values (W)
      
    }
    
    # combine the genotype table and the fitness table
    genotype_table_species[[i]] <- cbind(genotypes, fitnesses) # combining the genotype table and the fitness table
    # columns 1 to n represent the allelic values at each locus in the genome of the focal species
    # columns n+1 to n+(s*n) represent the allelic values at each locus in the genomes of the interacting species (= intergenomic epistasis)
    # columns n+(s*n)+1 to 2n+(s*n) are the fitness contributions per locus (h) for loci in the genome of the focal species
    # column 2n+(s*n)+1 is the calculated total fitness for each genotype taking into account all genetic interactions
    
    # store as data frame for ease of proceeding
    genotype_table_species[[i]] <- as.data.frame(genotype_table_species[[i]])
    colnames(genotype_table_species[[i]])[1:n] <- paste0("F.", 1:n) # loci of focal species ("F")
    colnames(genotype_table_species[[i]])[(n+1):(n+(s*n))] <- paste0("P.", 1:(s*n)) # loci of partner species ("P")
    colnames(genotype_table_species[[i]])[(n+(s*n)+1):(2*n+(s*n))] <- paste0("h.", 1:n) # fitness contributions of each locus
    colnames(genotype_table_species[[i]])[2*n+(s*n)+1] <- "fitness"
    
  }
  
  return(genotype_table_species)

}

```

## 4) Exploring the landscape topology
# 4.1) Find neighbors one step away
This will include mutations that can happen within a focal species genome but also mutations that can happen in the genome of one of the interacting species

```{r neighbour search}

findNeighbours <- function(landscape, 
                           startIndex,
                           nb_loci){ # focal genotype to start neighbour search with
  
  # focal genotype
  temp_genotype <- landscape[startIndex,]
  
  differences <- c(rep(0, length(landscape[,1]))) # vector with entries for each genotype to keep track of difference to reference
    
  for (i in 1:nb_loci){
    
    for (j in 1:length(landscape[,1])){
      
      if (landscape[j,i] != temp_genotype[i]){ # if both genotypes don't carry the same allele...
        
        differences[j] <- differences[j] + 1 # ... I mark a difference in my vector
        
      }
      
    }
    
  }
  
  neighbours <- landscape[which(differences == 1), ]
  
  return(neighbours)
  
}
```

# 4.2) visualise the landscape

```{r landscape visualisation}
visual_landscape <- function(landscape, n, c, s) {
  
  landscape_df <- data.frame(landscape)
  landscape_df$genotypeID <- c(1:(length(landscape[,1]))) # assign ID to each genotype
  
  # count the nb. of mutations separating each genotype from the reference
  landscape_df$mutations <- 0
  
  for (i in 1:length(landscape_df[,1])) {
    
    landscape_df$seq[i] <- paste(paste(landscape_df[i, 1:n], collapse = ""), "-", c(paste(landscape_df[i, (n+1):(n+s*n)], collapse = ""))) # alternate way of representing the genotypes; this is purely visual information to plot

    for (locus in 1:(n+s*n)) {
      
      if (landscape_df[i,locus] != 1) {
        
        landscape_df$mutations[i] <- landscape_df$mutations[i] + 1
        
      }
      
    }
    
  }
  
  # classify the possible paths on the landscape (genotype to genotype)
  # connecting pairs of genotypes to link them on the landscape visualisation; each individual pair will get an ID number
  graph_df <- NULL
  pair <- 1
  
  # for each genotype
  for (i in 1:length(landscape_df[,1])) {
    
    # compute the list of neighbours for the focal genotype
    neighbours <- as.data.frame(findNeighbours(landscape_df, i, (n+s*n)))
    
    # assign ID numbers to focal genotype + neighbours; all pairs get individual IDs
    for (j in 1:length(neighbours[,1])) {
      
      # assign ID to focal genotype and add it to the data frame
      landscape_df[i, "group"] <- pair
      
      # assign the same ID to one of its neighbours and add it to the data frame
      neighbours[j, "group"] <- pair
      
      # check whether this neighbour is connected through a mutation within the genome (intra) or between the genomes (inter)
      if (paste(neighbours[j, 1:n], collapse = "") == paste(landscape_df[i, 1:n], collapse = "")){
        
         landscape_df[i, "mut"] <- "inter"
         neighbours[j, "mut"] <- "inter"
        
      } else {
        
        landscape_df[i, "mut"] <- "intra"
         neighbours[j, "mut"] <- "intra"
        
      }
      
      graph_df <- rbind(graph_df, landscape_df[i, ])
      graph_df <- rbind(graph_df, neighbours[j, ])
      
      
      pair <- pair + 1
      
    }
    
  }
  
  names(graph_df)[3*n+1] <- "fitness"
  graph_df$genotypeID <- as.factor(graph_df$genotypeID)
  
  return(graph_df)
  
}
```

# 5) Adaptive walks
three possible ways:
- greedy walk   -> move to the neighbour with the highest fitness
- random fitter -> move to a random neighbour with higher fitness
- proportional  -> probability to move to another genotype is weighted by the fitness differences

```{r adaptive walk}

adaptive_walk <- function(landscape, # landscape(s) on which to perform walk(s)
                          walk = c("greedy", "random", "prop"), # types of walks
                          n,
                          c,
                          s, # nb. of species interacting
                          s_tot, # total number of species in the system
                          IM_c,
                          start = c("WT", "R"), # choosing starting genotype
                          max_steps=100) # max. number of steps on the landscape before I interrupt
{
  
  # turn landscapes into data frames
  landscape_df <- list()
  
  for (i in 1:s_tot){
    
    landscape_df[[i]] <- as.data.frame(landscape[[i]])
    landscape_df[[i]]$ID <- 1:nrow(landscape_df[[i]]) # give genotypes an ID (we need this for our neighbour search later on)
    
  }
  
  # define start genotypes
  walks <- list() # this is a list to keep track of the genotypes during the adaptive walk
  
  if (start == "WT"){
    
    for (i in 1:s_tot){
      
      walks[[i]] <- landscape_df[[i]][1,] # this will give us the starting point of the adaptive walk
      walks[[i]]$step <- 0 # to signalise that this is the initial genotype
      walks[[i]]$focal <- NA # later I can store the ID of the focal species (the species that is mutating)
      
    }
    
  }
  
  if (start == "R"){
    
    random_seq <- sample(a, n*s_tot, replace = TRUE) # I'm just generating a random sequencing to start with; I guess right now this only works if all species interact with each other (s = s_tot-1)
    
    for (i in 1:s_tot){
      temp_seq <- NA # here I will store the sequence for each species; this will be updated as the positions of loci in the sequence will change for each species (focal species always at the start of the sequence)

      temp_seq[1:n] <- random_seq[(1+(i-1)*n):(n+(i-1)*n)] # these are the allelic values for the loci in the focal species
      temp_seq[(n+1):(n+n*s)] <- random_seq[-c((1+(i-1)*n):(n+(i-1)*n))] # these are the allelic values for the loci in the interacting species

      walks[[i]] <- landscape_df[[i]][rowSums(mapply(`==`, landscape_df[[i]][, 1:(n+n*s)], temp_seq)) == n+n*s,] # this will give us the starting point of the adaptive walk; I'm matching the entry in the genotype table to the random sequence I generated earlier here
      walks[[i]]$step <- 0 # to signalise that this is the initial genotype
      walks[[i]]$focal <- NA # later I can store the ID of the focal species (the species that is mutating)
      
    }
    
  }
  
  # set current genotype
  current_genotypes <- walks # this will be updated as we navigate the landscape(s)
  
  # count steps
  step <- 1
  
  # repeat adaptive steps until a local maximum or the maximum allowed number of steps are reached
  repeat { for (i in 1:s_tot){
    # find neighbours and choose those with higher fitness
    # need to determine how many there are; 
    # - if 0, end simulation?; 
    # - if 1, go there directly; 
    # - if >1, do true adaptive walk depending on method of choice
    
      # find neighbours one step away
    neighbours <- findNeighbours(landscape_df[[i]], current_genotypes[[i]]$ID, n)
    
    # but now I only want those neighbours that are accessible through mutation within a genome
    true_neighbours <- neighbours[which(rowSums(mapply(`==`, neighbours[, (n+1):(n+s*n)], current_genotypes[[i]][, c((n+1):(n+s*n))])) == n*s),] # checking each allelic value at loci of interacting species against reference ("current genotype") and only accept, if all column match
    
    # filter those with higher or equal fitness than the current genotype
    neighbours_fitter <- true_neighbours[which(true_neighbours[, 2*n+(s*n)+1] >= current_genotypes[[i]][, 2*n+(s*n)+1]),]
    
    new_genotypes <- list()
    
    # first option - already at peak; then stay
    if (nrow(neighbours_fitter) == 0) {
      
      new_genotypes[[i]] <- current_genotypes[[i]][, c(1:(2*n+n*s+2))] # stay - maybe something will happen in another species; will update step and focal species at the end of this go
      
      # or there is only one high-fitness neighbor - go there directly
    } else if (nrow(neighbours_fitter) == 1) {
      
      new_genotypes[[i]] <- neighbours_fitter
      
      # or there are several high-fitness neighbors, choose fittest neighbour
    } else if (walk == "greedy"){
      
      new_genotypes[[i]] <- neighbours_fitter[which(neighbours_fitter[, 2*n+(s*n)+1] == max(neighbours_fitter[,2*n+(s*n)+1])),]
      
      # choose random neighbour
    } else if (walk == "random"){
      
      new_genotypes[[i]] <- neighbours_fitter[sample(1:nrow(neighbours_fitter), 1),]
      
      # or choose neighbour with certain probability weighted by how much more fit they are                                  
    } else if (walk == "prop"){
      
      new_genotypes[[i]] <- neighbours_fitter[sample(1:nrow(neighbours_fitter), 1,
                                       prob=(mapply('-', neighbours_fitter[, 2*n+(s*n)+1], current_genotypes[[i]][2*n+(s*n)+1]))/abs(sum(mapply('-', neighbours_fitter[, 2*n+(s*n)+1], current_genotypes[[i]][2*n+(s*n)+1])))),]
    }
    
    # save step on landscape in my table to track the walk
    walks[[i]] <- rbind(walks[[i]], cbind(new_genotypes[[i]], step, focal = i))
    
    # after every step, update fitness of the other species since that might have changed due to intergenomic epistasis
    for (j in c(1:s_tot)[-i]){
      
      # update genotype
      new_genotypes[[j]] <- landscape_df[[j]][which(rowSums(mapply(`==`, landscape_df[[j]][, 1:n], current_genotypes[[j]][, 1:n])) == ncol(landscape_df[[j]][, 1:n]) & rowSums(mapply(`==`, landscape_df[[j]][, (n+1):(n+s*n)], new_genotypes[[i]][, 1:n])) == ncol(landscape_df[[j]][, (n+1):(n+s*n)])),] # the loci of the focal genome are keeping the same allelic values as before, but the rest are updated in case there was a mutation in one of the other species - right now this only works with s = 1... but too lazy to implement variable s here rn soz
      
      # store movement on landscape (or lack thereof I guess lol)
      walks[[j]] <- rbind(walks[[j]], cbind(new_genotypes[[j]], step, focal = i))
      
    }
    
    # set up next step on landscape
    current_genotypes <- new_genotypes
    step <- step+1
    
    # stop if fitness for *all* species didn't change since last step
    stop_test <- NULL
    
    if (step > 2){
    
    for (i in 1:s_tot){
      
      if (walks[[i]][nrow(walks[[i]]), 2*n+(s*n)+1] == walks[[i]][nrow(walks[[i]])-1, 2*n+(s*n)+1] &
          walks[[i]][nrow(walks[[i]]), 2*n+(s*n)+1] == walks[[i]][nrow(walks[[i]])-2, 2*n+(s*n)+1]) { # hmmm, if I have more species, maybe I'll have to check if fitness changed since the focal species was last allowed to mutate itself
        
        stop_test <- c(stop_test, 1)
        
      }
      
    }
    
    }
    
    
    if (length(stop_test) == s_tot) { break }
      
  }
    
    if (length(stop_test) == s_tot) { break }
   
    # stop after a number of steps if no optimum was reached (usually shouldn't be an issue)
    if (step > max_steps) { break } 
     
  }
  
  return(walks)
  
}

```


# 6) visualise the whole system 
```{r visualise systems and adaptive walks}

visualise_system <- function(landscapes,
                             n,
                             c,
                             s,
                             s_tot){
  
  visual_scapes_df <- NULL
  
  # combining all data frames into one, so I can plot the fitness landscape of each species as a separate facet 
  for (i in 1:s_tot){
    
    temp <- visual_landscape(landscapes[[i]], 
                                     n, 
                                     c, 
                                     s)
    temp$species <- i # to differentiate between species
    
    visual_scapes_df <- rbind(visual_scapes_df, temp)
    
  }
  
  ggplot(visual_scapes_df,
       aes(x = mutations,
           y = fitness)) +
  geom_line(data = visual_scapes_df,
            aes(group = group,
                linetype = mut),
            color="grey80",
            linewidth = 0.7) +
  geom_label(label = visual_scapes_df$seq,
             aes(col = seq)) +
  scale_linetype_manual(breaks = c("intra", "inter"),
                        values = c("solid", "dashed"))+
  xlab("Hamming distance from reference") +
  ylab("Fitness") +
    facet_wrap(~species,
               labeller = labeller(species = 
    c("1" = "Species 1",
      "2" = "Species 2"))) +
  theme_bw() +
  theme(legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(linewidth = 0.5, linetype = 2),
        panel.grid.minor.x = element_blank(),
        text = element_text(size = 15),
        axis.text = element_text(size = 13))
  
}

visualise_walks <- function(adaptive_walks,
                            n,
                            s,
                            s_tot,
                            landscapes){
  
  
  walks_df <- NULL

  # combining all data frames into one, so I can plot the adaptive walk of each species as a separate facet 
  for (i in 1:s_tot){
    
    temp <- as.data.frame(adaptive_walks[[i]])
    temp$peak <- unique(landscapes[[i]][which(landscapes[[i]][, 2*n+(s*n)+1] == max(landscapes[[i]][, 2*n+(s*n)+1])), 2*n+(s*n)+1]) # I also want to plot the fitness of the global fitness peak 
    
    temp$species <- i # to differentiate between species
    
    walks_df <- rbind(walks_df, temp)

  }
  
  colnames(walks_df)[2*n+(s*n)+1] <- "Fitness"

  ggplot(walks_df,
       aes(x = step,
           y = Fitness)) +
  geom_line() +
    geom_hline(aes(yintercept = peak),
               linetype = "dashed",
               col = "firebrick3") +
    facet_wrap(~species,
               labeller = labeller(species = 
    c("1" = "Species 1",
      "2" = "Species 2"))) +
  theme_bw()
  
}

```

# 7) Replicate the adaptive walks
````{r replicates}

assess_peaks <- function(n, # nb. of loci
                         k, # nb. of loci interacting within genome (intragenomic epistasis)
                         a, # nb. of alleles at each locus
                         c, # nb. of loci interacting between genomes (intergenomic epistasis)
                         s, # nb. of species interacting
                         s_tot, # total nb. of species in system
                         IM_k_reps, # nb. of replicates for intragenomic epistasis
                         IM_k_type, # type of interaction matrix for intragenomic epistasis
                         IM_c_reps, # nb. of replicates for intergenomic epistasis
                         IM_c_type, # type of interaction matrix for intergenomic epistasis
                         scape_reps, # nb. of replicates to generate fitness landscapes for each combination of IM_k and IM_c
                         fitness_contrib, # how fitness contributions are drawn 
                         fitness_calculation, # how fitness is calculated for genotypes
                         fit_mean, # mean of fintess distribution when drawing from a normal distribution, or min fitness when drawing from a uniform distribution
                         fit_sd, # sd of fitness distribution when drawing from a normal distribution, or max fitness when drawing from a uniform distribution
                         walk_reps, # nb. of replicates of adaptive walks on a given landscape
                         walk_type, # vector of types of adaptive walks (random, greedy, prop)
                         walk_start, # starting genotype of adaptive walk (random or starting at reference type/WT)
                         max_steps) # max nb. of steps in adaptive walk
{

# replicates of interaction matrices
IM_k_replicated <- list()

for (k_rep in 1:IM_k_reps){
  
  
  IM_k_replicated[[k_rep]] <- build_IMk(IM = IM_k_type,
                      n,
                      k,
                      s,
                      s_tot)

}
 
IM_c_replicated <- list()
  
for (c_rep in 1:IM_c_reps){
  
  IM_c_replicated[[c_rep]] <- build_IMc(IM = IM_c_type,
                      n,
                      c,
                      s,
                      s_tot)
}


# for each combination of IM_k and IM_c make the landscapes and perform the random walks

peaks_df <- NULL #I want to save the endpoints of all walks in one df
total_walks <- list()
total_walks[[c_rep]] <- list()

for (k_rep in 1:IM_k_reps) {
  
  IM_k <- IM_k_replicated[[k_rep]]
  
  for (c_rep in 1:IM_c_reps){
    
    IM_c <- IM_c_replicated[[c_rep]]
    
    scapes_replicated <- list() # to store the landscapes
    scapes_replicated[[c_rep]] <- list() # I want to save the landscapes for each combination of k and c matrix (only C is variable for now)
  
    # create the landscapes
  for (scape_rep in 1:scape_reps) {
    
    scapes_replicated[[c_rep]][[scape_rep]] <- build_landscape(IM_k,
                             IM_c, 
                fitness_contrib,
                fitness_calculation,
                n,
                k,
                a,
                c,
                s,
                s_tot,
                fit_mean,
                fit_sd)
    
    # identify the global fitness peak for each landscape
    global_peaks <- list()
    
    for (global_peak in 1:s_tot){
      
      global_peaks[[global_peak]] <-  max(scapes_replicated[[c_rep]][[scape_rep]][[global_peak]][,2*n+s*n+1])
      
    }
    
    # for each landscape perform the adaptive walks
    total_walks[[c_rep]][[scape_rep]] <- list()
    
    for (walking in walk_type) { # perform different types of adaptive walks for the same landscape to have the direct comparison e.g. random walk vs greedy walk

    walks_replicated <- list()
    
    # perform the walk
    for (walk_rep in 1:walk_reps) {
      
      walks_replicated[[walk_rep]] <- adaptive_walk(scapes_replicated[[c_rep]][[scape_rep]], 
              walk = walking,
              n,
              c,
              s, 
              s_tot, 
              IM_c,
              start = walk_start,
              max_steps)
      
      # store the desired information (endpoint of walk and simulation parameters)
      for (species in 1:s_tot) {
        
        start_seq <- paste(paste(walks_replicated[[walk_rep]][[species]][1, c(1:n)], collapse = ""), "-", c(paste(walks_replicated[[walk_rep]][[species]][1, c((n+1):(n+n*s))], collapse = ""))) # I want to save the starting point of each adaptive walk
        
        # and then keep track of the end points of each walk here; I am saving the end point of the walk alongside the simulation parameters
        peaks_df <- rbind(peaks_df, cbind(walks_replicated[[walk_rep]][[species]][nrow(walks_replicated[[walk_rep]][[species]]),], data.frame(k_rep, 
                                                                                                                                              c_rep, 
                                                                                                                                              scape_rep, 
                                                                                                                                              walk_rep, 
                                                                                                                                              species,
                                                                                                                                              n,
                                                                                                                                              k,
                                                                                                                                              a,
                                                                                                                                              c,
                                                                                                                                              s,
                                                                                                                                              walk_start,
                                                                                                                                              walking,
                                                                                                                                              start_seq,
                                                                                                                                              global_peak = global_peaks[[species]])))
        
      }
      
    }
    
    total_walks[[c_rep]][[scape_rep]][[match(walking, walk_type)]] <- walks_replicated # store adaptive walk for each landscape replicate for the different types of adaptive walk
    
    }
  
  }
    
  }
  
}

return(list(peaks_df, 
            IM_k_replicated,
            IM_c_replicated,
            scapes_replicated,
            total_walks))

}


````


# XX) test runs
```{r test landscape}

# set.seed(1313)
# 
# n = 2
# k = 0
# a = 2
# c = 0
# s = 1
# s_tot = 2
# 
# IM_c <- build_IMc(IM = "R",
#                       n,
#                       c,
#                       s,
#                       s_tot)
# 
# IM_k <- build_IMk(IM = "R",
#                       n,
#                       k,
#                       s,
#                       s_tot)
# 
# testscape <- build_landscape(IM_k,
#                              IM_c, 
#                 fitness_contrib = "N",
#                 fitness_calculation = "KJ",
#                 n,
#                 k,
#                 a,
#                 c,
#                 s,
#                 s_tot,
#                 fit_mean = 0,
#                 fit_sd = 0.5)
# 
# system_fig <- visualise_system(testscape,
#                  n,
#                  c,
#                  s,
#                  s_tot)
# 
# walk_test <- adaptive_walk(testscape, 
#               walk = "random",
#               n,
#               c,
#               s, 
#               s_tot, 
#               IM_c,
#               start = c("R"),
#               max_steps=100)
# 
# walks_fig <- visualise_walks(walk_test,
#                 n,
#                 s,
#                 s_tot,
#                 testscape)


```