---
title: "NKC(S)"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_knit$set(root.dir = "~/OneDrive - Universitaet Bern/R_scripts/NKC(S)/") # set directory
```

### Set up workspace
```{r libraries}
rm (list = ls())

library(ggplot2) 
library(gtools)

```

### The NKC(S) model
code for NK model based on explanations from Welch & Waxman (2005) and supported by python code from Maciej Workiewicz (https://github.com/Mac13kW/NK_model)

the NK model was introduced by Kauffman & Weinberger (1989) and the NKC(S) model was introduced by Kauffman & Johnson (1991)

## 1) Variable explanations
n = nb. of haploid loci
a = nb. of possible alleles per locus
k = nb. of loci that epistatically influence a given focal locus; k <= n-1
s = nb. of species that are linked through intergenomic epistasis
s_tot = total nb. of species in the system
c = nb. of loci in each of s species epistatically influencing a given focal locus
W = fitness
h = fitness contributions of each locus
IM = interaction matrix; determines how the loci are linked epistatically

(for now we will assume full symmetry; i.e. all species have the same n, a, k, s, c, and h)

## 2) Interaction matrix (IM)
the fitness contribution of a locus i depends on the allelic value itself (position i) and the allelic values at k other loci; the interaction matrix defines *which* loci are epistatically connected
here I define functions for different types of interaction matrices

# 2.1) random matrix
any locus can be influenced by any locus - interactions are not necessarily reciprocal

```{r random interaction matrix}
IM_random <- function(n, k){
  
  if (n == 2 & k == 1){
    
    IM_random <- matrix(n, n, data = rep(1, n^2))
    
  } else {
  
  IM_random <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_random[row(IM_random) == col(IM_random)] <- 1 # fitness value at locus i always depends on allele at locus i itself for within species genetic interactions
  
  for (i in 1:n) { # for each row we assign random indices that we assign as interacting loci
    
    interacting_loci <- sample(c(1:nrow(IM_random))[-i], k) # draw random non-diagonal loci that epistatically interact with locus i
    IM_random[i, interacting_loci] <- 1
    
  }
  
  }
  
  return(IM_random)
  
}

IM_random_c <- function(n, c){
  
  IM_random <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

  for (i in 1:n) { # for each row we assign random indices that we assign as interacting loci
    
    interacting_loci <- sample(c(1:nrow(IM_random)), c) # draw random loci that epistatically interact with locus i
    IM_random[i, interacting_loci] <- 1
    
  }
  
  return(IM_random)
  
}
```

# 2.2) modular matrix
epistatic connections are arranged in blocks of k+1 reciprocally interacting loci ("block-diagonal" matrix);
n needs to be divisible by k+1

```{r modular interaction matrix}
IM_modular <- function(n, k){
  
  if (n%%(k+1) != 0){
    
    print("n needs to be divisible by k+1") # prints message if genome string cannot be divided into equal blocks
    
  }
  
  else{
  
  IM_modular <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  
  i <- 1
  while (i <= n) {# we assign blocks of interacting loci
    
    IM_modular[i:(i+k), i:(i+k)] <- 1
    
    i <- i+k+1
    
  }
  
  return(IM_modular)
  
  }
  
}

IM_modular_c <- function(n, c){
  
  if (n%%(c) != 0){
    
    print("n needs to be divisible by c") # prints message if genome string cannot be divided into equal blocks
    
  }
  
  else{
  
  IM_modular <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  
  i <- 1
  while (i <= n) {# we assign blocks of interacting loci
    
    IM_modular[i:(i+c-1), i:(i+c-1)] <- 1
    
    i <- i+c
    
  }
  
  return(IM_modular)
  
  }
  
}
```

# 2.3) Nearest neighbour 
the genome is circular and each locus reciprocally interacts with its k neighbours ("local" interactions); 
k needs to be divisible by 2 for symmetry reasons -> interactions with k/2 neighbours to either side

```{r nearest neighbour interaction matrix}
IM_neighbour <- function(n, k){
  
  if (k%%(2) != 0){
    
    print("k needs to be divisible by 2") # prints message
    
  }
  
  else{
    
    IM_neighbour <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

    for (i in 1:n){ # assign neighbours in each row (= i +/- k/2)
      
     if (i-k/2 < 1) { # to avoid going out of bounds (negative indeces)
       
       out_bounds <- 1 - (i-k/2) # these are the loci that "wrap around" in the circular genome
       
       IM_neighbour[i, i:(i+k/2)] <- 1 # normal assignment of "downstream" loci 
       IM_neighbour[i, (i-k/2+out_bounds):i] <- 1
       IM_neighbour[i, (n-out_bounds+1):n] <- 1 
       
     }
      
      else if (i+k/2 > n) { # to avoid going out of bounds (indeces exceeding n)
        
        out_bounds <- (i+k/2) - n # these are the loci that "wrap around" in the circular genome
       
        IM_neighbour[i, (i-k/2):i] <- 1 # normal assignment of "upstream" loci 
        IM_neighbour[i, i:(i+k/2-out_bounds)] <- 1
        IM_neighbour[i, 1:out_bounds] <- 1
       
      }
      
      else {
        
        IM_neighbour[i, (i-k/2):(i+k/2)] <- 1
        
      }
      
    }
    
    return(IM_neighbour)
    
  }
  
}
```

# 2.4) Preferential attachment (Rivkin & Siggelkow, 2007)
loci that already have many interactions are more likely to add a further interaction than loci that have few interactions; total of n*k interactions among loci

```{r preferential interaction matrix}
IM_preferential <- function(n, k){
  
  IM_preferential <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_preferential[row(IM_preferential) == col(IM_preferential)] <- 1 # fitness value at locus i always depends on allele at locus i itself
  
  while (sum(IM_preferential) < n*(k+1)) {
    
    # pick a random row
    row <- sample(n ,1)
    
    # pick a column (weighted by how many '1's the column already contains)
    column <- sample(n, 1, prob = colSums(IM_preferential))
    
    IM_preferential[row, column] <- 1
    
    
  }
  
  return(IM_preferential)
  
}

IM_preferential_c <- function(n, c){
  
  IM_preferential <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

  while (sum(IM_preferential) < n*c) {
    
    # pick a random row
    row <- sample(n ,1)
    
    # pick a column (weighted by how many '1's the column already contains)
    column <- sample(n, 1, prob = colSums(IM_preferential))
    
    IM_preferential[row, column] <- 1
    
    
  }
  
  return(IM_preferential)
  
}
  
```

# 2.5) Hierarchical (Rivkin & Siggelkow, 2007)
few loci influence all other loci; the matrix consists of '1's below the diagonal, starting with the ﬁrst column, continuing with the second column, etc., until there are n*k interactions among loci

```{r hierarchical interaction matrix}
IM_hierarchical <- function(n, k){
  
  IM_hierarchical <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_hierarchical[row(IM_hierarchical) == col(IM_hierarchical)] <- 1 # fitness value at locus i always depends on allele at locus i itself
    
    for (i in 1:n){# for each column
      
      for (j in 1:n){# for each row
        
        if (sum(IM_hierarchical) < n*(k+1) & j>i) { # below the diagonal until we get to n*k interactions among loci
          
          IM_hierarchical[j,i] <- 1
        
      }
      
    }
    
  }
  
  return(IM_hierarchical)
  
}

IM_hierarchical_c <- function(n, c){
  
  IM_hierarchical <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

    for (i in 1:n){# for each column
      
      for (j in 1:n){# for each row
        
        if (sum(IM_hierarchical) < n*c & j>=i) { # below and including the diagonal until we get to n*c interactions among loci
          
          IM_hierarchical[j,i] <- 1
        
      }
      
    }
    
  }
  
  return(IM_hierarchical)
  
}

```

# 2.6) Dependent (Rivkin & Siggelkow, 2007)
few loci are dependent on all other loci

```{r dependent interaction matrix}
IM_dependent <- function(n, k){
  
  IM_dependent <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_dependent[row(IM_dependent) == col(IM_dependent)] <- 1 # fitness value at locus i always depends on allele at locus i itself
  
for (i in n:1){# for each row
      
      for (j in n:1){# for each column
        
        if (sum(IM_dependent) < n*(k+1) & i>j) { # below the diagonal until we get to n*k interactions among loci
          
          IM_dependent[i,j] <- 1
        
      }
      
    }
    
  }
  
  
  return(IM_dependent)
  
}

IM_dependent_c <- function(n, c){
  
  IM_dependent <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

for (i in n:1){# for each row
      
      for (j in n:1){# for each column
        
        if (sum(IM_dependent) < n*c & i>=j) { # below and including the the diagonal until we get to n*c interactions among loci
          
          IM_dependent[i,j] <- 1
        
      }
      
    }
    
  }
  
  
  return(IM_dependent)
  
}

```

## 3) Creating the landscape
# 3.1) generate genotypes
generate all possible genotypes; alleles are encoded by numbers (1, 2, ..., a)

```{r generate genotypes}
generate_genotypes <- function(a, n){
  
  genotypes <- gtools::permutations(a, n, c(1:a), repeats = TRUE)
  return(genotypes)
  
}
```

# 3.2) generate fitness contributions
a^(k+1+c*s) different allele combinations per locus for each locus

```{r draw fitness contributions}

# Welch & Waxman drew from a normal distribution
generate_alleles <- function(n, k, a, c, s, fit_mean, fit_sd){
  
  allelic_vals <- matrix(c(rnorm(n*a^(k+1+c*s), fit_mean, fit_sd)), ncol = n) 
  return(allelic_vals)
  
}

# Kauffman drew from a uniform distribution
generate_alleles_unif <- function(n, k, a, c, s, fit_min, fit_max){
  
  allelic_vals <- matrix(c(runif(n*a^(k+1+c*s), fit_min, fit_max)), ncol = n)
  return(allelic_vals)
  
}
```

# 3.3) Calculate the genotype fitness
```{r calculate genotype fitness}

# fitness calaculation like Kauffman & Weinberger (1989) and Kauffman & Johnson (1991)
fitness_calc <- function(gene_vector){
  
  W = (1/length(gene_vector))*sum(gene_vector) 
  return(W)
  
}

# Welch & Waxman used a multiplicative model of fitness (ln fitness)
fitness_calc_mult <- function(gene_vector){
  
  W = exp(sum(gene_vector))
  return(W)
  
}

```

# 3.4) Generate intergenomic interaction matrices
```{r IM_c}

build_IMc <- function(IM = c("R", "M", "P", "H", "D"),
                      n,
                      c,
                      s,
                      s_tot){
  
  # determine how to construct the intergenomic epistatic interactions and what kind of interaction matrix (IM) to use 
  if (IM == "R"){# for Random matrix
    
    matrix_c <- IM_random_c
     
  } else if (IM == "M"){# for Modular matrix
    
    matrix_c <- IM_modular_c
    
  } else if (IM == "N"){# for nearest neighbour matrix
    
    matrix_c <- IM_neighbour_c
    
  } else if (IM == "P"){# for preferential interaction matrix
    
    matrix_c <- IM_preferential_c
    
  } else if (IM == "H"){# for hierarchical interaction matrix
    
    matrix_c <- IM_hierarchical_c
    
  } else if (IM == "D"){# for dependent interaction matrix
    
    matrix_c <- IM_dependent_c
    
  }
  
  matrix_c_species <- list()
  
  # for each species in the system
  for (i in 1:s_tot){
    
    # I need IM to describe the interaction between a focal species and each of its interaction partners
    matrix_temp <- list() # I collect this in a temporary list
    
    # so, for each interaction partner:
    for (j in 1:s){
      
      # generation intergenomic interaction matrix
      matrix_temp[[j]] <- matrix_c(n,c)
      
    }
    
    matrix_merged <- do.call(cbind, matrix_temp) # merge all IM by column (rows = loci in focal genome and then columns = all the loci in all the interacting species)
     matrix_c_species[[i]] <- matrix_merged
    
  }
  
  return(matrix_c_species)
  
}

```

# 3.5) Generate NKC(S) landscape
```{r generate landscape}
build_landscape <- function(IM_k = c("R", "M", "N", "P", "H", "D"), # type of interaction matrix (intragenomic epistasis)
                            IM_c, # I need to define the interaction matrix for intergenomic epistasis separately, so I can also refer to it during the adaptive walk
                            fitness_contrib = c("N", "U"), # way to draw fitness contributions (normal vs. uniform distribution)
                            fitness_calculation = c("KJ", "WW"), # way to calculate fitness (according to Kauffman & Johnson or Welch & Waxman) 
                            n, # nb of loci
                            k, # nb of interacting loci within a species
                            a, # nb of alleles per locus
                            c, # nb of interacting loci between species
                            s, # nb of species interacting
                            s_tot, # total number of species in the species
                            fit_mean, # mean of fintess distribution when drawing from a normal distribution, or min fitness when drawing from a uniform distribution
                            fit_sd) # sd of fintess distribution when drawing from a normal distribution, or max fitness when drawing from a uniform distribution
  {
  
  # determine how to construct the intragenomic epistatic interactions and what kind of interaction matrix (IM) to use 
  if (IM_k == "R"){# for Random matrix
    
    matrix_k <- IM_random
     
  } else if (IM_k == "M"){# for Modular matrix
    
    matrix_k <- IM_modular
    
  } else if (IM_k == "N"){# for nearest neighbour matrix
    
    matrix_k <- IM_neighbour
    
  } else if (IM_k == "P"){# for preferential interaction matrix
    
    matrix_k <- IM_preferential
    
  } else if (IM_k == "H"){# for hierarchical interaction matrix
    
    matrix_k <- IM_hierarchical
    
  } else if (IM_k == "D"){# for dependent interaction matrix
    
    matrix_k <- IM_dependent
    
  }

  
  # how to generate allelic values? (normal distribution vs uniform distribution)
  if (fitness_contrib == "N"){# for drawing from a normal distribution
    
    alleles_generate <- generate_alleles
    
  } else if (fitness_contrib == "U") {
    
    alleles_generate <- generate_alleles_unif
    
  }
  
  # how to calculate fitness?
  if (fitness_calculation == "KJ"){
    
    fitness_calculate <- fitness_calc 
    
  } else if (fitness_calculation == "WW"){
    
    fitness_calculate <- fitness_calc_mult 
    
  }
  
  # generate all possible genotypes (this is the same for all species here, since we assume that all species have the same n, a and c)
  genotypes <- generate_genotypes(a,n+(s*n)) # I generate "extended genotypes" to include the s*n sites in other species that are relevant for calculating fitness (but only n sites actually contribute to a genotype's fitness, if that makes sense?)
  
  # generate all possible fitness contributions depending on k epistatic interactions within species and c epistatic interactions with s other species
  h_table_species <- list() # a list with all look up tables for each of the s_tot species; each list item is a look-up table of dimension n x a^(k+1+c*s) for all possible allelic values
  
  # list of intragenomic epistasis IM for each species
  matrix_k_species <- list()
  
  # table to keep track of all fitness vectors
  fitnesses_species <- NULL
  
  # for each species:
  for (i in 1:s_tot){
    
    matrix_k_species[[i]] <- matrix_k(n,k)
    
    # generate look-up table with all possible allelic values (dependent on k+1+c*s loci within and between species); dimension n x a^(k+1+c*s) for all possible allelic values
    # each column = 1 locus, each row = different genetic background
    h_table_species[[i]] <- alleles_generate(n, k, a, c, s, fit_mean, fit_sd)
    
  }
  
  # now that we generated all the fitness contributions and know all the genetic interactions in the system
  
  # keeping track of "extended" genotypes, their fitness contributions and total calculated fitness
  genotype_table_species <- list()
  
  # for each species:
  for (i in 1:s_tot){
    
    # table to keep track of all fitness vectors
    fitnesses <- NULL
    
    # for each genotype (remember, all species have the same genotype encoding; it's just the fitness values and epistatic interactions that differ)
    for (j in 1:nrow(genotypes)){
      
      # keep track of fitness contribution at each locus (h)
      h_vector <- NULL # vector of fitness contributions per locus for each genotype
      
      # for each genotype we look up the fitness contribution (h) at each locus; h depends on k+1+c*s loci 
      # for each locus:
      for (l in 1:n) { # skipping "k" to iterate over, since k is used as a variable
        
        # which loci determine the fitness contribution at this locus?
        interesting_loci_k <- which(matrix_k_species[[i]][l, ] != 0) # based on the intragenomic IM
        interesting_loci_c <- which(IM_c[[i]][l,] != 0) # based on intergenomic IM
        
        interesting_loci <- c(interesting_loci_k, interesting_loci_c+n) # list of all loci that have an affect on the fitness contribution

        # what are the alleles present at the loci we're interested in for this given genotype?
        alleles <- genotypes[j, interesting_loci]
        
        # let's access the fitness contributions associated with the genetic background
        index <- 1
      
        # for all loci contributing to h:
        for (m in 1:(k+1+(s*c))) {
        
        index <- index + (a^((k+1+(s*c))-m))*(alleles[m]-1)
        
        }
      
        # store the fitness contributions in a vector
        h_vector <- cbind(h_vector, h_table_species[[i]][index,l])
      
      }
      
      # construct a table with all information relating to the fitness contributions etc.
      fitness_genotype <- cbind(h_vector, fitness_calculate(h_vector)) # calculate the total fitness (W) for each genotype
      fitnesses <- rbind(fitnesses, fitness_genotype) # compilation of individual fitness contributions (h) and calculated fitness values (W)
      
    }
    
    # combine the genotype table and the fitness table
    genotype_table_species[[i]] <- cbind(genotypes, fitnesses) # combining the genotype table and the fitness table
    # columns 1 to n represent the allelic values at each locus in the genome of the focal species
    # columns n+1 to n+(s*n) represent the allelic values at each locus in the genomes of the interacting species (= intergenomic epistasis)
    # columns n+(s*n)+1 to 2n+(s*n) are the fitness contributions per locus (h) for loci in the genome of the focal species
    # column 2n+(s*n)+1 is the calculated total fitness for each genotype taking into account all genetic interactions
      
  }
  
  return(genotype_table_species)

}

```

## 4) Exploring the landscape topology
# 4.1) Find neighbors one step away
This will include mutations that can happen within a focal species genome but also mutations that can happen in the genome of one of the interacting species

```{r neighbour search}

findNeighbours <- function(landscape, 
                           startIndex,
                           nb_loci){ # focal genotype to start neighbour search with
  
  # focal genotype
  temp_genotype <- landscape[startIndex,]
  
  differences <- c(rep(0, length(landscape[,1]))) # vector with entries for each genotype to keep track of difference to reference
    
  for (i in 1:nb_loci){
    
    for (j in 1:length(landscape[,1])){
      
      if (landscape[j,i] != temp_genotype[i]){ # if both genotypes don't carry the same allele...
        
        differences[j] <- differences[j] + 1 # ... I mark a difference in my vector
        
      }
      
    }
    
  }
  
  neighbours <- landscape[which(differences == 1), ]
  
  return(neighbours)
  
}
```

# 4.2) visualise the landscape

```{r landscape visualisation}
visual_landscape <- function(landscape, n, c, s) {
  
  landscape_df <- data.frame(landscape)
  landscape_df$genotypeID <- c(1:(length(landscape[,1]))) # assign ID to each genotype
  
  # count the nb. of mutations separating each genotype from the reference
  landscape_df$mutations <- 0
  
  for (i in 1:length(landscape_df[,1])) {
    
    landscape_df$seq[i] <- paste(paste(landscape_df[i, 1:n], collapse = ""), "-", c(paste(landscape_df[i, (n+1):(n+s*n)], collapse = ""))) # alternate way of representing the genotypes; this is purely visual information to plot

    for (locus in 1:(n+s*n)) {
      
      if (landscape_df[i,locus] != 1) {
        
        landscape_df$mutations[i] <- landscape_df$mutations[i] + 1
        
      }
      
    }
    
  }
  
  # classify the possible paths on the landscape (genotype to genotype)
  # connecting pairs of genotypes to link them on the landscape visualisation; each individual pair will get an ID number
  graph_df <- NULL
  pair <- 1
  
  # for each genotype
  for (i in 1:length(landscape_df[,1])) {
    
    # compute the list of neighbours for the focal genotype
    neighbours <- as.data.frame(findNeighbours(landscape_df, i, (n+s*n)))
    
    # assign ID numbers to focal genotype + neighbours; all pairs get individual IDs
    for (j in 1:length(neighbours[,1])) {
      
      # assign ID to focal genotype and add it to the data frame
      landscape_df[i, "group"] <- pair
      
      # assign the same ID to one of its neighbours and add it to the data frame
      neighbours[j, "group"] <- pair
      
      # check whether this neighbour is connected through a mutation in within the genome (intra) or between the genomes (inter)
      if (paste(neighbours[j, 1:n], collapse = "") == paste(landscape_df[i, 1:n], collapse = "")){
        
         landscape_df[i, "mut"] <- "inter"
         neighbours[j, "mut"] <- "inter"
        
      } else {
        
        landscape_df[i, "mut"] <- "intra"
         neighbours[j, "mut"] <- "intra"
        
      }
      
      graph_df <- rbind(graph_df, landscape_df[i, ])
      graph_df <- rbind(graph_df, neighbours[j, ])
      
      
      pair <- pair + 1
      
    }
    
  }
  
  names(graph_df)[3*n+1] <- "fitness"
  graph_df$genotypeID <- as.factor(graph_df$genotypeID)
  
  return(graph_df)
  
}
```

```{r test landscape}

IM_c <- build_IMc(IM = "R",
                      n = 2,
                      c = 1,
                      s = 1,
                      s_tot = 2)

testscape <- build_landscape(IM_k = "R",
                             IM_c, 
                fitness_contrib = "N",
                fitness_calculation = "KJ",
                n = 2,
                k = 1,
                a = 2,
                c = 1,
                s = 1,
                s_tot = 2,
                fit_mean = 0,
                fit_sd = 0.5)

visual_testscape <- visual_landscape(testscape[[2]], 
                                     n = 2, 
                                     c = 1, 
                                     s = 1)

scape_pic <- ggplot(visual_testscape,
       aes(x = mutations,
           y = fitness)) +
  geom_line(data = visual_testscape,
            aes(group = group,
                linetype = mut),
            color="grey80",
            linewidth = 0.7) +
  geom_label(label = visual_testscape$seq,
             aes(col = seq)) +
  scale_linetype_manual(breaks = c("intra", "inter"),
                        values = c("solid", "dashed"))+
  xlab("Hamming distance from reference") +
  ylab("Fitness") +
  theme_bw() +
  theme(legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(linewidth = 0.5, linetype = 2),
        panel.grid.minor.x = element_blank(),
        text = element_text(size = 15),
        axis.text = element_text(size = 13))

ggsave(path = "./",
       device = "pdf",
       units = c("cm"),
       width = 15,
       height = 10,
       filename = "NKCS_2111_sp2.pdf",
       plot = scape_pic)

```

# 5) Adaptive walks
three possible ways:
- greedy walk   -> move to the neighbour with the highest fitness
- random fitter -> move to a random neighbour with higher fitness
- proportional  -> probability to move to another genotype is weighted by the fitness differences

```{r adaptive walk}

adaptive_walk <- function(landscape, # landscape(s) on which to perform walk(s)
                          walk = c("greedy", "random", "prop"), # types of walks
                          n,
                          c,
                          s, # nb. of species interacting
                          s_tot, # total number of species in the system
                          IM_c = c("R"), # type of interaction matrix (intragenomic epistasis),
                          start = c("random", "WT"), # choosing starting genotype
                          max_steps=100) # max. number of steps on the landscape before I interrupt
{
 
  # determine how to construct the intergenomic epistatic interactions and what kind of interaction matrix (IM) to use 
  if (IM_c == "R"){# for Random matrix
    
    matrix_c <- IM_random
     
  } 
  
  # turn landscapes into data frames
  for (i in 1:s_tot){
    
    landscape_df[[i]] <- as.data.frame(landscape[[i]])
    landscape_df[[i]]$ID <- 1:nrow(landscape_df[[i]]) # give genotypes an ID (we need this for our neighbour search later on)
    
  }
  
  # define start genotypes
  walks <- list() # this is a list to keep track of the genotypes during the adaptive walk
  
  if (start == "WT"){
    
    for (i in 1:s_tot){
      
      walks[[i]] <- landscape_df[[i]][1,] # this will give us the starting point of the adaptive walk
      walks[[i]]$step <- 0 # to signalise that this is the initial genotype
      
    }
    
  }
  
  # set current genotype
  current_genotypes <- walks # this will be updated as we navigate the landscape(s)
  
  # count steps
  step <- 0
  
  # repeat adaptive steps until a local maximum or the maximum allowed number of steps are reached
  repeat
  {
    
    for (i in 1:s_tot){
    # find neighbours and choose those with higher fitness
    # need to determine how many there are; 
    # - if 0, end simulation; 
    # - if 1, go there directly; 
    # - if >1, do true adaptive walk depending on method of choice
    
      # find neighbours one step away, the number will always be n(a-1)
    neighbours <- findNeighbours(landscape_df[[i]], current_genotypes[[i]]$ID, n)
    
    # but now I only want those neighbours that are accessible through mutation within a genome
    true_neighbours <- neighbours[which(neighbours[, (n+1):(n+c*s)] == current_genotypes[[i]][,c((n+1):(n+c*s))]),]
    
    # filter those with higher or equal fitness than the current genotype
    neighbours_fitter <- true_neighbours[which(true_neighbours[, 2*n+(c*s)+1] >= current_genotypes[[i]][, 2*n+(c*s)+1]),]
    
    # first option - already at peak; then stay
    if (length(neighbours_fitter) == 0) {
      
      break
      
      # or there is only one high-fitness neighbor - go there directly
    } else if (length(neighbours_fitter)[1] == 2*n+(c*s)+2) {
      
      new_genotype <- neighbours_fitter
      
      # or there are several high-fitness neighbors, choose fittest neighbour
    } else if (walk == "greedy"){
      
      new_genotype <- neighbours_fitter[which(neighbours_fitter[, 2*n+(c*s)+1] == max(neighbours_fitter[,2*n+(c*s)+1])),]
      
      # choose random neighbour
    } else if (walk == "random"){
      
      new_genotype <- neighbours_fitter[sample(1:nrow(neighbours_fitter), 1),]
      
      # or choose neighbour with certain probability weighted by how much more fit they are                                  
    } else if (walk == "prop"){
      
      new_genotype <- neighbours_fitter[sample(1:nrow(neighbours_fitter), 1,
                                       prob=(neighbours_fitter[, 2*n+(c*s)+1] - temp_genotype[2*n+(c*s)+1])/abs(sum(neighbours_fitter[, 2*n+(c*s)+1] - temp_genotype[2*n+(c*s)+1]))),]
    }
    
    # after every step, update fitness of the other species since that might have changed due to intergenomic epistasis
    for (j in c(1:s_tot)[-i]){
      
      
      
    }
    
      
    }
    
  }
  
  as.data.frame(findNeighbours(landscape_df, i, n)) # this gives us the neighbours that are accessible through mutation within a genome
   
  
}

```