---
title: "NKC(S)"
output: html_notebook
---

Loraine Hablützel - 09.06.2026
see preprint: https://doi.org/10.64898/2026.04.01.715933

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png")
options(bitmapType = "cairo")

knitr::opts_knit$set(root.dir = "~/OneDrive - Universitaet Bern/NKC_project/R_scripts/") # set directory
```

# Set up workspace
```{r libraries}

library(gtools) # permutations to get all possible genotype combinations
library(dplyr) # for constructing the data sets

```

# (A) The NKC(S) model
code for NK model based on explanations from Welch & Waxman (2005) and supported by python code from Maciej Workiewicz (https://github.com/Mac13kW/NK_model)
the NK model was introduced by Kauffman & Weinberger (1989) and the NKC(S) model was introduced by Kauffman & Johnson (1991)

## 1) Variable explanations
n = nb. of haploid loci
a = nb. of possible alleles per locus
k = nb. of loci that epistatically influence a given focal locus; k <= n-1
s = nb. of species that are linked through intergenomic epistasis
s_tot = total nb. of species in the system
c = nb. of loci in each of s species epistatically influencing a given focal locus; c <= n
W = fitness
h = fitness contributions of each locus
IM = interaction matrix; determines how the loci are linked epistatically

(for now we will assume full symmetry; i.e. all species have the same n, a, k, s, c, and h)

## 2) Interaction matrix (IM)
the fitness contribution of a locus i depends on the allelic value itself (position i) and the allelic values at k other loci; the interaction matrix defines *which* loci are epistatically connected
here I define functions for different types of interaction matrices

### 2.1) random matrix
any locus can be influenced by any locus - interactions are not necessarily reciprocal

```{r random interaction matrix}
IM_random <- function(n, k){
  
  if (k == (n-1)){ # fully epistatic
    
    IM_random <- matrix(n, n, data = rep(1, n^2))
    
  } else {
  
  IM_random <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_random[row(IM_random) == col(IM_random)] <- 1 # fitness value at locus i always depends on allele at locus i itself for within species genetic interactions
  
  for (i in 1:n) { # for each row we assign random indices that we assign as interacting loci
    
    interacting_loci <- sample(c(1:nrow(IM_random))[-i], k) # draw random non-diagonal loci that epistatically interact with locus i
    IM_random[i, interacting_loci] <- 1
    
  }
  
  }
  
  return(IM_random)
  
}

IM_random_c <- function(n, c){
  
  IM_random <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

  for (i in 1:n) { # for each row we assign random indices that we assign as interacting loci
    
    interacting_loci <- sample(c(1:nrow(IM_random)), c) # draw random loci that epistatically interact with locus i
    IM_random[i, interacting_loci] <- 1
    
  }
  
  return(IM_random)
  
}
```

### 2.2) modular matrix
epistatic connections are arranged in blocks of k+1 reciprocally interacting loci ("block-diagonal" matrix);
n needs to be divisible by k+1

```{r modular interaction matrix}
IM_modular <- function(n, k){
  
  if (n%%(k+1) != 0){
    
    print("n needs to be divisible by k+1") # prints message if genome string cannot be divided into equal blocks
    
  }
  
  else{
  
  IM_modular <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  
  i <- 1
  while (i <= n) {# we assign blocks of interacting loci
    
    IM_modular[i:(i+k), i:(i+k)] <- 1
    
    i <- i+k+1
    
  }
  
  return(IM_modular)
  
  }
  
}

IM_modular_c <- function(n, c){
  
  if (n%%(c) != 0){
    
    print("n needs to be divisible by c") # prints message if genome string cannot be divided into equal blocks
    
  }
  
  else{
  
  IM_modular <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  
  i <- 1
  while (i <= n) {# we assign blocks of interacting loci
    
    IM_modular[i:(i+c-1), i:(i+c-1)] <- 1
    
    i <- i+c
    
  }
  
  return(IM_modular)
  
  }
  
}
```

### 2.3) Nearest neighbour 
the genome is circular and each locus reciprocally interacts with its k neighbours ("local" interactions); 
k needs to be divisible by 2 for symmetry reasons -> interactions with k/2 neighbours to either side

```{r nearest neighbour interaction matrix}
IM_neighbour <- function(n, k){
  
  if (k%%(2) != 0){
    
    print("k needs to be divisible by 2") # prints message
    
  }
  
  else{
    
    IM_neighbour <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

    for (i in 1:n){ # assign neighbours in each row (= i +/- k/2)
      
     if (i-k/2 < 1) { # to avoid going out of bounds (negative indeces)
       
       out_bounds <- 1 - (i-k/2) # these are the loci that "wrap around" in the circular genome
       
       IM_neighbour[i, i:(i+k/2)] <- 1 # normal assignment of "downstream" loci 
       IM_neighbour[i, (i-k/2+out_bounds):i] <- 1
       IM_neighbour[i, (n-out_bounds+1):n] <- 1 
       
     }
      
      else if (i+k/2 > n) { # to avoid going out of bounds (indeces exceeding n)
        
        out_bounds <- (i+k/2) - n # these are the loci that "wrap around" in the circular genome
       
        IM_neighbour[i, (i-k/2):i] <- 1 # normal assignment of "upstream" loci 
        IM_neighbour[i, i:(i+k/2-out_bounds)] <- 1
        IM_neighbour[i, 1:out_bounds] <- 1
       
      }
      
      else {
        
        IM_neighbour[i, (i-k/2):(i+k/2)] <- 1
        
      }
      
    }
    
    return(IM_neighbour)
    
  }
  
}
```

### 2.4) Preferential attachment (Rivkin & Siggelkow, 2007)
loci that already have many interactions are more likely to add a further interaction than loci that have few interactions; total of n*k interactions among loci

```{r preferential interaction matrix}
IM_preferential <- function(n, k){
  
  IM_preferential <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_preferential[row(IM_preferential) == col(IM_preferential)] <- 1 # fitness value at locus i always depends on allele at locus i itself
  
  while (sum(IM_preferential) < n*(k+1)) {
    
    # pick a random row
    row <- sample(n ,1)
    
    # pick a column (weighted by how many '1's the column already contains)
    column <- sample(n, 1, prob = colSums(IM_preferential))
    
    IM_preferential[row, column] <- 1
    
    
  }
  
  return(IM_preferential)
  
}

IM_preferential_c <- function(n, c){
  
  IM_preferential <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

  while (sum(IM_preferential) < n*c) {
    
    # pick a random row
    row <- sample(n ,1)
    
    # pick a column (weighted by how many '1's the column already contains)
    column <- sample(n, 1, prob = colSums(IM_preferential))
    
    IM_preferential[row, column] <- 1
    
    
  }
  
  return(IM_preferential)
  
}
  
```

### 2.5) Hierarchical (Rivkin & Siggelkow, 2007)
few loci influence all other loci; the matrix consists of '1's below the diagonal, starting with the ﬁrst column, continuing with the second column, etc., until there are n*k interactions among loci

```{r hierarchical interaction matrix}
IM_hierarchical <- function(n, k){
  
  IM_hierarchical <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_hierarchical[row(IM_hierarchical) == col(IM_hierarchical)] <- 1 # fitness value at locus i always depends on allele at locus i itself
    
    for (i in 1:n){# for each column
      
      for (j in 1:n){# for each row
        
        if (sum(IM_hierarchical) < n*(k+1) & j>i) { # below the diagonal until we get to n*k interactions among loci
          
          IM_hierarchical[j,i] <- 1
        
      }
      
    }
    
  }
  
  return(IM_hierarchical)
  
}

IM_hierarchical_c <- function(n, c){
  
  IM_hierarchical <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

    for (i in 1:n){# for each column
      
      for (j in 1:n){# for each row
        
        if (sum(IM_hierarchical) < n*c & j>=i) { # below and including the diagonal until we get to n*c interactions among loci
          
          IM_hierarchical[j,i] <- 1
        
      }
      
    }
    
  }
  
  return(IM_hierarchical)
  
}

```

### 2.6) Dependent (Rivkin & Siggelkow, 2007)
few loci are dependent on all other loci

```{r dependent interaction matrix}
IM_dependent <- function(n, k){
  
  IM_dependent <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s
  IM_dependent[row(IM_dependent) == col(IM_dependent)] <- 1 # fitness value at locus i always depends on allele at locus i itself
  
for (i in n:1){# for each row
      
      for (j in n:1){# for each column
        
        if (sum(IM_dependent) < n*(k+1) & i>j) { # below the diagonal until we get to n*k interactions among loci
          
          IM_dependent[i,j] <- 1
        
      }
      
    }
    
  }
  
  
  return(IM_dependent)
  
}

IM_dependent_c <- function(n, c){
  
  IM_dependent <- matrix(n, n, data = rep(0, n^2)) # matrix with dimensions n x n, initiated with 0s

for (i in n:1){# for each row
      
      for (j in n:1){# for each column
        
        if (sum(IM_dependent) < n*c & i>=j) { # below and including the diagonal until we get to n*c interactions among loci
          
          IM_dependent[i,j] <- 1
        
      }
      
    }
    
  }
  
  
  return(IM_dependent)
  
}

```

## 3) Creating the landscape
### 3.1) generate genotypes
generate all possible genotypes; alleles are encoded by numbers (1, 2, ..., a)

```{r generate genotypes}
generate_genotypes <- function(a, n){
  
  genotypes <- gtools::permutations(a, n, c(1:a), repeats = TRUE)
  return(genotypes)
  
}
```

### 3.2) generate fitness contributions
a^(k+1+c*s) different allele combinations per locus for each locus

```{r draw fitness contributions}

# Welch & Waxman drew from a normal distribution
generate_alleles <- function(n, k, a, c, s, fit_mean, fit_sd){
  
  allelic_vals <- matrix(c(rnorm(n*a^(k+1+c*s), fit_mean, fit_sd)), ncol = n) 
  return(allelic_vals)
  
}

# Kauffman drew from a uniform distribution
generate_alleles_unif <- function(n, k, a, c, s, fit_min, fit_max){
  
  allelic_vals <- matrix(c(runif(n*a^(k+1+c*s), fit_min, fit_max)), ncol = n)
  return(allelic_vals)
  
}
```

### 3.3) Calculate the genotype fitness
```{r calculate genotype fitness}

# fitness calaculation like Kauffman & Weinberger (1989) and Kauffman & Johnson (1991)
fitness_calc <- function(gene_vector){
  
  W = (1/length(gene_vector))*sum(gene_vector) 
  return(W)
  
}

# Welch & Waxman used a multiplicative model of fitness (ln fitness)
fitness_calc_mult <- function(gene_vector){
  
  W = exp(sum(gene_vector))
  return(W)
  
}

```

### 3.4) Generate intergenomic interaction matrices
To automate the generation of the interaction matrices for intergenomic interactions
```{r IM_c}

build_IMc <- function(IM = c("R", "M", "P", "H", "D"), # type of matrix
                      n, # number of loci in each genome
                      c, # number of loci interacting
                      s, # number of species interacting
                      s_tot){ # total number of species in the community
  
  # determine how to construct the intergenomic epistatic interactions and what kind of interaction matrix (IM) to use 
  if (IM == "R"){# for Random matrix
    
    matrix_c <- IM_random_c
     
  } else if (IM == "M"){# for Modular matrix
    
    matrix_c <- IM_modular_c
    
  } else if (IM == "N"){# for nearest neighbour matrix
    
    matrix_c <- IM_neighbour_c
    
  } else if (IM == "P"){# for preferential interaction matrix
    
    matrix_c <- IM_preferential_c
    
  } else if (IM == "H"){# for hierarchical interaction matrix
    
    matrix_c <- IM_hierarchical_c
    
  } else if (IM == "D"){# for dependent interaction matrix
    
    matrix_c <- IM_dependent_c
    
  }
  
  matrix_c_species <- list()
  
  # for each species in the system
  for (i in 1:s_tot){
    
    # I need IM to describe the interaction between a focal species and each of its interaction partners
    matrix_temp <- list() # I collect this in a temporary list
    
    # so, for each interaction partner:
    for (j in 1:s){
      
      # generation intergenomic interaction matrix
      matrix_temp[[j]] <- matrix_c(n,c)
      
    }
    
    matrix_merged <- do.call(cbind, matrix_temp) # merge all IM by column (rows = loci in focal genome and then columns = all the loci in all the interacting species)
     matrix_c_species[[i]] <- matrix_merged
    
  }
  
  return(matrix_c_species)
  
}

```

### 3.4) Generate intragenomic interaction matrices
```{r IM_k}

build_IMk <- function(IM = c("R", "M", "N", "P", "H", "D"),
                      n,
                      k,
                      s,
                      s_tot){

  # determine how to construct the intragenomic epistatic interactions and what kind of interaction matrix (IM) to use 
  if (IM == "R"){# for Random matrix
    
    matrix_k <- IM_random
     
  } else if (IM == "M"){# for Modular matrix
    
    matrix_k <- IM_modular
    
  } else if (IM == "N"){# for nearest neighbour matrix
    
    matrix_k <- IM_neighbour
    
  } else if (IM == "P"){# for preferential interaction matrix
    
    matrix_k <- IM_preferential
    
  } else if (IM == "H"){# for hierarchical interaction matrix
    
    matrix_k <- IM_hierarchical
    
  } else if (IM == "D"){# for dependent interaction matrix
    
    matrix_k <- IM_dependent
    
  }
  
  matrix_k_species <- list()
  
  # for each species in the system
  for (i in 1:s_tot){
    
      # generation intragenomic interaction matrix
      matrix_k_species[[i]] <- matrix_k(n,k)

  }
  
  return(matrix_k_species)

}


```

### 3.5) Generate NKC(S) landscape
```{r generate landscape}
build_landscape <- function(IM_k, # intragenomic epistasis matrices
                            IM_c, # intergenomic epistasis matrices
                            fitness_contrib = c("N", "U"), # way to draw fitness contributions (normal vs. uniform distribution)
                            fitness_calculation = c("KJ", "WW"), # way to calculate fitness (according to Kauffman & Johnson or Welch & Waxman) 
                            n, # nb of loci
                            k, # nb of interacting loci within a species
                            a, # nb of alleles per locus
                            c, # nb of interacting loci between species
                            s, # nb of species interacting
                            s_tot, # total number of species in the species
                            fit_mean, # mean of fintess distribution when drawing from a normal distribution, or min fitness when drawing from a uniform distribution
                            fit_sd) # sd of fintess distribution when drawing from a normal distribution, or max fitness when drawing from a uniform distribution
  {
  

  # how to generate allelic values? (normal distribution vs uniform distribution)
  if (fitness_contrib == "N"){# for drawing from a normal distribution
    
    alleles_generate <- generate_alleles
    
  } else if (fitness_contrib == "U") {
    
    alleles_generate <- generate_alleles_unif
    
  }
  
  # how to calculate fitness?
  if (fitness_calculation == "KJ"){
    
    fitness_calculate <- fitness_calc 
    
  } else if (fitness_calculation == "WW"){
    
    fitness_calculate <- fitness_calc_mult 
    
  }
  
  # generate all possible genotypes (this is the same for all species here, since we assume that all species have the same n, a and c)
  genotypes <- generate_genotypes(a,n+(s*n)) # I generate "extended genotypes" to include the s*n sites in other species that are relevant for calculating fitness (but only n sites actually contribute to a genotype's fitness, if that makes sense?)
  
  # generate all possible fitness contributions depending on k epistatic interactions within species and c epistatic interactions with s other species
  h_table_species <- list() # a list with all look up tables for each of the s_tot species; each list item is a look-up table of dimension n x a^(k+1+c*s) for all possible allelic values
  
  # for each species:
  for (i in 1:s_tot){
    
    # generate look-up table with all possible allelic values (dependent on k+1+c*s loci within and between species); dimension n x a^(k+1+c*s) for all possible allelic values
    # each column = 1 locus, each row = different genetic background
    h_table_species[[i]] <- alleles_generate(n, k, a, c, s, fit_mean, fit_sd)
    
  }
  
  # now that we generated all the fitness contributions and know all the genetic interactions in the system
  
  # keeping track of "extended" genotypes, their fitness contributions and total calculated fitness
  genotype_table_species <- list()
  
  # for each species:
  for (i in 1:s_tot){
    
    # table to keep track of all fitness vectors
    fitnesses <- NULL
    
    # for each genotype (remember, all species have the same genotype encoding; it's just the fitness values and epistatic interactions that differ)
    for (j in 1:nrow(genotypes)){
      
      # keep track of fitness contribution at each locus (h)
      h_vector <- NULL # vector of fitness contributions per locus for each genotype
      
      # for each genotype we look up the fitness contribution (h) at each locus; h depends on k+1+c*s loci 
      # for each locus:
      for (l in 1:n) { # skipping the placeholer "k" to iterate over, since k is used as a variable in the model
        
        # which loci determine the fitness contribution at this locus?
        interesting_loci_k <- which(IM_k[[i]][l, ] != 0) # based on the intragenomic IM
        interesting_loci_c <- which(IM_c[[i]][l,] != 0) # based on intergenomic IM
        
        interesting_loci <- c(interesting_loci_k, interesting_loci_c+n) # list of all loci that have an affect on the fitness contribution

        # what are the alleles present at the loci we're interested in for this given genotype?
        alleles <- genotypes[j, interesting_loci]
        
        # let's access the fitness contributions associated with the genetic background
        index <- 1
      
        # for all loci contributing to h:
        for (m in 1:length(alleles)) {
        
        index <- index + (a^((k+1+(s*c))-m))*(alleles[m]-1)
        
        }
      
        # store the fitness contributions in a vector
        h_vector <- cbind(h_vector, h_table_species[[i]][index,l])
      
      }
      
      # construct a table with all information relating to the fitness contributions etc.
      fitness_genotype <- cbind(h_vector, fitness_calculate(h_vector)) # calculate the total fitness (W) for each genotype
      fitnesses <- rbind(fitnesses, fitness_genotype) # compilation of individual fitness contributions (h) and calculated fitness values (W)
      
    }
    
    # combine the genotype table and the fitness table
    genotype_table_species[[i]] <- cbind(genotypes, fitnesses) # combining the genotype table and the fitness table
    # columns 1 to n represent the allelic values at each locus in the genome of the focal species
    # columns n+1 to n+(s*n) represent the allelic values at each locus in the genomes of the interacting species (= intergenomic epistasis)
    # columns n+(s*n)+1 to 2n+(s*n) are the fitness contributions per locus (h) for loci in the genome of the focal species
    # column 2n+(s*n)+1 is the calculated total fitness for each genotype taking into account all genetic interactions
    
    # store as data frame for ease of proceeding
    genotype_table_species[[i]] <- as.data.frame(genotype_table_species[[i]])
    colnames(genotype_table_species[[i]])[(n+1):(n+(s*n))] <- paste0("P.", 1:(s*n)) # loci of partner species ("P"); if s = 0, this will be overwritten in next steps
    colnames(genotype_table_species[[i]])[1:n] <- paste0("F.", 1:n) # loci of focal species ("F")
    colnames(genotype_table_species[[i]])[(n+(s*n)+1):(2*n+(s*n))] <- paste0("h.", 1:n) # fitness contributions of each locus
    colnames(genotype_table_species[[i]])[2*n+(s*n)+1] <- "fitness"
    
    # adding peak rank information
    genotype_table_species[[i]]$rank <- dplyr::dense_rank(-genotype_table_species[[i]]$fitness) # highest fitness will have rank 1
    
  }
  
  return(genotype_table_species)

}

```

## 4) Exploring the landscape topology
### 4.1) Find neighbors one step away
This will include mutations that can happen within a focal species genome but also mutations that can happen in the genome of one of the interacting species

```{r neighbour search}

findNeighbours <- function(landscape, 
                           startIndex, # focal genotype to start neighbour search with
                           nb_loci){ 
  
  # focal genotype
  temp_genotype <- landscape[startIndex,]
  
  differences <- c(rep(0, length(landscape[,1]))) # vector with entries for each genotype to keep track of difference to reference
    
  for (loc in 1:nb_loci){
    
    for (geno in 1:length(landscape[,1])){
      
      if (landscape[geno,loc] != temp_genotype[loc]){ # if both genotypes don't carry the same allele...
        
        differences[geno] <- differences[geno] + 1 # ... I mark a difference in my vector
        
      }
      
    }
    
  }
  
  neighbours <- landscape[which(differences == 1), ]
  
  return(neighbours)
  
}
```

### 4.2) visualise the landscape

```{r landscape visualisation}
visual_landscape <- function(landscape, n, c, s) {
  
  landscape_df <- data.frame(landscape)
  landscape_df$genotypeID <- c(1:(length(landscape[,1]))) # assign ID to each genotype
  
  # count the nb. of mutations separating each genotype from the reference
  landscape_df$mutations <- 0
  
  for (i in 1:length(landscape_df[,1])) {
    
    landscape_df$seq[i] <- paste(paste(landscape_df[i, 1:n], collapse = ""), "-", c(paste(landscape_df[i, (n+1):(n+s*n)], collapse = ""))) # alternate way of representing the genotypes; this is purely visual information to plot

    for (locus in 1:(n+s*n)) {
      
      if (landscape_df[i,locus] != 1) {
        
        landscape_df$mutations[i] <- landscape_df$mutations[i] + 1
        
      }
      
    }
    
  }
  
  # classify the possible paths on the landscape (genotype to genotype)
  # connecting pairs of genotypes to link them on the landscape visualisation; each individual pair will get an ID number
  graph_df <- NULL
  pair <- 1
  
  # for each genotype
  for (i in 1:length(landscape_df[,1])) {
    
    # compute the list of neighbours for the focal genotype
    neighbours <- as.data.frame(findNeighbours(landscape_df, i, (n+s*n)))
    
    # assign ID numbers to focal genotype + neighbours; all pairs get individual IDs
    for (j in 1:length(neighbours[,1])) {
      
      # assign ID to focal genotype and add it to the data frame
      landscape_df[i, "group"] <- pair
      
      # assign the same ID to one of its neighbours and add it to the data frame
      neighbours[j, "group"] <- pair
      
      # check whether this neighbour is connected through a mutation within the genome (intra) or between the genomes (inter)
      if (paste(neighbours[j, 1:n], collapse = "") == paste(landscape_df[i, 1:n], collapse = "")){
        
         landscape_df[i, "mut"] <- "inter"
         neighbours[j, "mut"] <- "inter"
        
      } else {
        
        landscape_df[i, "mut"] <- "intra"
         neighbours[j, "mut"] <- "intra"
        
      }
      
      graph_df <- rbind(graph_df, landscape_df[i, ])
      graph_df <- rbind(graph_df, neighbours[j, ])
      
      
      pair <- pair + 1
      
    }
    
  }
  
  names(graph_df)[3*n+1] <- "fitness"
  graph_df$genotypeID <- as.factor(graph_df$genotypeID)
  
  return(graph_df)
  
}
```

## 5) Adaptive walks
three possible ways:
- greedy walk   -> move to the neighbour with the highest fitness
- random fitter -> move to a random neighbour with higher fitness
- proportional  -> probability to move to another genotype is weighted by the fitness differences

```{r adaptive walk}
adaptive_walk_R <- function(landscape, # landscape(s) on which to perform walk(s)
                          walk = c("greedy", "random", "prop"), # types of walks
                          n,
                          c,
                          s, # nb. of species interacting
                          s_tot, # total number of species in the system
                          IM_c,
                          R, # "rounds of mutation to introduce asymmetry between species
                          lambda_R, # if R = NA -> lambda of Poisson distribution
                          start = c("WT", "R", "S"), # choosing starting genotype
                          desired_start, # if I want to start at a specific genotype (start = "S")
                          max_steps=100) # max. number of steps on the landscape before I interrupt
{
  
  # turn landscapes into data frames
  landscape_df <- list()
  
  for (i in 1:s_tot){
    
    landscape_df[[i]] <- as.data.frame(landscape[[i]])
    landscape_df[[i]]$ID <- 1:nrow(landscape_df[[i]]) # give genotypes an ID (we need this for our neighbour search later on)
    
  }
  
  # define start genotypes
  walks <- list() # this is a list to keep track of the genotypes during the adaptive walk
  
  if (start == "WT"){
    
    for (i in 1:s_tot){
      
      walks[[i]] <- landscape_df[[i]][1,] # this will give us the starting point of the adaptive walk
      walks[[i]]$step <- 0 # to signalise that this is the initial genotype
      walks[[i]]$focal <- NA # later I can store the ID of the focal species (the species that is mutating)
      
    }
    
  }
  
  if (start == "R"){
    
    random_seq <- sample(a, n*s_tot, replace = TRUE) # I'm just generating a random sequencing to start with; I guess right now this only works if all species interact with each other (s = s_tot-1)
    
    for (i in 1:s_tot){
      temp_seq <- NA # here I will store the sequence for each species; this will be updated as the positions of loci in the sequence will change for each species (focal species always at the start of the sequence)

      temp_seq[1:n] <- random_seq[(1+(i-1)*n):(n+(i-1)*n)] # these are the allelic values for the loci in the focal species
      temp_seq[(n+1):(n+n*s)] <- random_seq[-c((1+(i-1)*n):(n+(i-1)*n))] # these are the allelic values for the loci in the interacting species

      walks[[i]] <- landscape_df[[i]][rowSums(mapply(`==`, landscape_df[[i]][, 1:(n+n*s)], temp_seq)) == n+n*s,] # this will give us the starting point of the adaptive walk; I'm matching the entry in the genotype table to the random sequence I generated earlier here
      walks[[i]]$step <- 0 # to signalise that this is the initial genotype
      walks[[i]]$focal <- NA # later I can store the ID of the focal species (the species that is mutating)
      
    }
    
  }
  
  if (start == "S"){
    
    specific_seq <- desired_start # this is to plug in the desired starting sequence
    
    for (i in 1:s_tot){
      temp_seq <- NA # here I will store the sequence for each species; this will be updated as the positions of loci in the sequence will change for each species (focal species always at the start of the sequence)

      temp_seq[1:n] <- specific_seq[(1+(i-1)*n):(n+(i-1)*n)] # these are the allelic values for the loci in the focal species
      
      if(s !=0){
       
        temp_seq[(n+1):(n+n*s)] <- specific_seq[-c((1+(i-1)*n):(n+(i-1)*n))] # these are the allelic values for the loci in the interacting species 
        
      }

      walks[[i]] <- landscape_df[[i]][rowSums(mapply(`==`, landscape_df[[i]][, 1:(n+n*s)], temp_seq)) == n+n*s,] # this will give us the starting point of the adaptive walk; I'm matching the entry in the genotype table to the desired sequence
      walks[[i]]$step <- 0 # to signalise that this is the initial genotype
      walks[[i]]$focal <- NA # later I can store the ID of the focal species (the species that is mutating)
      
    }
    
  }
  
  # set current genotype
  current_genotypes <- walks # this will be updated as we navigate the landscape(s)
  
  # count steps
  step <- 1
  
  # if R = NA
  if(is.na(R)){
    
    repeat_steps <- rpois(1, lambda = lambda_R)
    
  } 
  
  if(!is.na(R)) {
    
    repeat_steps <- R
    
  }
  
  # repeat adaptive steps until a local maximum or the maximum allowed number of steps are reached
  repeat { for (sp in c(rep(1, repeat_steps),2)){ # allow species 1 more rounds of mutation
    # find neighbours and choose those with higher fitness
    # need to determine how many there are; 
    # - if 0, end simulation?; 
    # - if 1, go there directly; 
    # - if >1, do true adaptive walk depending on method of choice
    
      # find neighbours one step away
    neighbours <- findNeighbours(landscape_df[[sp]], current_genotypes[[sp]]$ID, n)
    
    # but now I only want those neighbours that are accessible through mutation within a genome
    true_neighbours <- neighbours[which(rowSums(mapply(`==`, neighbours[, (n+1):(n+s*n)], current_genotypes[[sp]][, c((n+1):(n+s*n))])) == n*s),] # checking each allelic value at loci of interacting species against reference ("current genotype") and only accept, if all columns match
    
    if(s == 0){ # if there is no interaction, all neighbours are true neighbours
      
      true_neighbours <- neighbours
      
    }
    
    # filter those with higher or equal fitness than the current genotype
    neighbours_fitter <- true_neighbours[which(true_neighbours[, 2*n+(s*n)+1] >= current_genotypes[[sp]][, 2*n+(s*n)+1]),]
    
    new_genotypes <- list()
    
    # first option - already at peak; then stay
    if (nrow(neighbours_fitter) == 0) {
      
      new_genotypes[[sp]] <- current_genotypes[[sp]][, c(1:(2*n+n*s+3))] # stay - maybe something will happen in another species; will update step and focal species at the end of this go
      
      # or there is only one high-fitness neighbor - go there directly
    } else if (nrow(neighbours_fitter) == 1) {
      
      new_genotypes[[sp]] <- neighbours_fitter
      
      # or there are several high-fitness neighbors, choose fittest neighbour
    } else if (walk == "greedy"){
      
      new_genotypes[[sp]] <- neighbours_fitter[which(neighbours_fitter[, 2*n+(s*n)+1] == max(neighbours_fitter[,2*n+(s*n)+1])),]
      
      # choose random neighbour
    } else if (walk == "random"){
      
      new_genotypes[[sp]] <- neighbours_fitter[sample(1:nrow(neighbours_fitter), 1),]
      
      # or choose neighbour with certain probability weighted by how much more fit they are                                  
    } else if (walk == "prop"){
      
      new_genotypes[[sp]] <- neighbours_fitter[sample(1:nrow(neighbours_fitter), 1,
                                       prob=(mapply('-', neighbours_fitter[, 2*n+(s*n)+1], current_genotypes[[sp]][2*n+(s*n)+1]))/abs(sum(mapply('-', neighbours_fitter[, 2*n+(s*n)+1], current_genotypes[[sp]][2*n+(s*n)+1])))),]
    }
    
    # save step on landscape in my table to track the walk
    walks[[sp]] <- rbind(walks[[sp]], cbind(new_genotypes[[sp]], step, focal = sp))
    
    # after every step, update fitness of the other species since that might have changed due to intergenomic epistasis
    for (j in c(1:s_tot)[-sp]){
      
      # update (meta)genotype
      new_genotypes[[j]] <- landscape_df[[j]][which(rowSums(mapply(`==`, landscape_df[[j]][, 1:n], current_genotypes[[j]][, 1:n])) == ncol(landscape_df[[j]][, 1:n]) & rowSums(mapply(`==`, landscape_df[[j]][, (n+1):(n+s*n)], new_genotypes[[sp]][, 1:n])) == ncol(landscape_df[[j]][, (n+1):(n+s*n)])),] # the loci of the focal genome are keeping the same allelic values as before, but the rest are updated in case there was a mutation in one of the other species
      
      if(s == 0){
        
        new_genotypes[[j]] <- current_genotypes[[j]][, 1:(2*n+3)] # no need to change anything if there is no interaction
        
      }
      
      # store movement on landscape (or lack thereof I guess lol)
      walks[[j]] <- rbind(walks[[j]], cbind(new_genotypes[[j]], step, focal = sp ))
      
    }
    
    # set up next step on landscape
    current_genotypes <- new_genotypes
    step <- step+1
    
    # stop if fitness for *all* species didn't change since last step
    stop_test <- NULL
    
    # will take at least three steps to compare current fitness to two different time points in the past 
    if (step > 3){
    
    for (sp in 1:s_tot){
      
      # comparing fitness between now and last step as well as comparing fitness with now and two steps ago
      if (walks[[sp]][nrow(walks[[sp]]), 2*n+(s*n)+1] == walks[[sp]][nrow(walks[[sp]])-1, 2*n+(s*n)+1] &
          walks[[sp]][nrow(walks[[sp]]), 2*n+(s*n)+1] == walks[[sp]][nrow(walks[[sp]])-2, 2*n+(s*n)+1] &
          walks[[sp]][nrow(walks[[sp]]), 2*n+(s*n)+1] == walks[[sp]][nrow(walks[[sp]])-3, 2*n+(s*n)+1]) { # hmmm, if I have more species, maybe I'll have to check if fitness changed since the focal species was last allowed to mutate itself; for now two steps back works because of s_tot = 2; if I introduce larger asymmetries with R this also needs to be updated?
        
        stop_test <- c(stop_test, 1)
        
      }
      
    }
    
    }
    
    
    if (length(stop_test) == s_tot) { break }
      
  }
    
    if (length(stop_test) == s_tot) { break }
   
    # stop after a number of steps if no optimum was reached (usually only an issue if there is cycling)
    if (step > max_steps) { break } 
    
    # if R = NA; redraw repeat_steps
  if(is.na(R)){
    
    repeat_steps <- rpois(1, lambda = lambda_R)
    
  }
     
  }
  
  return(walks)
  
}

```


## 6) Visualise the system (coupled landscapes and walks)
```{r visualise systems and adaptive walks}

visualise_system <- function(landscapes,
                             n,
                             c,
                             s,
                             s_tot){
  
  visual_scapes_df <- NULL
  
  # combining all data frames into one, so I can plot the fitness landscape of each species as a separate facet 
  for (i in 1:s_tot){
    
    temp <- visual_landscape(landscapes[[i]], 
                                     n, 
                                     c, 
                                     s)
    temp$species <- i # to differentiate between species
    
    visual_scapes_df <- rbind(visual_scapes_df, temp)
    
  }
  
  ggplot(visual_scapes_df,
       aes(x = mutations,
           y = fitness)) +
  geom_line(data = visual_scapes_df,
            aes(group = group,
                linetype = mut),
            color="grey70",
            linewidth = 1) +
  geom_label(label = visual_scapes_df$seq,
             linewidth = 0.6, # thickness of label border in mm
             size = 4.5, # size of label in mm
             fontface = "bold" # bold font
             ) +
  scale_linetype_manual(breaks = c("intra", "inter"),
                        values = c("solid", "dashed"))+
  xlab("Hamming distance from reference metagenotype") +
  ylab("Fitness") +
    facet_wrap(~species,
               labeller = labeller(species = 
    c("1" = "Focal species",
      "2" = "Partner species"))) +
  theme_bw() +
  theme(legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(linewidth = 0.8, linetype = 2),
        panel.grid.minor.x = element_blank(),
        text = element_text(size = 15),
        axis.text = element_text(size = 13))
  
}

visualise_walks <- function(adaptive_walks,
                            n,
                            s,
                            s_tot,
                            landscapes){
  
  
  walks_df <- NULL

  # combining all data frames into one, so I can plot the adaptive walk of each species as a separate facet 
  for (i in 1:s_tot){
    
    temp <- as.data.frame(adaptive_walks[[i]])
    temp$peak <- unique(landscapes[[i]][which(landscapes[[i]][, 2*n+(s*n)+1] == max(landscapes[[i]][, 2*n+(s*n)+1])), 2*n+(s*n)+1]) # I also want to plot the fitness of the global fitness peak 
    
    temp$species <- i # to differentiate between species
    
    walks_df <- rbind(walks_df, temp)

  }
  
  colnames(walks_df)[2*n+(s*n)+1] <- "Fitness"

  ggplot(walks_df,
       aes(x = step,
           y = Fitness)) +
  geom_line(linewidth = 0.8) +
    geom_hline(aes(yintercept = peak),
               linetype = "dashed",
               col = "firebrick3",
               linewidth = 0.9) +
    facet_wrap(~species,
               labeller = labeller(species = 
    c("1" = "Species 1",
      "2" = "Species 2"))) +
  theme_bw()
  
}

```

## 7) Replicate the adaptive walks
````{r replicates}
assess_peaks_R <- function(n, # nb. of loci
                         k, # nb. of loci interacting within genome (intragenomic epistasis)
                         a, # nb. of alleles at each locus
                         c, # nb. of loci interacting between genomes (intergenomic epistasis)
                         s, # nb. of species interacting
                         R, # number of mutation rounds for sp 1
                         lambda_R, # if R = NA -> lambda of Poisson distribution
                         s_tot, # total nb. of species in system
                         IM_ks, # list of intragenomic epistasis interaction matrices
                         IM_cs, # list of intergenomic epistasis interaction matrices
                         scape_reps, # nb. of replicates to generate fitness landscapes for each combination of IM_k and IM_c
                         fitness_contrib, # how fitness contributions are drawn 
                         fitness_calculation, # how fitness is calculated for genotypes
                         fit_mean, # mean of fitness distribution when drawing from a normal distribution, or min fitness when drawing from a uniform distribution
                         fit_sd, # sd of fitness distribution when drawing from a normal distribution, or max fitness when drawing from a uniform distribution
                         walk_reps, # nb. of replicates of adaptive walks on a given landscape
                         walk_type, # vector of types of adaptive walks (random, greedy, prop)
                         walk_start, # starting genotype of adaptive walk (random, starting at reference type/WT, or starting at a specified sequence)
                         start_seqs, # if I want to specify where the adaptive walk starts -> supplied as a list
                         max_steps) # max nb. of steps in adaptive walk
{

# get number of replicates for intragenomic epistasis interaction matrix
  IM_k_reps <- length(IM_ks)
 
# get number of replicates for intergenomic epistasis interaction matrix
  IM_c_reps <- length(IM_cs)

# for each combination of IM_k and IM_c make the landscapes and perform the random walks
total_walks <- list()
scapes_replicated <- list() # to store the landscapes

peaks_df <- NULL #I want to save the endpoints of all walks in one df
total_walks[[IM_k_reps]] <- list()
total_walks[[IM_k_reps]][[IM_c_reps]] <- list()

for (k_rep in 1:IM_k_reps) {
  
  IM_k <- IM_ks[[k_rep]]
  
  scapes_replicated[[k_rep]] <- list()
  
  for (c_rep in 1:IM_c_reps){
    
    IM_c <- IM_cs[[c_rep]]
    
    scapes_replicated[[k_rep]][[c_rep]] <- list() # I want to save the landscapes for each combination of k and c matrix
  
    # create the landscapes
  for (scape_rep in 1:scape_reps) {
    
    scapes_replicated[[k_rep]][[c_rep]][[scape_rep]] <- build_landscape(IM_k,
                             IM_c, 
                fitness_contrib,
                fitness_calculation,
                n,
                k,
                a,
                c,
                s,
                s_tot,
                fit_mean,
                fit_sd)
    
    # identify the global fitness peak for each landscape
    global_peaks <- list()
    
    for (global_peak in 1:s_tot){
      
      global_peaks[[global_peak]] <-  max(scapes_replicated[[k_rep]][[c_rep]][[scape_rep]][[global_peak]][,2*n+s*n+1])
      
    }
    
    # for each landscape perform the adaptive walks
    total_walks[[k_rep]][[c_rep]][[scape_rep]] <- list()
    
    for (walking in walk_type) { # perform different types of adaptive walks for the same landscape to have the direct comparison e.g. random walk vs greedy walk

    walks_replicated <- list()
    
    # perform the walk
    for (walk_rep in 1:walk_reps) {
      
      if (walk_start == "S"){
        
        desired_start <- start_seqs[[walk_rep %% length(start_seqs) + 1]]
          
      }
      
      walks_replicated[[walk_rep]] <- adaptive_walk_R(scapes_replicated[[k_rep]][[c_rep]][[scape_rep]], 
              walk = walking,
              n,
              c,
              s,
              s_tot, 
              IM_c,
              R,
              lambda_R,
              start = walk_start,
              desired_start,
              max_steps)
      
      # store the desired information (endpoint of walk and simulation parameters)
      for (species in 1:s_tot) {
        
        start_seq <- paste(paste(walks_replicated[[walk_rep]][[species]][1, c(1:n)], collapse = ""), "-", c(paste(walks_replicated[[walk_rep]][[species]][1, c((n+1):(n+n*s))], collapse = ""))) # I want to save the starting point of each adaptive walk
        
        # and then keep track of the end points of each walk here; I am saving the end point of the walk alongside the simulation parameters
        peaks_df <- rbind(peaks_df, cbind(walks_replicated[[walk_rep]][[species]][nrow(walks_replicated[[walk_rep]][[species]]),], data.frame(k_rep, 
                                                                                                                                              c_rep, 
                                                                                                                                              scape_rep, 
                                                                                                                                              walk_rep, 
                                                                                                                                              species,
                                                                                                                                              n,
                                                                                                                                              k,
                                                                                                                                              a,
                                                                                                                                              c,
                                                                                                                                              s,
                                                                                                                                              R, 
                                                                                                                                              walk_start,
                                                                                                                                              walking,
                                                                                                                                              start_seq,
                                                                                                                                              global_peak = global_peaks[[species]])))
        
      }
      
    }
    
    total_walks[[k_rep]][[c_rep]][[scape_rep]][[match(walking, walk_type)]] <- walks_replicated # store adaptive walk for each landscape replicate for the different types of adaptive walk
    
    }
  
  }
    
  }
  
}

return(list(peaks_df, # store the dataset with endpoint stats of adaptive walks
            IM_ks, # interaction matrices of intragenomic interactions
            IM_cs, # interaction matrices of intergenomic interactions
            scapes_replicated, # all the fitness landscapes
            total_walks)) # the individual adaptive walks

}

## if I want to rerun simulations on already existing fitness landscapes:
assess_peaks_R_input <- function(n, # nb. of loci
                         k, # nb. of loci interacting within genome (intragenomic epistasis)
                         a, # nb. of alleles at each locus
                         c, # nb. of loci interacting between genomes (intergenomic epistasis)
                         s, # nb. of species interacting
                         R, # number of mutation rounds for sp 1
                         lambda_R, # if R = NA -> lambda of Poisson distribution
                         s_tot, # total nb. of species in system
                         IM_ks, # list of intragenomic epistasis interaction matrices
                         IM_cs, # list of intergenomic epistasis interaction matrices
                         landscapes, # give previously generated fitness landscapes as an input here
                         scape_reps, # nb. of replicates to generate fitness landscapes for each combination of IM_k and IM_c
                         walk_reps, # nb. of replicates of adaptive walks on a given landscape
                         walk_type, # vector of types of adaptive walks (random, greedy, prop)
                         walk_start, # starting genotype of adaptive walk (random, starting at reference type/WT, or starting at a specified sequence)
                         start_seqs, # if I want to specify where the adaptive walk starts -> supplied as a list
                         max_steps) # max nb. of steps in adaptive walk
{

# get number of replicates for intragenomic epistasis interaction matrix
  IM_k_reps <- length(IM_ks)
 
# get number of replicates for intergenomic epistasis interaction matrix
  IM_c_reps <- length(IM_cs)

# for each combination of IM_k and IM_c make the landscapes and perform the random walks
total_walks <- list()
scapes_replicated <- landscapes # to store the landscapes

peaks_df <- NULL #I want to save the endpoints of all walks in one df
total_walks[[IM_k_reps]] <- list()
total_walks[[IM_k_reps]][[IM_c_reps]] <- list()

for (k_rep in 1:IM_k_reps) {
  
  IM_k <- IM_ks[[k_rep]]
  
  for (c_rep in 1:IM_c_reps){
    
    IM_c <- IM_cs[[c_rep]]
    
    # create the landscapes
  for (scape_rep in 1:scape_reps) {
    
    # identify the global fitness peak for each landscape
    global_peaks <- list()
    
    for (global_peak in 1:s_tot){
      
      global_peaks[[global_peak]] <-  max(scapes_replicated[[k_rep]][[c_rep]][[scape_rep]][[global_peak]][,2*n+s*n+1])
      
    }
    
    # for each landscape perform the adaptive walks
    total_walks[[k_rep]][[c_rep]][[scape_rep]] <- list()
    
    for (walking in walk_type) { # perform different types of adaptive walks for the same landscape to have the direct comparison e.g. random walk vs greedy walk

    walks_replicated <- list()
    
    # perform the walk
    for (walk_rep in 1:walk_reps) {
      
      if (walk_start == "S"){
        
        desired_start <- start_seqs[[walk_rep %% length(start_seqs) + 1]]
          
      }
      
      walks_replicated[[walk_rep]] <- adaptive_walk_R(scapes_replicated[[k_rep]][[c_rep]][[scape_rep]], 
              walk = walking,
              n,
              c,
              s,
              s_tot, 
              IM_c,
              R,
              lambda_R,
              start = walk_start,
              desired_start,
              max_steps)
      
      # store the desired information (endpoint of walk and simulation parameters)
      for (species in 1:s_tot) {
        
        start_seq <- paste(paste(walks_replicated[[walk_rep]][[species]][1, c(1:n)], collapse = ""), "-", c(paste(walks_replicated[[walk_rep]][[species]][1, c((n+1):(n+n*s))], collapse = ""))) # I want to save the starting point of each adaptive walk
        
        # and then keep track of the end points of each walk here; I am saving the end point of the walk alongside the simulation parameters
        peaks_df <- rbind(peaks_df, cbind(walks_replicated[[walk_rep]][[species]][nrow(walks_replicated[[walk_rep]][[species]]),], data.frame(k_rep, 
                                                                                                                                              c_rep, 
                                                                                                                                              scape_rep, 
                                                                                                                                              walk_rep, 
                                                                                                                                              species,
                                                                                                                                              n,
                                                                                                                                              k,
                                                                                                                                              a,
                                                                                                                                              c,
                                                                                                                                              s,
                                                                                                                                              R,
                                                                                                                                              walk_start,
                                                                                                                                              walking,
                                                                                                                                              start_seq,
                                                                                                                                              global_peak = global_peaks[[species]])))
        
      }
      
    }
    
    total_walks[[k_rep]][[c_rep]][[scape_rep]][[match(walking, walk_type)]] <- walks_replicated # store adaptive walk for each landscape replicate for the different types of adaptive walk
    
    }
  
  }
    
  }
  
}

return(list(peaks_df, # store the dataset with endpoint stats of adaptive walks
            IM_ks, # interaction matrices of intragenomic interactions
            IM_cs, # interaction matrices of intergenomic interactions
            scapes_replicated, # all the fitness landscapes
            total_walks)) # the individual adaptive walks

}


````

## 8) test runs
```{r test landscape}

# set.seed(1313)
# 
# n = 2
# k = 1
# a = 2
# c = 1
# s = 1
# s_tot = 2
# 
# IM_c <- build_IMc(IM = "R",
#                       n,
#                       c,
#                       s,
#                       s_tot)
# 
# IM_k <- build_IMk(IM = "R",
#                       n,
#                       k,
#                       s,
#                       s_tot)
# 
# testscape <- build_landscape(IM_k,
#                              IM_c,
#                 fitness_contrib = "N",
#                 fitness_calculation = "KJ",
#                 n,
#                 k,
#                 a,
#                 c,
#                 s,
#                 s_tot,
#                 fit_mean = 0,
#                 fit_sd = 0.5)
# 
# system_fig <- visualise_system(testscape,
#                  n,
#                  c,
#                  s,
#                  s_tot)
# 
# walk_test <- adaptive_walk_R(testscape,
#               walk = "random",
#               n,
#               c,
#               s,
#               s_tot,
#               IM_c,
#               start = c("R"),
#               max_steps=100)
# 
# walks_fig <- visualise_walks(walk_test,
#                 n,
#                 s,
#                 s_tot,
#                 testscape)

```


# (B) NKsea model (NK seascapes)
In order to have a comparison for multidimensional fitness mappings and have an abiotic equivalent to dynamic environments created by the species interactions, we implement a seascapes equivalent repurposing the NKC functions 

Let's imagine we create a s*n seascape equivalent to the NKC model, to start off we can imagine that n loci are relevant for each abiotic environment (essentially each of s_tot species is translated into a different abiotic environment). We can reinterpret the K from the NKC model as genetic interactions between loci relevant for a given abiotic environment and C as genetic interactions between loci relevant for different abiotic environments. Additionally, we could toggle the pleiotropy in the system by changing the number of loci that contribute to environment-specific fitness (but note that this is not actually implemented here... yet!)

## 1) Variable explanations
n = baseline nb. of haploid loci contributing to environment-specific fitness
a = nb. of possible alleles per locus
k = nb. of interactions between loci encoding for the same environment-specific fitness; k <= n+p-1
env = nb. of environments a species experiences
env_tot = total nb. of abiotic environments in the system
k_e = nb. of interactions between loci encoding for different environment-specific fitness; k_e <= n-p (equivalent to c)
p = nb. of haploid loci contributing to multiple environment-specific fitnesses (= pleiotropic loci)
W_e = environment-specific fitness
h = fitness contributions of each locus
IM = interaction matrix; determines how the loci are linked epistatically

(again, we will assume full symmetry between environments)


## 2) Creating the landscapes
### 2.1) Generate seascapes
```{r NK seascapes}
build_seascape <- function(IM_sea, # seascape intercation matrix
                            fitness_contrib = c("N", "U"), # way to draw fitness contributions (normal vs. uniform distribution)
                            fitness_calculation = c("KJ", "WW"), # way to calculate fitness (according to Kauffman & Johnson or Welch & Waxman) 
                            n, # nb of loci contributing to an environment
                            k, # nb of interacting loci within an environment
                           k_e, # nb of interacting loci between environments
                            a, # nb of alleles per locus
                            env_tot, # total nb. of abiotic environments in the system
                           p, # pleiotropic loci - not implemented yet
                            fit_mean, # mean of fintess distribution when drawing from a normal distribution, or min fitness when drawing from a uniform distribution
                            fit_sd) # sd of fintess distribution when drawing from a normal distribution, or max fitness when drawing from a uniform distribution
  {
  
  env <- env_tot-1

  # how to generate allelic values? (normal distribution vs uniform distribution)
  if (fitness_contrib == "N"){# for drawing from a normal distribution
    
    alleles_generate <- generate_alleles
    
  } else if (fitness_contrib == "U") {
    
    alleles_generate <- generate_alleles_unif
    
  }
  
  # how to calculate fitness?
  if (fitness_calculation == "KJ"){
    
    fitness_calculate <- fitness_calc 
    
  } else if (fitness_calculation == "WW"){
    
    fitness_calculate <- fitness_calc_mult 
    
  }
  
  # generate all possible genotypes 
  genotypes <- generate_genotypes(a,env_tot*n)
  
  # generate all possible fitness contributions depending on k and k_e epistatic interactions
  h_table_env <- list() # a list with all look up tables for each of the env_tot environments; each list item is a look-up table of dimension n*env_tot x a^(k+1+k_e*env) for all possible allelic values
  
  # for each species:
  for (i in 1:env_tot){
    
    # generate look-up table with all possible allelic values (dependent on k+1+k_e*env loci within and between species); dimension n x a^(k+1+k_e*env) for all possible allelic values; here is where the pleiotropy would come in -> (n+p) x a^(...)
    # each column = 1 locus, each row = different genetic background
    h_table_env[[i]] <- alleles_generate(n+p, k, a, k_e, env, fit_mean, fit_sd) # I reuse the NKC function and sub out k_e for c
    
  }
  
  # now that we generated all the fitness contributions and know all the genetic interactions in the system
  
  # keeping track of all genotypes, their fitness contributions and total calculated fitness
  genotype_table_env <- list()
  
  # for each environment:
  for (i in 1:env_tot){
    
    # table to keep track of all fitness vectors
    fitnesses <- NULL
    
    # for each genotype (remember, the genotype encoding is the same in all environments; it's just the fitness values and epistatic interactions that differ)
    for (j in 1:nrow(genotypes)){
      
      # keep track of fitness contribution at each locus (h)
      h_vector <- NULL # vector of fitness contributions per locus for each genotype
      
      # for each genotype we look up the fitness contribution (h) at each locus; h depends on k+1+k_e*env loci 
      # for each locus:
      for (l in (1+n*(i-1)):(n+n*(i-1))) { # skipping the placeholder "k" to iterate over, since k is used as a variable in the model; this would have to be adjusted for p != 0
        
        # which loci determine the fitness contribution at this locus?
        interesting_loci <- which(IM_sea[l, ] != 0) # based on the seascape interaction matrix

        # what are the alleles present at the loci we're interested in for this given genotype?
        alleles <- genotypes[j, interesting_loci]
        
        # let's access the fitness contributions associated with the genetic background
        index <- 1
      
        # for all loci contributing to h:
        for (m in 1:length(alleles)) {
        
        index <- index + (a^((k+1+(env*k_e))-m))*(alleles[m]-1)
        
        }
      
        # store the fitness contributions in a vector
        
        
        h_vector <- cbind(h_vector, h_table_env[[i]][index, (l %% n)+1])
      
      }
      
      # construct a table with all information relating to the fitness contributions etc.
      fitness_genotype <- cbind(h_vector, fitness_calculate(h_vector)) # calculate the total fitness (W) for each genotype
      fitnesses <- rbind(fitnesses, fitness_genotype) # compilation of individual fitness contributions (h) and calculated fitness values (W)
      
    }
    
    # combine the genotype table and the fitness table
    genotype_table_env[[i]] <- cbind(genotypes, fitnesses) # combining the genotype table and the fitness table
    # columns 1 to n represent the allelic values at each locus in the genome encoding fitness in environment 1
    # columns n+1 to n+(env*n) represent the allelic values at each locus in the genome encoding fitness in environment 2,...
    # columns n+(env*n)+1 to 2n+(env*n) are the fitness contributions per locus (h) for loci in the genome encoding fitness in environment 1
    # column 2n+(env*n)+1 is the calculated total fitness for each genotype taking into account all genetic interactions
    
    # store as data frame for ease of proceeding
    genotype_table_env[[i]] <- as.data.frame(genotype_table_env[[i]])
    colnames(genotype_table_env[[i]])[(n+1):(n+(env*n))] <- paste0("E2.", 1:(env*n)) # loci for environment 2; if env_tot = 1, this will be overwritten in next steps
    colnames(genotype_table_env[[i]])[1:n] <- paste0("E1.", 1:n) # loci for environment 1
    colnames(genotype_table_env[[i]])[(n+(env*n)+1):(2*n+(env*n))] <- paste0("h.", 1:n) # fitness contributions of each locus
    colnames(genotype_table_env[[i]])[2*n+(env*n)+1] <- "fitness"
    
    # adding peak rank information
    genotype_table_env[[i]]$rank <- dplyr::dense_rank(-genotype_table_env[[i]]$fitness) # highest fitness will have rank 1
    
  }
  
  landscape_combined <- genotype_table_env[[1]][, 1:(n*env_tot)] # one single data frame that shows rank and fitness for both environments
  
  for (e in 1:env_tot) {
    
    cols <- c(paste0("E", e, ".fitness"), paste0("E", e, ".rank"))
    landscape_combined[, cols] <- genotype_table_env[[e]][, c("fitness", "rank")]
    
  }
  
  return(landscape_combined)

}

```

### 2.2) Turn NKC landscapes to NK seascape
For the ultimate comparison of dynamic fitness landscapes, I take the NKC landcsapes for two species and turn them into a single species seascape with two environment-associated traits
````{r}

NKC_to_NKsea <- function(landscape_list, # NKC landscapes to transform; stored as list with landscapes[[k_rep]][[c_rep]][[scape_rep]][[species]]
                         env_tot, # total number of environments (previously species)
                         k_reps = 1, # for the NKC model I only use on type of IM_K at a time (for now...); if there are more I need to change thow I iterate over these
                         c_reps,
                         scape_reps,
                         n){
  
  seascape_list <- list()
  
  
  for (k_rep in 1:k_reps){
    
    for (c_rep in 1:c_reps){
      
      seascape_list[[c_rep]] <- list() # right now the number of IM_cs is equal to seascape interaction matrices... but as mentioned above this does not have to be true 
      
      for (scape_rep in 1:scape_reps){
        
          seascape_list[[c_rep]][[scape_rep]] <- landscape_list[[k_rep]][[c_rep]][[scape_rep]][[1]][, c(1:(n*env_tot), (n*(env_tot+1)+1), (n*(env_tot+1)+2))]
          colnames(seascape_list[[c_rep]][[scape_rep]])[c((n*(env_tot)+1), (n*(env_tot)+2))] <- c("E1.fitness", "E1.rank")
          
          for (species in 2:env_tot) {
            
            temp_landscape <-  landscape_list[[k_rep]][[c_rep]][[scape_rep]][[species]]
            temp_landscape <- temp_landscape[with(temp_landscape, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1; needs to be adjusted for more species and or loci; but doing this quick and dirty for now OB-)
            colnames(temp_landscape)[c((n*(env_tot+1)+1), (n*(env_tot+1)+2))] <- c("E2.fitness", "E2.rank")
            
            seascape_list[[c_rep]][[scape_rep]] <- cbind(seascape_list[[c_rep]][[scape_rep]], temp_landscape[, c("E2.fitness", "E2.rank")])
            
            
          }
          
          
        }
        
      }
      
      
      
  }
  
 return(seascape_list) # list of translated seascapes    
    
  }


````

## 3) Adaptive walks on seascape = adaptive voyage?
````{r adaptive voyage}

adaptive_walk_sea <- function(landscape_df, # landscape on which to perform walk(s) -> the shape of the fitness landscape can change across abiotic environments
                          walk = c("greedy", "random", "prop"), # types of walks
                          n,
                          env_tot, # total number of environments in the system
                          change, # "rounds of mutation" spent in the same abiotic environment (rate of envrionmental change)
                          lambda_change, # if change = NA -> lambda of Poisson distribution
                          start = c("WT", "R", "S"), # choosing starting genotype
                          desired_start, # if I want to start at a specific genotype (start = "S")
                          max_steps=100) # max. number of steps on the landscape before I interrupt
{
  
  env <- env_tot - 1
  
  landscape_df$ID <- 1:nrow(landscape_df) # give genotypes an ID (we need this for our neighbour search later on)
  
  # define start genotypes
  walks <- NULL # this is a dataframe to keep track of the genotypes during the adaptive walk
  
  if (start == "WT"){
    
walks <- landscape_df[1,] # this will give us the starting point of the adaptive walk; presumably we always start in environment 1
      walks$step <- 0 # to signalise that this is the initial genotype
      walks$env <- 1 # starting in environment 1

  }
  
  if (start == "R"){
    
    random_seq <- sample(a, n*env_tot, replace = TRUE) # I'm just generating a random sequencing to start with; I guess right now this only works if a species experiences all abiotic environments (env = env_tot-1)
    
      walks <- landscape_df[rowSums(mapply(`==`, landscape_df[, 1:(n+n*env)], temp_seq)) == n+n*env,] # this will give us the starting point of the adaptive walk; I'm matching the entry in the genotype table to the random sequence I generated earlier here; we always start in environment 1
      walks$step <- 0 # to signalise that this is the initial genotype
      walks$env <- 1 # starting in environment 1
      
    }
  
  
  if (start == "S"){
    
    specific_seq <- desired_start # this is to plug in the desired starting sequence
    
      walks <- landscape_df[rowSums(mapply(`==`, landscape_df[, 1:(n+n*env)], specific_seq)) == n+n*env,] # this will give us the starting point of the adaptive walk; I'm matching the entry in the genotype table to the desired sequence
      walks$step <- 0 # to signalise that this is the initial genotype
      walks$env <- 1 # starting in environment 1
      
    }
    
  # set current genotype
  current_genotypes <- walks # this will be updated as we navigate the landscape(s)
  
  # count steps
  step <- 1
  
  # if change = NA
  if(is.na(change)){
    
    repeat_env <- rpois(1, lambda = lambda_change)
    
  } 
  
  if(!is.na(change)) {
    
    repeat_env <- change
    
  }
  
  # repeat adaptive steps until a local maximum or the maximum allowed number of steps are reached
  repeat { for (e in c(rep(1, repeat_env),2)){ # to switch between environments
    # find neighbours and choose those with higher fitness
    # need to determine how many there are; 
    # - if 0, end simulation?; 
    # - if 1, go there directly; 
    # - if >1, do true adaptive walk depending on method of choice
    
      # find neighbours one step away
    neighbours <- findNeighbours(landscape_df, current_genotypes$ID, n*env_tot)
    
    # filter those with higher fitness than the current genotype
    neighbours_fitter <- neighbours[which(neighbours[, paste0("E", e, ".fitness")] > current_genotypes[, paste0("E", e, ".fitness"),]),] # NKC was greater or equal to...
    
    new_genotypes <- list()
    
    # first option - already at peak; then stay
    if (nrow(neighbours_fitter) == 0) {
      
      new_genotypes <- current_genotypes[, c(1:(env_tot*n+env_tot*2+1))] # stay - maybe something will happen in another environment
      
      # or there is only one high-fitness neighbor - go there directly
    } else if (nrow(neighbours_fitter) == 1) {
      
      new_genotypes <- neighbours_fitter
      
      # or there are several high-fitness neighbors, choose fittest neighbour
    } else if (walk == "greedy"){
      
      new_genotypes <- neighbours_fitter[which(neighbours_fitter[, paste0("E", e, ".fitness")] == max(neighbours_fitter[,paste0("E", e, ".fitness")])),]
      
      # choose random neighbour
    } else if (walk == "random"){
      
      new_genotypes <- neighbours_fitter[sample(1:nrow(neighbours_fitter), 1),]
      
      # or choose neighbour with certain probability weighted by how much more fit they are                                  
    } else if (walk == "prop"){
      
      new_genotypes <- neighbours_fitter[sample(1:nrow(neighbours_fitter), 1,
                                       prob=(mapply('-', neighbours_fitter[, paste0("E", e, ".fitness")], current_genotypes[paste0("E", e, ".fitness")]))/abs(sum(mapply('-', neighbours_fitter[, paste0("E", e, ".fitness")], current_genotypes[paste0("E", e, ".fitness")])))),]
    }
    
    # save step on landscape in my table to track the walk
    walks <- rbind(walks, cbind(new_genotypes, step, env = e))
    
    # set up next step on landscape
    current_genotypes <- new_genotypes
    step <- step+1
    
    # stop if fitness for *all* species didn't change since last step
    stop_test <- NULL
    
    # will take at least three steps to compare current fitness to two different time points in the past 
    if (step > 3){
    
    for (e in 1:env_tot){
      
      # comparing fitness between now and last step as well as comparing fitness with now and two steps ago
      if (walks[nrow(walks), paste0("E", e, ".fitness")] == walks[nrow(walks)-1, paste0("E", e, ".fitness")] &
          walks[nrow(walks), paste0("E", e, ".fitness")] == walks[nrow(walks)-2, paste0("E", e, ".fitness")] &
          walks[nrow(walks), paste0("E", e, ".fitness")] == walks[nrow(walks)-3, paste0("E", e, ".fitness")]) { # should probably be more dynamic to account for different rates of environmental changes
        
        stop_test <- c(stop_test, 1)
        
      }
      
    }
    
    }
    
    
    if (length(stop_test) == env_tot) { break }
      
  }
    
    if (length(stop_test) == env_tot) { break }
   
    # stop after a number of steps if no optimum was reached (usually only an issue if there is cycling)
    if (step > max_steps) { break } 
    
    # if R = NA; redraw repeat_env
  if(is.na(change)){
    
    repeat_env <- rpois(1, lambda = lambda_change)
    
  }
     
  }
  
  return(walks)
  
}

````

## 4) Replicate the adaptive walks on the seascape
````{r replicates seascapes}
assess_peaks_sea <- function(n, # nb. of loci
                         k, # nb of interacting loci within an environment
                           k_e, # nb of interacting loci between environments
                         a, # nb. of alleles at each locus
                         p, # pleiotropic loci - not implemented yet
                         change, # "rounds of mutation" spent in the same abiotic environment (rate of envrionmental change)
                          lambda_change, # if change = NA -> lambda of Poisson distribution
                         env_tot, # total number of environments in the system
                         IM_seas, # interaction matrix
                         scape_reps, # nb. of replicates to generate fitness landscapes for each combination of IM_k and IM_c
                         fitness_contrib, # how fitness contributions are drawn 
                         fitness_calculation, # how fitness is calculated for genotypes
                         fit_mean, # mean of fitness distribution when drawing from a normal distribution, or min fitness when drawing from a uniform distribution
                         fit_sd, # sd of fitness distribution when drawing from a normal distribution, or max fitness when drawing from a uniform distribution
                         walk_reps, # nb. of replicates of adaptive walks on a given landscape
                         walk_type, # vector of types of adaptive walks (random, greedy, prop)
                         walk_start, # starting genotype of adaptive walk (random, starting at reference type/WT, or starting at a specified sequence)
                         start_seqs, # if I want to specify where the adaptive walk starts -> supplied as a list
                         max_steps) # max nb. of steps in adaptive walk
{
  
  env <- env_tot # for now assuming a species experiences every abiotic environment in the system

# get number of replicates for interaction matrix
  IM_sea_reps <- length(IM_seas)
 
# for each combination of IM_k and IM_c make the landscapes and perform the random walks
total_walks <- list()
scapes_replicated <- list()

peaks_df <- NULL #I want to save the endpoints of all walks in one df
total_walks[[IM_sea_reps]] <- list()

for (sea_rep in 1:IM_sea_reps) {
  
  IM_sea <- IM_seas[[sea_rep]]
  
  scapes_replicated[[sea_rep]] <- list()
  
    # create the landscapes
  for (scape_rep in 1:scape_reps) {
    
    scapes_replicated[[sea_rep]][[scape_rep]] <- build_seascape(IM_sea,
                fitness_contrib,
                fitness_calculation,
                n,
                k,
                k_e,
                a,
                env_tot,
                p,
                fit_mean,
                fit_sd)
    
    # identify the global fitness peak for each landscape
    global_peaks <- list()
    
    for (e in 1:env_tot){
      
      global_peaks[[e]] <-  max(scapes_replicated[[sea_rep]][[scape_rep]][, paste0("E", e, ".fitness")])
      
    }
    
    # for each landscape perform the adaptive walks
    total_walks[[sea_rep]][[scape_rep]] <- list()
    
    for (walking in walk_type) { # perform different types of adaptive walks for the same landscape to have the direct comparison e.g. random walk vs greedy walk

    walks_replicated <- list()
    
    # perform the walk
    for (walk_rep in 1:walk_reps) {
      
      if (walk_start == "S"){
        
        desired_start <- start_seqs[[walk_rep %% length(start_seqs) + 1]]
          
      }
      
      walks_replicated[[walk_rep]] <- adaptive_walk_sea(scapes_replicated[[sea_rep]][[scape_rep]], 
              walk = walking,
              n,
              env_tot, 
              change,
              lambda_change,
              start = walk_start,
              desired_start,
              max_steps)
      
      # store the desired information (endpoint of walk and simulation parameters)
      start_seq <- paste(walks_replicated[[walk_rep]][1, c(1:(n*env_tot))], collapse = "") # I want to save the starting point of each adaptive walk
        
        # and then keep track of the end points of each walk here; I am saving the end point of the walk alongside the simulation parameters
        peaks_df <- rbind(peaks_df, cbind(walks_replicated[[walk_rep]][nrow(walks_replicated[[walk_rep]]),], data.frame(sea_rep,
                                                                                                                                              scape_rep, 
                                                                                                                                              walk_rep, 
                                                                                                                                              n,
                                                                                                                                              k,
                                                                                                                                              k_e,
                                                                                                                                              a,
                                                                                                                                              env_tot,
                                                                                                                                              walk_start,
                                                                                                                                              walking,
                                                                                                                                              start_seq,
                                                                                                                                              global_peak_E1 = global_peaks[[1]],
                                                                                                                                              global_peak_E2 = global_peaks[[2]])))
        
      
      
    }
    
    total_walks[[sea_rep]][[scape_rep]][[match(walking, walk_type)]] <- walks_replicated # store adaptive walk for each landscape replicate for the different types of adaptive walk
    
    }
    
  }
  
}

return(list(peaks_df, # store the dataset with endpoint stats of adaptive walks
            IM_seas, # interaction matrices 
            scapes_replicated, # all the fitness landscapes
            total_walks)) # the individual adaptive walks

}

## if I want to rerun simulations on already existing fitness seascapes:
assess_peaks_sea_input <- function(n, # nb. of loci
                         k, # nb of interacting loci within an environment
                           k_e, # nb of interacting loci between environments
                         a, # nb. of alleles at each locus
                         p, # pleiotropic loci - not implemented yet
                         change, # "rounds of mutation" spent in the same abiotic environment (rate of envrionmental change)
                          lambda_change, # if change = NA -> lambda of Poisson distribution
                         env_tot, # total number of environments in the system
                         IM_seas, # interaction matrix
                         seascapes, # input the seascapes to perform adaptive walks on
                         scape_reps, # nb. of replicates to generate fitness landscapes for each combination of IM_k and IM_c
                         walk_reps, # nb. of replicates of adaptive walks on a given landscape
                         walk_type, # vector of types of adaptive walks (random, greedy, prop)
                         walk_start, # starting genotype of adaptive walk (random, starting at reference type/WT, or starting at a specified sequence)
                         start_seqs, # if I want to specify where the adaptive walk starts -> supplied as a list
                         max_steps) # max nb. of steps in adaptive walk
{
  
  env <- env_tot # for now assuming a species experiences every abiotic environment in the system

# get number of replicates for interaction matrix
  IM_sea_reps <- length(IM_seas)
 
# for each combination of IM_k and IM_c make the landscapes and perform the random walks
total_walks <- list()
scapes_replicated <- seascapes # we are importing the landscapes we want to use

peaks_df <- NULL #I want to save the endpoints of all walks in one df
total_walks[[IM_sea_reps]] <- list()

for (sea_rep in 1:IM_sea_reps) {
  
  IM_sea <- IM_seas[[sea_rep]]
  
    # create the landscapes
  for (scape_rep in 1:scape_reps) {

    # identify the global fitness peak for each landscape
    global_peaks <- list()
    
    for (e in 1:env_tot){
      
      global_peaks[[e]] <-  max(scapes_replicated[[sea_rep]][[scape_rep]][, paste0("E", e, ".fitness")])
      
    }
    
    # for each landscape perform the adaptive walks
    total_walks[[sea_rep]][[scape_rep]] <- list()
    
    for (walking in walk_type) { # perform different types of adaptive walks for the same landscape to have the direct comparison e.g. random walk vs greedy walk

    walks_replicated <- list()
    
    # perform the walk
    for (walk_rep in 1:walk_reps) {
      
      if (walk_start == "S"){
        
        desired_start <- start_seqs[[walk_rep %% length(start_seqs) + 1]]
          
      }
      
      walks_replicated[[walk_rep]] <- adaptive_walk_sea(scapes_replicated[[sea_rep]][[scape_rep]], 
              walk = walking,
              n,
              env_tot, 
              change,
              lambda_change,
              start = walk_start,
              desired_start,
              max_steps)
      
      # store the desired information (endpoint of walk and simulation parameters)
      start_seq <- paste(walks_replicated[[walk_rep]][1, c(1:(n*env_tot))], collapse = "") # I want to save the starting point of each adaptive walk
        
        # and then keep track of the end points of each walk here; I am saving the end point of the walk alongside the simulation parameters
        peaks_df <- rbind(peaks_df, cbind(walks_replicated[[walk_rep]][nrow(walks_replicated[[walk_rep]]),], data.frame(sea_rep,
                                                                                                                                              scape_rep, 
                                                                                                                                              walk_rep, 
                                                                                                                                              n,
                                                                                                                                              k,
                                                                                                                                              k_e,
                                                                                                                                              a,
                                                                                                                        change,
                                                                                                                                              env_tot,
                                                                                                                                              walk_start,
                                                                                                                                              walking,
                                                                                                                                              start_seq,
                                                                                                                                              global_peak_E1 = global_peaks[[1]],
                                                                                                                                              global_peak_E2 = global_peaks[[2]])))
        
      
      
    }
    
    total_walks[[sea_rep]][[scape_rep]][[match(walking, walk_type)]] <- walks_replicated # store adaptive walk for each landscape replicate for the different types of adaptive walk
    
    }
    
  }
  
}

return(list(peaks_df, # store the dataset with endpoint stats of adaptive walks
            IM_seas, # interaction matrices 
            scapes_replicated, # all the fitness landscapes
            total_walks)) # the individual adaptive walks

}
````
