---
title: "NKC_exploration"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_knit$set(root.dir = "~/OneDrive - Universitaet Bern/NKC_project/R_scripts/") # set directory
```

# Set up workspace
```{r libraries}
rm (list = ls())

library(ggplot2) # for plotting
library(dplyr) # for constructing the data sets
library(gghalves) # for plotting mixed boxplots with points
library(ggtext) # to get different colour axis titles

library(ggraph) # for plotting networks -> adaptive walks representation
library(igraph) # for plotting networks -> adaptive walks representation

library(ggarrow) # to plot individual cycles

library(ggpubr) # to arrange multiple figures

# load NKC functions
source(knitr::purl("NKC(S).Rmd", quiet=TRUE)) # to get the landscape visualisation functions for example

# load data of simulations
load("peaks_total5") 

```

# 1.) Exploratory plots
```{r}
### some exploratory plots

# how many species reach the global peak (0/1/2)
ggplot(peaks_summarised,
        aes(y = prop_reached,
            x = interaction(peaked, n, k, c),
            fill = walking)) +
     geom_boxplot() +
     theme_bw()

# when does cycling occur?
ggplot(peaks_summarised,
        aes(y = prop_cycled,
            x = interaction(peaked, n, k, c),
            fill = walking)) +
     geom_boxplot() +
     theme_bw()

# how often does cycling occur?
ggplot(peaks_summarised_cycles,
        aes(y = prop_cycles,
            x = interaction(peaked, n, k, c),
            fill = walking)) +
     geom_boxplot() +
     theme_bw()

ggplot(peaks_summarised2[peaks_summarised$cycle_count > 0,],
        aes(y = prop_cycled,
            x = interaction(n, k, c),
            fill = walking)) +
     geom_boxplot() +
     theme_bw()

# individual replicates reaching peak
ggplot(peaks_summarised,
        aes(y = prop_reached,
            x = interaction(peaked, n, k, c),
            col = walking)) +
     geom_jitter() +
     theme_bw()

# how many steps in the adaptive walks?
ggplot(peaks_total[peaks_total$reached == TRUE,],
       aes(y = step,
           x = interaction(n, k, c),
           col = walking,
           shape = as.factor(species))) +
  geom_jitter() +
  theme_bw()

ggplot(peaks_total,
       aes(y = step,
           x = interaction(n, k, c),
           col = walking,
           shape = as.factor(species))) +
  geom_jitter() +
  theme_bw()


```

# 2.) Plots for manuscript
```{r}
# main theme for all my figures
fig_theme <- theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        )

#capabilities("cairo") # I think this was to check whether I could save my pdfs with a special unicode character; but I no longer remember... sorry :-(

```

## Fig. 2 - fitness landscape example; R^2 version
This figure shows us the two-dimensional fitness mapping for all the metagenotype -> each metagenotype can correspond to a different fitness rank for the two species
```{r}
# recoding fitness landscapes; 
## in my model the alleles are encoded as 1 and 2, but I would different alleles for the two species to better distinguish them (differences in metagenotypes should be easier to spot this way)

scape_sp1 <- peaks_nkcs_2111[[4]][[2]][[10]][[1]] # take desired landscape replicate for species 1 = "focal species"

# recode alleles for focal species 
scape_sp1[scape_sp1$F.1 == 1, "F.1"] <- "a" 
scape_sp1[scape_sp1$F.1 == 2, "F.1"] <- "A"
scape_sp1[scape_sp1$F.2 == 1, "F.2"] <- "a"
scape_sp1[scape_sp1$F.2 == 2, "F.2"] <- "A"

# recode alleles for partner species
scape_sp1[scape_sp1$P.1 == 1, "P.1"] <- "b"
scape_sp1[scape_sp1$P.1 == 2, "P.1"] <- "B"
scape_sp1[scape_sp1$P.2 == 1, "P.2"] <- "b"
scape_sp1[scape_sp1$P.2 == 2, "P.2"] <- "B"

# rename columns, so I can combine the landscapes of both species next
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

# take the corresponding fitness landscape of species 2 in the chosen species pair
scape_sp2 <- peaks_nkcs_2111[[4]][[2]][[10]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine landscaps of sp1 and sp2
scapes_combined <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(scapes_combined)[c(9,10)] <- c("fitness_sp2", "rank_sp2") # adjust column names

# get the metagenotypes, so I can plot them; this is just for text in the plot
for (i in 1:16){
  
  scapes_combined$seq[i] <- paste(paste(scapes_combined[i, c("F.1", "F.2")], collapse = ""), "-", c(paste(scapes_combined[i, c("P.1", "P.2")], collapse = "")))
  
}

scapes_combined$background <- paste0(scapes_combined$P.1, scapes_combined$P.2) # genotype of sp2
scapes_combined$gen <- paste0(scapes_combined$F.1, scapes_combined$F.2) # genotype of sp1

# now I use my function from the NKC(S) code file to infer which metagenotypes are one-mutation step neighbours
visual_test_df <- visual_landscape(scapes_combined,
                 n = 2,
                  c = 1,
                 s = 1) # this is how I get the transitions between metagenotypes

# now I plot
lanscape_Rsqrd <- ggplot(visual_test_df,
       aes(x = rank_sp1,
           y = rank_sp2)) +
  geom_line(data = visual_test_df[visual_test_df$mut == "intra",],
            aes(group = group,
                linetype = mut,
                col = background),
            linewidth = 0.75) +
  geom_line(data = visual_test_df[visual_test_df$mut == "inter",],
            aes(group = group,
                linetype = mut),
            col = "grey",
            linewidth = 0.5) +
  geom_label(label = visual_test_df$seq,
             aes(col = background),
             linewidth = 0.6, # thickness of label border in mm
             size = 4.5, # size of label in mm
             fontface = "bold" # bold font
             ) +
  scale_x_continuous(breaks = c(1:16),
                     name = "Fitness rank focal species") +
  scale_y_continuous(breaks = c(1:16),
                     name = "Fitness rank partner species") +
  scale_colour_manual(values = c("dodgerblue", "darkblue", "slategrey", "purple"))+
  scale_linetype_manual(breaks = c("intra", "inter"),
                        values = c("solid", "dashed"))+
  ylab("Fitness rank partner species") +
  theme_classic() +
  fig_theme

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 19,
       height = 17,
       filename = "lanscape_Rsqrd_NKC_211_2_30.pdf",
       plot = lanscape_Rsqrd)

## versions of this figure I used in a presentation showing how to go from one-dimensional fitness mapping to two-dimensional fitness mapping
# lanscape_Rsqrd_sp1 <- ggplot(visual_test_df[visual_test_df$background == "bb",],
#        aes(x = rank_sp1,
#            y = rank_sp2)) +
#   geom_line(data = visual_test_df[visual_test_df$mut == "intra" &
#                                     visual_test_df$background == "bb",],
#             aes(group = group,
#                 linetype = mut,
#                 col = background),
#             linewidth = 0.75) +
#   geom_line(data = visual_test_df[visual_test_df$mut == "inter" &
#                                     visual_test_df$background == "bb",],
#             aes(group = group,
#                 linetype = mut),
#             col = "grey",
#             linewidth = 0.5) +
#   geom_label(label = visual_test_df[visual_test_df$background == "bb", "seq"],
#              aes(col = background),
#              linewidth = 0.6, # thickness of label border in mm
#              size = 4.5, # size of label in mm
#              fontface = "bold" # bold font
#              ) +
#   scale_x_continuous(breaks = c(1:16),
#                      name = "Fitness rank focal species",
#                      limits = c(1,16)) +
#   scale_y_continuous(breaks = c(1:16),
#                      name = "Fitness rank partner species",
#                      limits = c(1,16)) +
#   scale_colour_manual(values = c("dodgerblue", "darkblue", "slategrey", "purple"))+
#   scale_linetype_manual(breaks = c("intra", "inter"),
#                         values = c("solid", "dashed"))+
#   ylab("Fitness rank partner species") +
#   theme_classic() +
#   fig_theme
# 
# ggplot(visual_test_df[visual_test_df$gen == "Aa",],
#        aes(x = rank_sp1,
#            y = rank_sp2)) +
#   geom_line(data = visual_test_df[visual_test_df$mut == "intra" &
#                                     visual_test_df$gen == "Aa",],
#             aes(group = group,
#                 linetype = mut,
#                 col = background),
#             linewidth = 0.75) +
#   geom_line(data = visual_test_df[visual_test_df$mut == "inter" &
#                                     visual_test_df$gen == "Aa",],
#             aes(group = group,
#                 linetype = mut),
#             col = "grey",
#             linewidth = 0.5) +
#   geom_label(label = visual_test_df[visual_test_df$gen == "Aa", "seq"],
#              aes(col = background),
#              linewidth = 0.6, # thickness of label border in mm
#              size = 4.5, # size of label in mm
#              fontface = "bold" # bold font
#              ) +
#   scale_x_continuous(breaks = c(1:16),
#                      name = "Fitness rank focal species",
#                      limits = c(1,16)) +
#   scale_y_continuous(breaks = c(1:16),
#                      name = "Fitness rank partner species",
#                      limits = c(1,16)) +
#   scale_colour_manual(values = c("dodgerblue", "darkblue", "slategrey", "purple"))+
#   scale_linetype_manual(breaks = c("intra", "inter"),
#                         values = c("solid", "dashed"))+
#   ylab("Fitness rank partner species") +
#   theme_classic() +
#   fig_theme
# 
# ggsave(path = "../Figures/",
#        device = "pdf",
#        units = c("cm"),
#        width = 19,
#        height = 17,
#        filename = "lanscape_Rsqrd_NKC_211_2_30_sp1.pdf",
#        plot = lanscape_Rsqrd_sp1)
# 
# lanscape_R_sp1 <- ggplot(visual_test_df[visual_test_df$background == "bb",],
#        aes(x = rank_sp1,
#            y = background)) +
#   geom_label(label = visual_test_df[visual_test_df$background == "bb", "gen"],
#              aes(col = background),
#              linewidth = 0.6, # thickness of label border in mm
#              size = 4.5, # size of label in mm
#              fontface = "bold" # bold font
#              ) +
#   scale_x_continuous(breaks = c(2,16),
#                      labels = c("high",  "low"),
#                      name = "Fitness focal species",
#                      limits = c(2,16)) +
#   scale_colour_manual(values = c("dodgerblue", "darkblue", "slategrey", "purple"))+
#   scale_linetype_manual(breaks = c("intra", "inter"),
#                         values = c("solid", "dashed"))+
#   ylab("") +
#   theme_classic() +
#   fig_theme +
#   theme(axis.text.y = element_blank(),
#         axis.ticks.y = element_blank())
# 
# ggsave(path = "../Figures/",
#        device = "pdf",
#        units = c("cm"),
#        width = 19,
#        height = 5,
#        filename = "lanscape_R_NKC_211_2_30_sp1.pdf",
#        plot = lanscape_R_sp1)


```

## Fig 3 - Repeatability N = 2
This is the first results figure that shows how many adaptive walks lead to the same outcome on each of our fitness lanscape replicates
```{r}
localrep_N2 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "prop",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_violin(aes(y = prop_cycle,
                  x = rank),
              col = "grey45") +
  geom_jitter(col = "springgreen4",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  geom_jitter(aes(y = prop_cycle,
                  x = rank),
               col = "skyblue",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the mean proportion of cycling/landscape
                  x = rank),
               fun = mean,
               geom = "crossbar",
               linewidth = 0.4,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the median proportion of cycling/landscape
                  x = rank),
               fun = median,
               geom = "point",
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode character
       units = c("cm"),
       width = 26,
       height = 17,
       filename = "localrep_N2.pdf",
       plot = localrep_N2)

```

## Fig 4 - effect of interaction matrices on repeatability
Here we show how patterns of repeatability for C = 1 differ between the different interaction networks used to couple the two species
```{r}

effectIM_N2 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                         peaks_total_ranked_summarised$c == 1 &
                                       peaks_total_ranked_summarised$walking == "prop",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_violin(aes(y = prop_cycle,
                  x = rank),
              col = "grey45") +
  geom_jitter(aes(col = as.factor(c_rep)),
              size = 2.5,
              height = 0.01,
              alpha = 0.5) +
  geom_jitter(aes(y = prop_cycle,
                  x = rank),
               col = "skyblue",
              size = 2.5,
              height = 0.01,
              alpha = 0.5) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the mean proportion of cycling/landscape
                  x = rank),
               fun = mean,
               geom = "crossbar",
               linewidth = 0.4,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the median proportion of cycling/landscape
                  x = rank),
               fun = median,
               geom = "point",
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c_rep ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                     limits = c(0,1)) +
  scale_color_manual(values=c("forestgreen", "limegreen", "olivedrab2", "gold")) + # different colours for the four ineraction networks
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
        legend.position = "none",
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 21,
       filename = "effectIM_N2.pdf",
       plot = effectIM_N2)

```

## Fig 5 - fitness distribution
Here we show which fitness outcomes are the most common, which gives us the expected fitness distribution for each combination of K and C; this figure also shows the cycling probability
```{r}
fitness_dis_N2 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "prop",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_bar(aes(y = after_stat(prop), # proportion of data points at each rank (calculated for each facet)
               group = 1),
           fill = "thistle3") + # across all my groupings
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26, # 30
       height = 17, # 15
       filename = "fitness_dis_N2.pdf",
       plot = fitness_dis_N2)

```

## Fig 6 - correlation-fitness relationship
Next, we show how the correlation of fitness ranks between the species can reveal some trends on how lare the expected fitnes cost of a species is
```{r}

# for this I first need to calculate the correlation of fitness ranks for all fitness landscapes with different combinations of C and K; but I'm only interested in cases with C > 0

# N = 2, K = 0, C = 1
## prep dataframes 
combined_scapes_nkc_201 <- list() # here I store the combined landscapes and the correlation of their fitness ranks
summary_cors_nkc_201 <- NULL # and this is to keep track of the summaries (correlation for each landscape)

for (i in 1:4){ # for each interaction matrix
  
  combined_scapes_nkc_201[[i]] <- list() # prep entry in list for storage
  
for (j in 1:50){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2011[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2011[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 0, 1, i, j))

summary_cors_nkc_201 <- rbind(summary_cors_nkc_201, summary_temp) # combine all stats

combined_scapes_nkc_201[[i]][[j]] <- test_df # save combined fitness landscape; why? not sure tbh
  
}
}

### now repeat for all others

# N = 2, K = 0, C = 2
combined_scapes_nkc_202 <- list()
combined_scapes_nkc_202[[1]] <- list()
summary_cors_nkc_202 <- NULL

for (j in 1:200){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2021[[4]][[1]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2021[[4]][[1]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 2,
                              c_rep = 1,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 0, 2, 1, j))

summary_cors_nkc_202 <- rbind(summary_cors_nkc_202, summary_temp)

combined_scapes_nkc_202[[1]][[j]] <- test_df
  
}

###
combined_scapes_nkc_211 <- list()
summary_cors_nkc_211 <- NULL

for (i in 1:4){ # for each interaction matrix
  
  combined_scapes_nkc_211[[i]] <- list()
  
for (j in 1:50){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2111[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2111[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 1, 1, i, j))

summary_cors_nkc_211 <- rbind(summary_cors_nkc_211, summary_temp)

combined_scapes_nkc_211[[i]][[j]] <- test_df
  
}
}

###
combined_scapes_nkc_212 <- list()
combined_scapes_nkc_212[[1]] <- list()
summary_cors_nkc_212 <- NULL

for (j in 1:200){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2121[[4]][[1]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2121[[4]][[1]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 2,
                              c_rep = 1,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 1, 2, 1, j))

summary_cors_nkc_212 <- rbind(summary_cors_nkc_212, summary_temp)

combined_scapes_nkc_212[[1]][[j]] <- test_df
  
}


#############

# now I combine all the stats across all landscapes into one big data frame
summary_cors <- rbind(summary_cors_nkc_201, summary_cors_nkc_202, summary_cors_nkc_211, summary_cors_nkc_212)

# and I want to link the correlations I just calculated to my results; so I add it so my dataframe, where the adaptive outcomes of both species are combined 

# I'm sure this could be done with an apply function, but alas I am using a for loop
for (i in 1:nrow(peaks_total_ranked2_summarised[, ])){
  
  ID <- peaks_total_ranked2_summarised[i, "landscape_ID" ]
  
  if (ID %in% summary_cors$landscape_ID){
    
    peaks_total_ranked2_summarised[i, "corr_rank" ] <- summary_cors[as.character(summary_cors$landscape_ID) == as.character(ID), "corr"]
    
  }

}

# now, let's plot; since this type of figure is difficult to interpret we only show one of them in the main text and the rest can be found in the supplementary material

# we combine three plots; (i) the results for N = 2, K = 0, C = 1, (ii) an empty plot; here I add our expectations and the categorisation of win/win, Lose/lose, win/lose and cycling in post using Adobe illustrator, and (iii) a distance plot to show the second important feater we observe - how the difference in fitness ranks depends on the fitness rank correlation

# first plot
eco_outcome <- ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank) &
                                                       peaks_total_ranked2_summarised$k == 0 &
                                                       peaks_total_ranked2_summarised$c == 1,],
       aes(x = corr_rank,
           y = rank_sp1)) +
   geom_segment(aes(x = corr_rank, 
      y = rank_sp1, 
      xend = corr_rank, 
      yend = rank_sp2),
      col = "grey40",
      alpha = 0.8) +
  geom_point(col = "forestgreen",
             size = 2,
             aes(alpha = rank_peaked/80)) +
  geom_point(aes(x = corr_rank,
                 y = rank_sp2,
                 alpha = rank_peaked/80),
                 col = "forestgreen",
             size = 2) +
  scale_y_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk") +
  scale_x_continuous(name = "rank correlation(F, P)",
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character

# second plot
blank <- ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank) &
                                                       peaks_total_ranked2_summarised$k == 0 &
                                                       peaks_total_ranked2_summarised$c == 1,],
       aes(x = corr_rank,
           y = rank_sp1)) +
  scale_y_continuous(labels = c("1", "3", "5", "7", "9", "11", "13", "15", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = seq(1, 17, 2),
                   name = "Fitness rank at end of adaptive walk") +
  scale_x_continuous(name = "  ",
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        axis.title.y = element_text(size=17),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


# third plot
distance_plot <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$rank_sp1 != 17 &
                                                         peaks_total_ranked2_summarised$k == 0 &
                                                       peaks_total_ranked2_summarised$c == 1 &
                                        !is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = corr_rank,
           y = abs(rank_sp1-rank_sp2))) +
  geom_point(col = "dodgerblue") +
  geom_smooth(method = "glm") +
  scale_y_continuous(labels = c("0", "2", "4", "6", "8", "10", "12", "14"),
                     breaks = seq(0,14,2),
                     limits = c(0,15),
                   name = "Difference in fitness rank") +
  scale_x_continuous(name = "rank correlation(F, P)",
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        axis.title.y = element_text(size=17),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character

# combined plots
fig_test <- ggpubr::ggarrange(eco_outcome, 
                  ggpubr::ggarrange(blank, distance_plot, nrow = 2),
                  ncol = 2,
                     widths = c(1.35, 1))

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "eco_fig.pdf",
       plot = fig_test)

```

## Fig 7 - cycle investigation
```{r}

# for N = 2, K = 0, C = 1
cycles_nkc_201 <- NULL

c_rep <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 1 & 
                     peaks_total$step == 200 & 
                       peaks_total$walking == "greedy" &
                       peaks_total$species == 1, "c_rep"]

for (i in unique(c_rep)){ # IM replicates
  
  scape_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 1 & 
                              peaks_total$c_rep == i &
                           peaks_total$step == 200 & 
                       peaks_total$walking == "greedy" &
                       peaks_total$species == 1, "scape_rep"]
  
  for (j in unique(scape_reps)) { # fitness landscape replicates
    
    walk_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 1 & 
                              peaks_total$c_rep == i &
                               peaks_total$scape_rep == j &
                           peaks_total$step == 200 & 
                       peaks_total$walking == "greedy" &
                       peaks_total$species == 1, "walk_rep"]
    
    for (l in unique(walk_reps)) {
      
      ranks_sp1 <- unique(peaks_nkcs_2011[[5]][[i]][[j]][[3]][[l]][[1]][c(190:200), "rank"])
      ranks_sp2 <- unique(peaks_nkcs_2011[[5]][[i]][[j]][[3]][[l]][[2]][c(190:200), "rank"])
      
      summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              walk_rep = l,
                              nb_in_cycle_sp1 = length(ranks_sp1), # should be 4?
                              nb_in_cycle_sp2 = length(ranks_sp2), # should be 4?
                              high_rank_sp1 = min(ranks_sp1),
                              high_rank_sp2 = min(ranks_sp2),
                              low_rank_sp1 = max(ranks_sp1),
                              low_rank_sp2 = max(ranks_sp2),
                              var_rank_sp1 = var(ranks_sp1),
                              var_rank_sp2 = var(ranks_sp2),
                              mean_rank_sp1 = mean(ranks_sp1),
                              mean_rank_sp2 = mean(ranks_sp2),
                           landscape_ID = interaction(2, 0, 1, i, j))
      
      cycles_nkc_201 <- rbind(cycles_nkc_201, summary_temp)
      
    }
    
  }
  
}

# for N = 2, K = 1, C = 1
cycles_nkc_211 <- NULL

c_rep <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 1 & 
                     peaks_total$step == 200 & 
                       peaks_total$walking == "prop" &
                       peaks_total$species == 1, "c_rep"]

for (i in unique(c_rep)){ # IM replicates
  
  scape_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 1 & 
                              peaks_total$c_rep == i &
                           peaks_total$step == 200 & 
                       peaks_total$walking == "prop" &
                       peaks_total$species == 1, "scape_rep"]
  
  for (j in unique(scape_reps)) { # fitness landscape replicates
    
    walk_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 1 & 
                              peaks_total$c_rep == i &
                               peaks_total$scape_rep == j &
                           peaks_total$step == 200 & 
                       peaks_total$walking == "prop" &
                       peaks_total$species == 1, "walk_rep"]
    
    for (l in unique(walk_reps)) {
      
      ranks_sp1 <- unique(peaks_nkcs_2111[[5]][[i]][[j]][[3]][[l]][[1]][c(190:200), "rank"])
      ranks_sp2 <- unique(peaks_nkcs_2111[[5]][[i]][[j]][[3]][[l]][[2]][c(190:200), "rank"])
      
      summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              walk_rep = l,
                              nb_in_cycle_sp1 = length(ranks_sp1), # should be 4?
                              nb_in_cycle_sp2 = length(ranks_sp2), # should be 4?
                              high_rank_sp1 = min(ranks_sp1),
                              high_rank_sp2 = min(ranks_sp2),
                              low_rank_sp1 = max(ranks_sp1),
                              low_rank_sp2 = max(ranks_sp2),
                              var_rank_sp1 = var(ranks_sp1),
                              var_rank_sp2 = var(ranks_sp2),
                              mean_rank_sp1 = mean(ranks_sp1),
                              mean_rank_sp2 = mean(ranks_sp2),
                           landscape_ID = interaction(2, 1, 1, i, j))
      
      cycles_nkc_211 <- rbind(cycles_nkc_211, summary_temp)
      
    }
    
  }
  
}

cycles_df <- rbind(cycles_nkc_201)
cycles_df$cycle_ID <- interaction(cycles_df[, c("high_rank_sp1", "high_rank_sp2", "low_rank_sp1", "low_rank_sp2")])

# I want to look at unique cycles (it is possible to have "multiple cycles" because of the specific interactions of networks 1 and 4 )
summary_cycles <-  NULL

for (scape_ID in unique(cycles_df$landscape_ID)){
  
  for (cycle_ID in unique(cycles_df[cycles_df$landscape_ID == scape_ID, "cycle_ID"])) {
    
    temp_df <- cycles_df[cycles_df$landscape_ID == scape_ID &
                                              cycles_df$cycle_ID == cycle_ID, ]
    
    summary_temp <- data.frame(n = 2,
                              k = unique(temp_df$k),
                              c = unique(temp_df$c),
                              c_rep = unique(temp_df$c_rep),
                              scape_ID = scape_ID,
                              cycle_ID = cycle_ID,
                              nb_in_cycle_sp1 = mean(temp_df$nb_in_cycle_sp1),
                              nb_in_cycle_sp2 = mean(temp_df$nb_in_cycle_sp2), 
                              high_rank_sp1 = unique(temp_df$high_rank_sp1),
                              high_rank_sp2 = unique(temp_df$high_rank_sp2),
                              low_rank_sp1 = unique(temp_df$low_rank_sp1),
                              low_rank_sp2 = unique(temp_df$low_rank_sp2),
                              var_rank_sp1 = mean(temp_df$var_rank_sp1),
                              var_rank_sp2 = mean(temp_df$var_rank_sp2),
                              mean_rank_sp1 = mean(temp_df$mean_rank_sp1),
                              mean_rank_sp2 = mean(temp_df$mean_rank_sp2),
                              appeared = nrow(temp_df))
    
    summary_cycles <- rbind(summary_cycles, summary_temp)
    
  }
  
}


ggplot(peaks_total[peaks_total$k == 0 &
                     peaks_total$c == 1 &
                     peaks_total$walking == "greedy" &
                     peaks_total$species == 1,],
       aes(y = step,
           x = interaction(n, k, c))) +
  geom_jitter(col = "forestgreen") +
  ylab("steps") +
  xlab("N-K-C") +
  theme_bw() +
  fig_theme

ggplot(cycles_df,
       aes(y = nb_in_cycle_sp1,
           x = interaction(n,k,c),
           group = interaction(n,k,c))) +
  geom_violin() +
  scale_y_continuous(name = "meteganotypes in cycle",
                      limits = c(0,10),
                      breaks = seq(0,10,2)) +
   xlab("N-K-C") +
  theme_bw() +
  fig_theme


ggplot(summary_cycles,
       aes(y = var_rank_sp2,
           x = interaction(n,k,c),
           group = interaction(n,k,c))) +
  geom_violin() +
  geom_jitter(col = "forestgreen",
              size = 2,
              aes(alpha = appeared/80)) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  scale_y_continuous(name = "var(fitness rank)",
                     limits = c(0,30)) +
   xlab("N-K-C") +
  theme_bw() +
  fig_theme

ggplot(cycles_df,
       aes(y = var_rank_sp2,
           x = interaction(n,k,c),
           group = landscape_ID)) +
  geom_violin() +
  scale_y_continuous(name = "var(fitness rank)") +
   xlab("N-K-C") +
  theme_bw() +
  fig_theme

ggplot(summary_cycles,
       aes(y = high_rank_sp2,
           x = interaction(n,k,c),
           group = interaction(n,k,c))) +
  geom_violin() +
  geom_jitter(col = "forestgreen",
              size = 2,
              aes(alpha = appeared/80)) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  scale_y_continuous(name = "var(fitness rank)",
                     limits = c(1,16)) +
   xlab("N-K-C") +
  theme_bw() +
  fig_theme

ggplot(summary_cycles,
       aes(x = interaction(n,k,c),
           y = low_rank_sp1)) +
  geom_violin(col = "orange") +
  geom_violin(aes(x = interaction(n,k,c),
           y = high_rank_sp1),
              col = "purple") +
  geom_violin(aes(x = interaction(n,k,c),
           y = mean_rank_sp1),
              col = "grey40") +
  geom_jitter(size = 2,
              col = "orange") +
  geom_jitter(aes(x = interaction(n,k,c),
           y = high_rank_sp1),
                size = 2,
              col = "purple") +
  geom_jitter(aes(x = interaction(n,k,c),
           y = mean_rank_sp1),
                size = 2,
              col = "grey40") +
  scale_y_continuous(name = "fitness rank",
                     limits = c(1,16),
                     breaks = seq(1,16,2)) +
  xlab("N-K-C") +
  theme_bw() +
  fig_theme

library(reshape2)
df <- melt(summary_cycles[, c("n", "k", "c", "cycle_ID", "scape_ID", "high_rank_sp1", "high_rank_sp2", "low_rank_sp1", "low_rank_sp2")],  
           id.vars = c("n", "k", "c", "cycle_ID", "scape_ID"), 
           variable.name = 'ranks')

ggplot(df,
       aes(x = interaction(n,k,c),
           y = value,
           group = ranks)) +
  geom_violin(position = position_dodge(0.7),
              aes(col = ranks)) +
  geom_jitter(aes(col = ranks),
              position = position_jitterdodge(0.3)) +
  theme_bw() +
  scale_color_manual(values=c("slateblue", "slateblue", "orange", "orange")) +
  scale_y_continuous(name = "fitness rank",
                     limits = c(1,16),
                     breaks = seq(1,16,2)) +
  xlab("N-K-C") +
  fig_theme



ggplot(summary_cycles,
       aes(x = interaction(n,k,c),
           y = mean_rank_sp1)) +
  geom_violin() +
  geom_jitter(col = "forestgreen") +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  theme_bw() +
  xlab("N-K-C") +
  scale_y_continuous(name = "fitness rank",
                     limits = c(1,16),
                     breaks = seq(1,16,2)) +
  xlab("N-K-C") +
  fig_theme

```




## correlation for R = 2

```{r}

ggplot(peaks_total_ranked2_summarised_R[peaks_total_ranked2_summarised_R$rank_sp1 != 17 &
                                        !is.na(peaks_total_ranked2_summarised_R$corr_rank),],
       aes(x = corr_rank,
           y = rank_peaked/80)) +
  geom_point(col = "forestgreen") +
  facet_grid(c ~ k) +
  scale_y_continuous(limits = c(0,1),
                   name = "repeatability") +
  xlab("correlation(rank F, rank P)") +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme


### C = 2, R = 2
combined_scapes_nkc_202_R <- list()
summary_cors_nkc_202_R <- NULL

for (i in 1:1){ # for each interaction matrix
  
  combined_scapes_nkc_202_R[[i]] <- list()
  
for (j in 1:50){ # for each landscape replicate - should be 200!
  
  scape_sp1 <- peaks_nkcs_2021_R[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2021_R[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 0, 1, i, j))

summary_cors_nkc_202_R <- rbind(summary_cors_nkc_202_R, summary_temp)

combined_scapes_nkc_202_R[[i]][[j]] <- test_df
  
}
}


for (ID in summary_cors_nkc_202_R$landscape_ID){
  
  mean_rank1 <- mean(peaks_total_ranked2_summarised_R[peaks_total_ranked2_summarised_R$landscape_ID == ID, "rank_sp1"])
    mean_rank2 <- mean(peaks_total_ranked2_summarised_R[peaks_total_ranked2_summarised_R$landscape_ID == ID, "rank_sp2"])
    
    summary_cors_nkc_202_R[summary_cors_nkc_201_R$landscape_ID == ID, "mean_rank1"] <- mean_rank1
    summary_cors_nkc_202_R[summary_cors_nkc_201_R$landscape_ID == ID, "mean_rank2"] <- mean_rank2

}

ggplot(summary_cors_nkc_202_R,
       aes(x = corr,
           y = mean_rank1)) +
   geom_segment(aes(x = corr, 
      y = mean_rank1, 
      xend = corr, 
      yend = mean_rank2),
      col = "grey",
      alpha = 0.7) +
  geom_point(col = "dodgerblue") +
  geom_point(aes(x = corr,
                 y = mean_rank2),
             col = "purple") +
  scale_y_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "mean fitness rank") +
  xlab("correlation(rank F, rank P)") +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme



ggplot(summary_cors_nkc_202_R[summary_cors_nkc_202_R$mean_rank1 != 17,],
       aes(x = corr,
           y = abs(mean_rank1-mean_rank2))) +
  geom_point(col = "dodgerblue") +
  scale_y_continuous(labels = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(0:17),
                   name = "difference in mean fitness rank") +
  xlab("correlation(rank F, rank P)") +
  theme_bw() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme


```
 

# 3.) Supplementary figures
## Repeatability N' = 4
```{r}
localrep_N4 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 4 &
                                       peaks_total_ranked_summarised$walking == "prop",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
     theme_bw() +
  geom_violin(col = "grey45") +
  geom_jitter(col = "springgreen4",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  facet_grid( ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   limits = c(0.5,17.5),
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape") +
  theme(axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y = element_text(size=16),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 37,
       height = 10,
       filename = "localrep_N4.pdf",
       plot = localrep_N4)
```

## Ruggedness - roughness to slope 
```{r}
## calculate roughness to slope ratio
# fit a linear regression to gentoype - fitness 

r <- NULL
s <- NULL

# fully additive 
for (i in 1:200) { # for each landscape replicate
  
  temp_landscape <- peaks_nkcs_2001[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_200_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:200,
                            r = r,
                            s = s,
                            rugg = r/s)

# intragenomic epistasis
r <- NULL
s <- NULL

for (i in 1:200) {
  
  temp_landscape <- peaks_nkcs_2101[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_210_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:200,
                            r = r,
                            s = s,
                            rugg = r/s)

# intergenomic epistasis
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2011[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_201_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 2
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2011[[4]][[2]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_201_2_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(2, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 3
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2011[[4]][[3]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_201_3_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(3, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 4
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2011[[4]][[4]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_201_4_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(4, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# C = 2
r <- NULL
s <- NULL

for (i in 1:200) {
  
  temp_landscape <- peaks_nkcs_2021[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_202_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(2, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:200,
                            r = r,
                            s = s,
                            rugg = r/s)


# inter + intragenomic epistasis
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2111[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_211_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 2
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2111[[4]][[2]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_211_2_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(2, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 3
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2111[[4]][[3]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_211_3_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(3, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 4
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2111[[4]][[4]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_211_4_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(4, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# fully epistatic
r <- NULL
s <- NULL

for (i in 1:200) {
  
  temp_landscape <- peaks_nkcs_2121[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_212_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(2, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:200,
                            r = r,
                            s = s,
                            rugg = r/s)

# N = 4, K = 1
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_4101[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$F.3 + temp_landscape$F.4)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_410_1_1 <- data.frame(n = rep(4, length(r)),
                            k = rep(1, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(5, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)


# N = 4, K = 2
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_4201[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$F.3 + temp_landscape$F.4)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_420_1_1 <- data.frame(n = rep(4, length(r)),
                            k = rep(2, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(5, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# N = 4, K = 3
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_4301[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$F.3 + temp_landscape$F.4)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_430_1_1 <- data.frame(n = rep(4, length(r)),
                            k = rep(3, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(5, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

ruggedness_df <- rbind(ruggedness_nkc_rep_sp_200_1_1[1:50,], ruggedness_nkc_rep_sp_201_1_1, ruggedness_nkc_rep_sp_202_1_1[1:50,], ruggedness_nkc_rep_sp_210_1_1[1:50,], ruggedness_nkc_rep_sp_211_1_1, ruggedness_nkc_rep_sp_212_1_1[1:50,], ruggedness_nkc_rep_sp_410_1_1, ruggedness_nkc_rep_sp_420_1_1, ruggedness_nkc_rep_sp_430_1_1)

ruggedness_df$rugg <- abs(ruggedness_df$rugg)
ruggedness_df$rugg <- round(ruggedness_df$rugg, 4)

ruggedness <- ggplot(ruggedness_df,
       aes(x = interaction(k, c, n),
           y = rugg,
           group = interaction(k, c, n))) +
  geom_violin(col = "grey45") +
  geom_jitter(col = "springgreen4",
              alpha = 0.4,
              width = 0.2,
              size = 4) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 4,
               col = "black") +
  scale_y_log10() + 
  scale_x_discrete(labels=c("0.0.2" = "2-0-0", 
                            "1.0.2" = "2-1-0",
                            "0.1.2" = "2-0-1",
                            "1.1.2" = "2-1-1",
                            "0.2.2" = "2-0-2",
                            "1.2.2" = "2-1-2",
                            "1.0.4" = "4-1-0",
                            "2.0.4" = "4-2-0",
                            "3.0.4" = "4-3-0")) +
  xlab("N-K-C") +
  ylab("log(roughness/slope)")+
  theme_bw() +
  fig_theme +
  theme(panel.grid.major.x = element_blank())

# ggsave(path = "../Figures/",
#        device = cairo_pdf, # to save pdf with unicode
#        units = c("cm"),
#        width = 30,
#        height = 10,
#        filename = "ruggedness.pdf",
#        plot = ruggedness)

```

## ruggedness C = 1
```{r}

ruggedness_df_c1 <- rbind(ruggedness_nkc_rep_sp_201_1_1, ruggedness_nkc_rep_sp_201_2_1, ruggedness_nkc_rep_sp_201_3_1,
                          ruggedness_nkc_rep_sp_201_4_1, ruggedness_nkc_rep_sp_211_1_1, ruggedness_nkc_rep_sp_211_2_1,
                          ruggedness_nkc_rep_sp_211_3_1, ruggedness_nkc_rep_sp_211_4_1)

ruggedness_df_c1$rugg <- abs(ruggedness_df_c1$rugg)

ruggedness_c1 <- ggplot(ruggedness_df_c1,
       aes(x = interaction(IM_rep, k, c, n),
           y = rugg,
           group = interaction(IM_rep, k, c, n))) +
  geom_violin(col = "grey45") +
  geom_jitter(aes(col = as.factor(IM_rep)),
              alpha = 0.4,
              width = 0.2,
              size = 4) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 4,
               col = "black") +
  scale_color_manual(values=c("forestgreen", "limegreen", "olivedrab2", "gold")) +
  scale_y_log10() + 
  scale_x_discrete(labels=c("2-0-1", "2-1-1"),
                   breaks = c("2.0.1.2", "2.1.1.2")) +
  xlab("N-K-C") +
  ylab("log(roughness/slope)")+
  theme_bw() +
  fig_theme +
  theme(panel.grid.major.x = element_blank())

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 20,
       height = 10,
       filename = "ruggedness_c1.pdf",
       plot = ruggedness_c1)

```

## Ruggedness - repeatability
```{r}
complete_ruggedness_df <- rbind(ruggedness_nkc_rep_sp_201_1_1, ruggedness_nkc_rep_sp_201_2_1, ruggedness_nkc_rep_sp_201_3_1,
                          ruggedness_nkc_rep_sp_201_4_1, ruggedness_nkc_rep_sp_211_1_1, ruggedness_nkc_rep_sp_211_2_1,
                          ruggedness_nkc_rep_sp_211_3_1, ruggedness_nkc_rep_sp_211_4_1, ruggedness_nkc_rep_sp_200_1_1,
                          ruggedness_nkc_rep_sp_210_1_1, ruggedness_nkc_rep_sp_212_1_1, ruggedness_nkc_rep_sp_202_1_1)

complete_ruggedness_df$rugg <- abs(complete_ruggedness_df$rugg)
complete_ruggedness_df$landscape_ID <- interaction(complete_ruggedness_df$n, complete_ruggedness_df$k, complete_ruggedness_df$c, complete_ruggedness_df$IM_rep, complete_ruggedness_df$scape_rep)

for (i in 1:nrow(peaks_total_ranked2_summarised[, ])){
  
  ID <- peaks_total_ranked2_summarised[i, "landscape_ID" ]
  
  if (ID %in% complete_ruggedness_df$landscape_ID){
    
    peaks_total_ranked2_summarised[i, "rugg" ] <- complete_ruggedness_df[as.character(complete_ruggedness_df$landscape_ID) == as.character(ID), "rugg"]
    
  }

}

rug_rep <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$n == 2 &
                                        peaks_total_ranked2_summarised$c > 0,],
       aes(x = rugg,
           y = rank_peaked/80)) +
  geom_point(col = "forestgreen",
             size = 2,
             alpha = 0.8) +
  facet_grid(c ~ k) +
   scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "log(roughness/slope)",
                     transform = "log10",
       sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                           breaks = NULL, labels = NULL)) +
  theme_bw() +
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "rug_rep.pdf",
       plot = rug_rep)

```


## ruggedness - outcome
```{r}


rug_out <- ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = rugg,
           y = rank_sp1)) +
   geom_segment(aes(x = rugg, 
      y = rank_sp1, 
      xend = rugg, 
      yend = rank_sp2),
      col = "grey40",
      alpha = 0.8) +
  geom_point(col = "forestgreen",
             size = 2,
             aes(alpha = rank_peaked/80)) +
  geom_point(aes(x = rugg,
                 y = rank_sp2,
                 alpha = rank_peaked/80),
                 col = "forestgreen",
             size = 2) +
  facet_grid(c ~ k) +
   scale_y_continuous(labels = c("1", "3", "5", "7", "9", "11", "13", "15", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = seq(1, 17, 2),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "log(roughness/slope)",
                     transform = "log10",
       sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                           breaks = NULL, labels = NULL)) +
  theme_bw() +
  theme(axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) +
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "rug_out.pdf",
       plot = rug_out)

```

```{r}

rug_dis <- ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = rugg,
           y = abs(rank_sp1-rank_sp2))) +
  geom_point(col = "dodgerblue",
             size = 2,
             aes(alpha = rank_peaked/80)) +
  facet_grid(c ~ k) +
   scale_y_continuous(labels = c("1", "3", "5", "7", "9", "11", "13", "15", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = seq(1, 17, 2),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = "C", breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "log(roughness/slope)",
                     transform = "log10",
       sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL)) +
  theme_bw() +
  theme(axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) +
  fig_theme

```

```{r}

ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = rugg,
           y = corr_rank)) +
  geom_point() +
  scale_x_continuous(name = "log(roughness/slope)",
                     transform = "log10",
       sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL)) +
  theme_classic()

```

## Greedy Repeatability N = 2
```{r}
localrep_N2_greedy <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "greedy",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_violin(aes(y = prop_cycle,
                  x = rank),
              col = "grey45") +
  geom_jitter(col = "springgreen4",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  geom_jitter(aes(y = prop_cycle,
                  x = rank),
               col = "skyblue",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the mean proportion of cycling/landscape
                  x = rank),
               fun = mean,
               geom = "crossbar",
               linewidth = 0.4,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the median proportion of cycling/landscape
                  x = rank),
               fun = median,
               geom = "point",
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 17,
       filename = "localrep_N2_greedy.pdf",
       plot = localrep_N2_greedy)

```

## Random Repeatability N = 2
```{r}
localrep_N2_random <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "random",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_violin(aes(y = prop_cycle,
                  x = rank),
              col = "grey45") +
  geom_jitter(col = "springgreen4",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  geom_jitter(aes(y = prop_cycle,
                  x = rank),
               col = "skyblue",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the mean proportion of cycling/landscape
                  x = rank),
               fun = mean,
               geom = "crossbar",
               linewidth = 0.4,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the median proportion of cycling/landscape
                  x = rank),
               fun = median,
               geom = "point",
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 17,
       filename = "localrep_N2_random.pdf",
       plot = localrep_N2_random)

```

## R = 2
```{r}
localrep_N2_R <- ggplot(peaks_total_ranked_summarised_R[peaks_total_ranked_summarised_R$n == 2 &
                                       peaks_total_ranked_summarised_R$walking == "prop",], # only greedy walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_jitter(col = "springgreen4",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                     limits = c(0.5,17.5),
                   name = "Fitness rank focal species",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 15,
       filename = "localrep_N2_R.pdf",
       plot = localrep_N2_R)
```

## R = 2 - fitness distribution
```{r}
fitness_dis_N2_R <- ggplot(peaks_total_ranked_summarised_R[peaks_total_ranked_summarised_R$n == 2 &
                                       peaks_total_ranked_summarised_R$walking == "prop",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_bar(aes(y = after_stat(prop), # proportion of data points at each rank (calculated for each facet)
               group = 1),
           fill = "thistle3") + # across all my groupings
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL),
                   limits = c(0,1)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26, # 30
       height = 17, # 15
       filename = "fitness_dis_N2_R.pdf",
       plot = fitness_dis_N2_R)

```

## correlation - fitness outcomes -> full figure
```{r}
eco_outcomes <- ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = corr_rank,
           y = rank_sp1)) +
   geom_segment(aes(x = corr_rank, 
      y = rank_sp1, 
      xend = corr_rank, 
      yend = rank_sp2),
      col = "grey40",
      alpha = 0.8) +
  geom_point(col = "forestgreen",
             size = 2,
             aes(alpha = rank_peaked/80)) +
  geom_point(aes(x = corr_rank,
                 y = rank_sp2,
                 alpha = rank_peaked/80),
                 col = "forestgreen",
             size = 2) +
  facet_grid(c ~ k) +
  scale_y_continuous(labels = c("1", "3", "5", "7", "9", "11", "13", "15", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :-)
                     breaks = seq(1, 17, 2),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL),
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "eco_outcomes.pdf",
       plot = eco_outcomes)

```

## correlation-fitness difference relationship
```{r}

eco_dis <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$rank_sp1 != 17 &
                                        !is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = corr_rank,
           y = abs(rank_sp1-rank_sp2))) +
  geom_point(col = "dodgerblue") +
  geom_smooth(method = "glm") +
  facet_grid(c ~ k) +
  scale_y_continuous(labels = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(0:17),
                   name = "difference in fitness rank",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL),
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "eco_dis.pdf",
       plot = eco_dis)


ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = corr_rank,
           y = (rank_sp1 + rank_sp2)/2)) +
  geom_point(col = "dodgerblue") +
  facet_grid(c ~ k) +
  scale_y_continuous(labels = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(0:17),
                   name = "mean community fitness rank") +
  xlab("rank correlation(F, P)") +
  theme_bw() +
  theme(text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme
```


## IMs fitness
```{r}

effectIM_fit_N2 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                         peaks_total_ranked_summarised$c == 1 &
                                       peaks_total_ranked_summarised$walking == "prop",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_bar(aes(y = after_stat(prop), # proportion of data points at each rank (calculated for each facet)
               group = 1),
           fill = "thistle3") + # across all my groupings
     theme_bw() +
  facet_grid(c_rep ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                     limits = c(0,1)) +
  scale_color_manual(values=c("forestgreen", "limegreen", "olivedrab2", "gold")) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
        legend.position = "none",
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 21,
       filename = "effectIM_fit_N2.pdf",
       plot = effectIM_fit_N2)

```

## correlation R = 2
```{r}
## same but for R = 2
combined_scapes_nkc_201_R <- list()
summary_cors_nkc_201_R <- NULL

for (i in 1:4){ # for each interaction matrix
  
  combined_scapes_nkc_201_R[[i]] <- list()
  
for (j in 1:50){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2011_R[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2011_R[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 0, 1, i, j))

summary_cors_nkc_201_R <- rbind(summary_cors_nkc_201_R, summary_temp)

combined_scapes_nkc_201_R[[i]][[j]] <- test_df
  
}
}


combined_scapes_nkc_211_R <- list()
summary_cors_nkc_211_R <- NULL

for (i in 1:4){ # for each interaction matrix
  
  combined_scapes_nkc_211_R[[i]] <- list()
  
for (j in 1:50){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2111_R[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2111_R[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 1, 1, i, j))

summary_cors_nkc_211_R <- rbind(summary_cors_nkc_211_R, summary_temp)

combined_scapes_nkc_211_R[[i]][[j]] <- test_df
  
}
}

summary_cors_R <- rbind(summary_cors_nkc_211_R, summary_cors_nkc_201_R)

for (i in 1:nrow(peaks_total_ranked2_summarised_R[, ])){
  
  ID <- peaks_total_ranked2_summarised_R[i, "landscape_ID" ]
  
  if (ID %in% summary_cors_R$landscape_ID){
    
    peaks_total_ranked2_summarised_R[i, "corr_rank" ] <- summary_cors_R[as.character(summary_cors_R$landscape_ID) == ID, "corr"]
    
  }

}

eco_outcomes_R <- ggplot(peaks_total_ranked2_summarised_R[!is.na(peaks_total_ranked2_summarised_R$corr_rank),],
       aes(x = corr_rank,
           y = rank_sp1)) +
   geom_segment(aes(x = corr_rank, 
      y = rank_sp1, 
      xend = corr_rank, 
      yend = rank_sp2),
      col = "grey40",
      alpha = 0.8) +
  geom_point(col = "forestgreen",
             size = 2,
             aes(alpha = rank_peaked/80)) +
  geom_point(aes(x = corr_rank,
                 y = rank_sp2,
                 alpha = rank_peaked/80),
                 col = "forestgreen",
             size = 2) +
  facet_grid(c ~ k) +
  scale_y_continuous(labels = c("1", "3", "5", "7", "9", "11", "13", "15", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = seq(1, 17, 2),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = "C", breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL),
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "eco_outcomes_R.pdf",
       plot = eco_outcomes_R)

```


```{r}

eco_dis_R <- ggplot(peaks_total_ranked2_summarised_R[peaks_total_ranked2_summarised_R$rank_sp1 != 17 &
                                        !is.na(peaks_total_ranked2_summarised_R$corr_rank),],
       aes(x = corr_rank,
           y = abs(rank_sp1-rank_sp2))) +
  geom_point(col = "dodgerblue") +
  geom_smooth(method = "glm") +
  facet_grid(c ~ k) +
  scale_y_continuous(labels = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(0:17),
                   name = "difference in fitness rank",
                   sec.axis = sec_axis(~ . , name = "C", breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL),
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "eco_dis_R.pdf",
       plot = eco_dis_R)

```

```{r}


community_fit <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$rank_sp1 != 17 &
                                        !is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = corr_rank,
           y = (rank_sp1 + rank_sp2)/2)) +
  geom_point(col = "dodgerblue") +
  facet_grid(c ~ k) +
  geom_smooth(method = "glm") +
  scale_y_continuous(labels = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(0:17),
                   name = "mean community fitness rank",
                   sec.axis = sec_axis(~ . , name = "C", breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL),
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "community_fit.pdf",
       plot = community_fit)
```




## Repeatability predicted by interaction type (fitness correlation)?
```{r}

eco_rep <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$rank_sp1 != 17 &
                                        !is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = corr_rank,
           y = rank_peaked/80)) +
  geom_point(col = "forestgreen") +
  facet_grid(c ~ k) +
  xlim(c(-1,1)) +
  scale_y_continuous(limits = c(0,1),
                   name = "Proportion of adaptive walks/landscape") +
  xlab("rank correlation(F, P)") +
  theme_bw() +
  theme(text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 15,
       filename = "eco_rep_N2.pdf",
       plot = eco_rep)
```


## Visualising cycles
```{r}
# walk example 
cycle_walk <- peaks_nkcs_2011[[5]][[4]][[17]][[1]][[1]]

cycle_df <- data.frame(rank_sp1 = cycle_walk[[1]][,"rank"],
                         rank_sp2 = cycle_walk[[2]][,"rank"],
                         step = cycle_walk[[1]][,"step"])

cycle <- ggplot(cycle_df,
       aes(x = rank_sp1,
           y = rank_sp2)) + 
  geom_point(size = 3,
             col = "forestgreen") +
  geom_arrow_chain() +  geom_arrow_chain() +
  scale_x_continuous(breaks = c(1:16),
                     limits = c(1,16),
                     name = "Fitness rank focal species") +
  scale_y_continuous(breaks = c(1:16),
                     limits = c(1,16),
                     name = "Fitness rank partner species") +
  theme_classic() +
  fig_theme

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 15,
       height = 13,
       filename = "cycle_NKC_201_4_17.pdf",
       plot = cycle)

```

## N = 4 fitness distribution
```{r}
fitness_dis_N4 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 4 &
                                       peaks_total_ranked_summarised$walking == "prop",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_bar(aes(y = after_stat(prop), # proportion of data points at each rank (calculated for each facet)
               group = 1),
           fill = "thistle3") + # across all my groupings
     theme_bw() +
  facet_grid( ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank focal species",
                   limits = c(0.5,17.5),
                   sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                     limits = c(0,1)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 45,
       height = 15,
       filename = "fitness_dis_N4.pdf",
       plot = fitness_dis_N4)
```

## fitness distribution - greedy
```{r}
fitness_dis_N2_greedy <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "greedy",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_bar(aes(y = after_stat(prop), # proportion of data points at each rank (calculated for each facet)
               group = 1),
           fill = "thistle3") + # across all my groupings
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                   sec.axis = sec_axis(~ . , name = "C", breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26, # 30
       height = 17, # 15
       filename = "fitness_dis_N2_greedy.pdf",
       plot = fitness_dis_N2_greedy)

```

## fitness distribution - random
```{r}
fitness_dis_N2_random <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "random",], # only true walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_bar(aes(y = after_stat(prop), # proportion of data points at each rank (calculated for each facet)
               group = 1),
           fill = "thistle3") + # across all my groupings
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                   sec.axis = sec_axis(~ . , name = "C", breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26, # 30
       height = 17, # 15
       filename = "fitness_dis_N2_random.pdf",
       plot = fitness_dis_N2_random)

```


# 4.) Additional analysis
## Assessing the number of outcomes
```{r}
# how many outcomes are there on the same landscape?
true_only_summed2 <- as.data.frame(peaks_total_ranked2_summarised |> 
                            dplyr::group_by(k, c, n, landscape_ID, ) |>
                            dplyr::summarise(outcomes = n())) 

# K = 1, C = 0
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 1 & 
                            true_only_summed2$c == 0 &
                            true_only_summed2$outcomes > 1,]) # tot = 200

# K = 1, C = 1
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 1 & 
                            true_only_summed2$c == 1 &
                            true_only_summed2$outcomes > 1,]) # tot = 200

# K = 0, C = 1
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 0 & 
                            true_only_summed2$c == 1 &
                            true_only_summed2$outcomes > 1,]) # tot = 200

# K = 0, C = 2
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 0 & 
                            true_only_summed2$c == 2 &
                            true_only_summed2$outcomes > 1,]) # tot = 200


# K = 1, C = 2
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 1 & 
                            true_only_summed2$c == 2 &
                            true_only_summed2$outcomes > 1,]) # tot = 200


## same but with R = 2
# how many outcomes are there on the same landscape?
prop_only_summed2_R <- as.data.frame(peaks_total_ranked2_summarised_R |> 
                            dplyr::group_by(k, c, n, landscape_ID, ) |>
                            dplyr::summarise(outcomes = n())) 

# K = 1, C = 1
mult_peak2 <- nrow(prop_only_summed2_R[prop_only_summed2_R$k == 1 & 
                            prop_only_summed2_R$c == 1 &
                            prop_only_summed2_R$outcomes > 1,]) # tot = 200

# K = 0, C = 1
mult_peak2 <- nrow(prop_only_summed2_R[prop_only_summed2_R$k == 0 & 
                            prop_only_summed2_R$c == 1 &
                            prop_only_summed2_R$outcomes > 1,]) # tot = 200

```



## Trying some linear models
```{r}

test_data1 <- peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$a == 2 &
                                       peaks_total_ranked_summarised$walking == "greedy",]

test_data <- peaks_total[peaks_total$n == 2 &
                         peaks_total$a == 2 &
                           peaks_total$c != 2 &
                           peaks_total$walking == "greedy" &
                           peaks_total$step < max_steps,]

test_data3 <- peaks_total[peaks_total$n == 2 &
                         peaks_total$a == 2 &
                           peaks_total$walking == "greedy",]

test_data3$cycle <- "N"
test_data3[test_data3$step == max_steps, "cycle"] <- "Y"

library(nnet)
library(broom)

# the effect of C/K on the final rank
model <- nnet::multinom(as.factor(rank) ~ as.factor(k) * as.factor(c), data = test_data)
#sum_mod <- summary(model)

coef_df <- broom::tidy(model) %>%
  mutate(
    OR  = exp(estimate),                 # odds ratio
    OR_low  = exp(estimate - 1.96*std.error), # 95% CI lower
    OR_high = exp(estimate + 1.96*std.error)  # 95% CI upper
  )  %>%
  filter(term != "(Intercept)") %>%      # drop intercepts
  mutate(predictor = term,
         Rank   = factor(y.level, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16")))

ggplot(coef_df, 
       aes(x = predictor, 
           y = OR, 
           color = Rank)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "grey40") +
  geom_point(position = position_dodge(width = 0.7), 
             size = 3) +
  geom_errorbar(aes(ymin = OR_low, 
                    ymax = OR_high),
                width = 0.2,
                position = position_dodge(width = 0.7)) +
  scale_y_log10() +   # << log-transformed axis
  theme_bw(base_size = 14) +
  labs(y = "log(Odds ratio)", x = "") +
  scale_x_discrete(labels = c("as.factor(c)1" = "C = 1",
                              "as.factor(k)1" = "K = 1",
                              "as.factor(k)1:as.factor(c)1" = "C = 1:K = 1")) 

model_cycle <- glm(as.factor(cycle) ~ as.factor(k) * as.factor(c) * as.factor(c_rep),
             data = test_data3,
             family = binomial(link = "logit"))

coef_df <- broom::tidy(model_cycle) %>%
  mutate(
    OR  = exp(estimate),                 # odds ratio
    OR_low  = exp(estimate - 1.96*std.error), # 95% CI lower
    OR_high = exp(estimate + 1.96*std.error)  # 95% CI upper
  )  %>%
  filter(term != "(Intercept)") 

ggplot(coef_df, 
       aes(x = term, 
           y = OR)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "grey40") +
  geom_point(position = position_dodge(width = 0.7), 
             size = 3) +
  geom_errorbar(aes(ymin = OR_low, 
                    ymax = OR_high),
                width = 0.2,
                position = position_dodge(width = 0.7)) +
  scale_y_log10() +   # << log-transformed axis
  theme_bw(base_size = 14) +
  labs(y = "log(Odds ratio)", x = "") +
  scale_x_discrete(labels = c("as.factor(c)1" = "C = 1",
                              "as.factor(c)2" = "C = 2",
                              "as.factor(k)1" = "K = 1",
                              "as.factor(k)1:as.factor(c)1" = "C = 1:K = 1",
                              "as.factor(k)1:as.factor(c)2" = "C = 2:K = 1")) 


```


# 5.) Additional figures
## Fitness landscape example; "classic" version
```{r}
example_scape_fig <- visualise_system(peaks_nkcs_2111[[4]][[2]][[27]], # I recode the alleles into as and bs in Adobe Illustrator O:-)
                 n = 2,
                 c = 1,
                 s = 1,
                 s_tot = 2) +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=25 ),
        strip.text.x = element_text(size=25))

# ggsave(path = "../Figures/",
#        device = "pdf",
#        units = c("cm"),
#        width = 35,
#        height = 14,
#        filename = "scapes_NKC_201_2_17.pdf",
#        plot = example_scape_fig)
```

## Network representation of adaptive walks
```{r}
# Making an adjacency matrix (which metagenotypes can mutate into each other?)
x <- as.data.frame(gtools::permutations(2, 4, c(1:2), repeats = TRUE))
x$ID <- 1:16

adj_mat <- matrix(16, 16, data = rep(0, 16^2))

for (i in 1:16) {
  
  adj_mat[i,findNeighbours(x, i, 4)$ID] <- 1
  
}


# translating my adaptive walks into something I can use here
# I need to extract the transitions from my adaptive walks -> format: from - to - in how many replicates of walk

walks_dfs <- NULL
for (i in 1:48){
  
 temp_df <- peaks_nkcs_2011[[5]][[1]][[26]][[3]][[i]] # true walk
 
 IDs <- NULL
 
 for (j in 0:max(temp_df[[1]][,"step"])) {
   
    metagenotype <- temp_df[[1]][temp_df[[1]]$step == j, c("F.1", "F.2", "P.1", "P.2")]
 ID_temp <- x[rowSums(mapply(`==`, x[, c("V1", "V2", "V3", "V4")], metagenotype)) == 4, "ID"] # extract the ID of the metagenotype that matches my adjacency matrix IDs
 
 IDs <- c(IDs, ID_temp)
   
 }
 
 from_IDs <- IDs[1:(length(IDs)-1)]
 to_IDs <- IDs[2:length(IDs)]
 
 temp_df <- data.frame(from = from_IDs,
                       to = to_IDs,
                      step = temp_df[[1]][c(2:nrow(temp_df[[1]])),"step"],
                       focal = temp_df[[1]][c(2:nrow(temp_df[[1]])),"focal"],
                       walk = i)
 
 walks_dfs <- rbind(walks_dfs, temp_df)
  
}

walks_dfs_summed <- as.data.frame(walks_dfs |> 
                            dplyr::group_by(from, to, focal, walk) |>
                            dplyr::summarise(step_count = n()))

walks_dfs_summed2 <- as.data.frame(walks_dfs_summed |> 
                            dplyr::group_by(from, to, focal) |>
                            dplyr::summarise(rep_count = n())) # this gives me in how many replicates certain steps were taken from x to y given a certain focal species


g <- igraph::graph_from_data_frame(walks_dfs_summed2, 
                           directed = TRUE)

# add metadata to the nodes in the network (here "averaged per node")
igraph::V(g)$count <- ave(walks_dfs_summed2$rep_count, walks_dfs_summed2$from, FUN = max)[match(V(g)$name, walks_dfs_summed2$from)]

ranks_sp1 <- peaks_nkcs_2011[[4]][[1]][[26]][[1]]$rank
test_df <- peaks_nkcs_2011[[4]][[1]][[26]][[2]]
ranks_sp2 <- test_df[order(test_df$P.1, test_df$P.2, test_df$F.1, test_df$F.2), "rank"]

igraph::V(g)$rank_sp1 <- ranks_sp1
igraph::V(g)$rank_sp2 <- ranks_sp2


graph <- ggraph::ggraph(g,
               layout = "stress") +
  geom_edge_fan(aes(linetype = as.factor(focal)), # different edge color for the different steps based on focal species
                 end_cap = circle(5, "mm"), # buffer between node and arrow
                colour = "grey40") + 
  geom_edge_fan(arrow = arrow(type = "closed", # make arrow heads separately so they all have solid outlines
                              angle = 20, # "width" of arrow tip
                              length = unit(4, "mm")), # length of arrow tip
                edge_width = 0,
                 end_cap = circle(5, "mm"), # buffer between node and arrow
                colour = "grey40") + 
  geom_edge_loop(aes(linetype = as.factor(focal),
                     strength = (3*focal/4)), # to make non-overlapping loops
                 end_cap = circle(4, "mm"),
                colour = "grey40") +
  geom_edge_loop(aes(strength = (3*focal/4)), # make arrow heads separately so they all have solid outlines
                 arrow = arrow(type = "closed",
                               angle = 20,
                 length = unit(4, "mm")),
                 edge_width = 0,
                 end_cap = circle(4, "mm"),
                colour = "grey40") +
  geom_node_arc_bar(aes(x0 = x,
                        y0 = y,
                        r0 = 0, 
                        r = count/300 + 0.1,
                       start = pi, 
                       end = 2*pi,
                       fill = rank_sp1),
                       colour = "white") + # left semicircle
  geom_node_arc_bar(aes(x0 = x,
                        y0 = y,
                        r0 = 0, 
                        r = count/300 + 0.1, 
                        start = 0, 
                        end = pi,
                       fill = rank_sp2),
                       colour = "white") + # right semicircle
  #geom_node_text(aes(label = name)) +                   # "name" is automatically generated from the node IDs in the edges; then adjust r0 o read text
  scale_size(range = c(5, 15),
             guide = "none") +
  scale_edge_linetype_manual(values = c("solid", "dashed"),
                             name = "focal species") +
  scale_fill_gradient2(name = "fitness rank",
                         low = "#5d36f7",
                         high = "#f9db45",
                         mid = "#f274f0",
                         midpoint = mean(ranks_sp1), # to adjust midpoint for landscapes with more or less peaks
                         guide = "colourbar",
                         aesthetics = "fill",
                         transform = "reverse",
                       breaks = c(1, 4, 8, 12, 16)) +
  theme_void() +
  guides(edge_linetype = guide_legend(position = "top"))


# ggsave(path = "../Figures/",
#        device = "pdf",
#        units = c("cm"),
#        width = 15,
#        height = 12,
#        filename = "graph_NKC_201_4_17.pdf",
#        plot = graph)


```

## Community fitness
```{r}
community_pattern <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$n == 2,], # only true walks in main text
        aes(y = rank_peaked/80,
            x = (rank_sp1 + rank_sp2)/2,
            group = (rank_sp1 + rank_sp2)/2)) +
  geom_bar(aes(y = after_stat(prop), # proportion of data points at each rank (calculated for each facet)
               group = 1),
           fill = "thistle3") + # across all my groupings
  geom_violin(col = "grey45") +
  geom_jitter(col = "springgreen4",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                   name = "Cpmmunity fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "<span style='color:thistle4'> Proportion of overall outcomes </span>  \nProportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = "C", breaks = NULL, labels = NULL)) +
  theme(axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 17,
       filename = "community_pattern.pdf",
       plot = community_pattern)


```

# 6.) Plots I put on my GRS/GRC poster
``` {r Poster figures}

legend <- scale_colour_manual(values = c("#157F1F", "#FCA311", "#CB48B7"),
                              breaks = c("greedy","prop", "random"),
                              labels = c("greedy",
                                         "weighted",
                                         "random"),
                              name="type of adaptive walk")

poster_theme <- theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=25),
                      legend.text = element_text(size=15),
                      legend.title = element_text(size=20),
                      legend.position = "top")

peak_fig <- ggplot(peaks_summarised2[peaks_summarised2$peaked == 2,],
        aes(y = prop_reached,
            x = interaction(n, k, c),
            col = walking)) +
     gghalves::geom_half_boxplot(nudge = 0.05,
                                 fill = "grey90") +
  gghalves::geom_half_point(position = "dodge2",
                            transformation = position_jitter(w = 0.05, h = 0)) +
  scale_x_discrete(labels=c("2.0.0" = "2-0-0", 
                            "2.1.0" = "2-1-0",
                            "2.0.1" = "2-0-1",
                            "2.1.1" = "2-1-1",
                            "2.0.2" = "2-0-2",
                            "2.1.2" = "2-1-2")) +
  ylab("Probability of both species reaching their global peak") +
  xlab("N-K-C") +
  legend +
  theme_bw() +
  poster_theme +
  theme(axis.title.y = element_text(size = 22))

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 26,
       height = 18.5,
       filename = "peak_fig.pdf",
       plot = peak_fig)

step_fig <- ggplot(peaks_total2,
       aes(y = step,
           x = interaction(peaked, n, k, c),
           col = walking)) +
  gghalves::geom_half_boxplot(nudge = 0.05,
                                 fill = "grey80") +
  gghalves::geom_half_point(position = "dodge2",
                            transformation = position_jitter(w = 0.05, h = 0)) +
  scale_x_discrete(labels=c("2.2.0.0" = "2-0-0~2", 
                            "0.2.1.0" = "2-1-0~0",
                            "1.2.1.0" = "2-1-0~1",
                            "2.2.1.0" = "2-1-0~2",
                            "0.2.0.1" = "2-0-1~0",
                            "1.2.0.1" = "2-0-1~1",
                            "2.2.0.1" = "2-0-1~2",
                            "0.2.1.1" = "2-1-1~0",
                            "1.2.1.1" = "2-1-1~1",
                            "2.2.1.1" = "2-1-1~2",
                            "0.2.0.2" = "2-0-2~0",
                            "1.2.0.2" = "2-0-2~1",
                            "2.2.0.2" = "2-0-2~2",
                            "0.2.1.2" = "2-1-2~0",
                            "1.2.1.2" = "2-1-2~1",
                            "2.2.1.2" = "2-1-2~2")) +
  ylab("Steps in adaptive walk") +
  xlab("N-K-C ~ nb. of species at global peak") +
  legend +
  theme_bw() +
  poster_theme

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 45,
       height = 18,
       filename = "step_fig.pdf",
       plot = step_fig)

cycle_fig <- ggplot(peaks_summarised_cycles,
        aes(y = prop_cycles,
            x = interaction(n, k, c),
            col = walking)) +
  gghalves::geom_half_boxplot(nudge = 0.05,
                                 fill = "grey80") +
  gghalves::geom_half_point(position = "dodge2",
                            transformation = position_jitter(w = 0.05, h = 0)) +
  scale_x_discrete(labels=c("2.0.0" = "2-0-0", 
                            "2.1.0" = "2-1-0",
                            "2.0.1" = "2-0-1",
                            "2.1.1" = "2-1-1",
                            "2.0.2" = "2-0-2",
                            "2.1.2" = "2-1-2")) +
  ylab("Probability of cycling") +
  xlab("N-K-C") +
  legend +
  theme_bw() +
  poster_theme

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 26,
       height = 18,
       filename = "cycle_fig.pdf",
       plot = cycle_fig)

example_scape_fig <- visualise_system(peaks_nkcs_2111[[4]][[2]][[40]], # this is just a pair of landscapes I chose because they lead to cycling
                 n,
                 c,
                 s,
                 s_tot) +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=25 ),
        strip.text.x = element_text(size=25))

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 35,
       height = 14,
       filename = "scapes_NKC_211_2_40.pdf",
       plot = example_scape_fig)

walks_fig <- visualise_walks(peaks_nkcs_2111[[5]][[5]][[22]][[1]][[28]], # these are the adaptive walks (cycling) that go with the example I chose (greedy walk)
                n,
                s,
                s_tot,
                peaks_nkcs_2111[[4]][[5]][[22]]) + # this is the matching pair of landscapes
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=25),,
        strip.text.x = element_text(size=25))

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 30,
       height = 14,
       filename = "walks_fig.pdf",
       plot = walks_fig)
 
```


