---
title: "NKC_exploration"
output: html_notebook
---

Loraine Hablützel - 29.07.2026
This is the code used to generate all simulations; note that this takes quite a while to run with the number of landscape replicates, walk replicates and adaptive walk cutoffs I'm using. (Estimate: ~2 days for the NK(C) simulations and another ~3 days for the seascapes; once the NKC landscapes have been generated, you can plug them into the simulations with different mutation rates or reuse them for the seascapes simulations, so these parts can be split up and ran in parallel!)

see preprint: https://doi.org/10.64898/2026.04.01.715933

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png")
options(bitmapType = "cairo")

knitr::opts_knit$set(root.dir = "~/OneDrive - Universitaet Bern/NKC_project/R_scripts/") # set directory
```

# Set up workspace
```{r libraries}
rm (list = ls())

library(gtools) # permutations to get all possible genotype combinations
library(dplyr) # for constructing the data sets

# load NKC functions
source(knitr::purl("NKC(S).Rmd", quiet=TRUE)) # this way I load the code from the code chunks in the markdown file; when running on the cluster I need to make sure all chunks have unique names, otherwise I'll get errors

```

# 1) NK(C) simulations!
## 1.1) defining parameters
```{r parameters}
set.seed(2512) # for reproducibility

n = 2 # number of loci in each genome
a = 2 # number of alleles at each locus
s = 1 # number of species interacting
s_tot = 2 # total number of species in the community
lambda_R = 1 # if I want to draw the number of mutational steps from a poisson distribution
scape_reps = 50 # number of landscape replicates
fitness_contrib = "N" # distribution from which we draw fitness contributions
fitness_calculation = "KJ" # way to calculate genotype fitness 
fit_mean = 0 # mean of distribution from which we draw fitness contribution
fit_sd = 0.5 # sd of distribution from which we draw fitness contribution
walk_reps = 80 # number of replicates for adaptive walks on a fitness landscape - starting at each metagenotype 5 times
walk_type = c("greedy", "random", "prop") # types of adaptive walks implemented
walk_start = "S" # where to start the adaptive walks (R - Random, WT - wildtype, S - specified)
max_steps = 300 # max number of steps in the adaptive walk

# defining the starting sequences for N = 2, so I can cycle through all possible starting points
metatypes_n2 <- gtools::permutations(a, 2*n, c(1:a), repeats = TRUE) # all possible metagenotypes
metaseqs_n2 <- split(metatypes_n2, row(metatypes_n2)) # break into list, where every metagenotype is an entry
metaseqs_n2 <- lapply(metaseqs_n2, as.numeric) # converting into numbers

# defining the starting sequences for N = 4, so I can cycle through all possible starting points
metatypes_n4 <- gtools::permutations(a, 8, c(1:a), repeats = TRUE) # all possible metagenotypes
metaseqs_n4 <- split(metatypes_n4, row(metatypes_n4)) # break into list, where every metagenotype is an entry
metaseqs_n4 <- lapply(metaseqs_n4, as.numeric) # converting into numbers


# defining all the interaction matrices outside the simulations for more reproducibility
## K - intragenomic epistasis
IM_k0_n2 <- list(build_IMk(IM = "R",
                      2,
                      0,
                      s,
                      s_tot)) # only one possible layout

IM_k1_n2 <- list(build_IMk(IM = "R",
                      2,
                      1,
                      s,
                      s_tot)) # only one possible layout; all ones

IM_k3_n4 <- list(build_IMk(IM = "R",
                      4,
                      3,
                      s,
                      s_tot)) # only one possible layout; all ones

IM_k0_n4 <- list(build_IMk(IM = "R",
                      4,
                      0,
                      s,
                      s_tot)) # only one possible layout

# replicates of interaction matrices
## K = 1
IM_k1_n4 <- list()

# random
IM_k1_n4[[1]] <- build_IMk(IM = "R",
                      4,
                      1,
                      s,
                      s_tot)

# modular
IM_k1_n4[[2]] <- build_IMk(IM = "M",
                      4,
                      1,
                      s,
                      s_tot)

# nearest neighbour (but only to one side)
IM_k1_n4[[3]] <- list()
IM_k1_n4[[3]][[1]] <- matrix(c(1,1,0,0,
                               0,1,1,0,
                               0,0,1,1,
                               1,0,0,1), 4, 4, byrow = TRUE)
IM_k1_n4[[3]][[2]] <- matrix(c(1,1,0,0,
                               0,1,1,0,
                               0,0,1,1,
                               1,0,0,1), 4, 4, byrow = TRUE)

# preferential - on average k interactions per locus
IM_k1_n4[[4]] <- build_IMk(IM = "P",
                      4,
                      1,
                      s,
                      s_tot)

# hierarchical - on average k interactions per locus
IM_k1_n4[[5]] <- build_IMk(IM = "H",
                      4,
                      1,
                      s,
                      s_tot)


## K = 2
IM_k2_n4 <- list()

# random
IM_k2_n4[[1]] <- build_IMk(IM = "R",
                      4,
                      2,
                      s,
                      s_tot)

# modular
IM_k2_n4[[2]] <- list()
IM_k2_n4[[2]][[1]] <- matrix(c(1,1,1,0,
                               1,1,1,0,
                               1,1,1,0,
                               0,1,1,1), 4, 4, byrow = TRUE)
IM_k2_n4[[2]][[2]] <- matrix(c(1,1,1,0,
                               1,1,1,0,
                               1,1,1,0,
                               0,1,1,1), 4, 4, byrow = TRUE)

# nearest neighbour
IM_k2_n4[[3]] <- build_IMk(IM = "N",
                      4,
                      2,
                      s,
                      s_tot)

# preferential - on average k interactions per locus
IM_k2_n4[[4]] <- build_IMk(IM = "P",
                      4,
                      2,
                      s,
                      s_tot)

# hierarchical - on average k interactions per locus
IM_k2_n4[[5]] <- build_IMk(IM = "H",
                      4,
                      2,
                      s,
                      s_tot)

## C
IM_c0_n2 <- list(build_IMc(IM = "R",
                      2,
                      0,
                      s,
                      s_tot)) # only one possible layout

IM_c2_n2 <- list(build_IMc(IM = "R",
                      2,
                      2,
                      s,
                      s_tot)) # only one possible layout

IM_c0_n4 <- list(build_IMc(IM = "R",
                      4,
                      0,
                      s,
                      s_tot)) # only one possible layout

# C = 1
IM_c1_n2 <- list()

# symmetric
# only one locus involved in intergenomic epistasis
IM_c1_n2[[1]] <- list()
IM_c1_n2[[1]][[1]] <- matrix(c(1, 1, 0 , 0), 2, 2)
IM_c1_n2[[1]][[2]] <- matrix(c(1, 1, 0 , 0), 2, 2)

# all loci involved in interaction
IM_c1_n2[[2]] <- list()
IM_c1_n2[[2]][[1]] <- matrix(c(1, 0, 0 , 1), 2, 2)
IM_c1_n2[[2]][[2]] <- matrix(c(1, 0, 0 , 1), 2, 2)

# asymmetric 
# all loci involved in interaction
IM_c1_n2[[3]] <- list()
IM_c1_n2[[3]][[1]] <- matrix(c(1, 0, 0 , 1), 2, 2)
IM_c1_n2[[3]][[2]] <- matrix(c(0, 1, 1 , 0), 2, 2)

# all loci involved in interaction for one species; only one locus for the other
IM_c1_n2[[4]] <- list()
IM_c1_n2[[4]][[1]] <- matrix(c(1, 0, 0 , 1), 2, 2)
IM_c1_n2[[4]][[2]] <- matrix(c(1, 1, 0 , 0), 2, 2)
```

## 1.2) running the simulations
```{r simulations}
set.seed(2512) # for reproducibility

# symmetry in mutation steps between species
peaks_nkcs_2011 <- assess_peaks_R(n, 
                         k = 0,
                         a, 
                         c = 1, 
                         s, 
                         R = 1,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k0_n2,
                         IM_cs = IM_c1_n2, 
                         scape_reps, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2121 <- assess_peaks_R(n, 
                         k = 1,
                         a, 
                         c = 2, 
                         s, 
                         R = 1,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k1_n2,
                         IM_cs = IM_c2_n2,
                         scape_reps = 200, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start,
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2021 <- assess_peaks_R(n, 
                         k = 0,
                         a, 
                         c = 2, 
                         s, 
                         R = 1,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k0_n2,
                         IM_cs = IM_c2_n2, 
                         scape_reps = 200, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2111 <- assess_peaks_R(n, 
                         k = 1,
                         a, 
                         c = 1, 
                         s, 
                         R = 1,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k1_n2,
                         IM_cs = IM_c1_n2, 
                         scape_reps, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2101 <- assess_peaks_R(n, 
                         k = 1,
                         a, 
                         c = 0, 
                         s, 
                         R = 1,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k1_n2,
                         IM_cs = IM_c0_n2, 
                         scape_reps = 200, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2001 <- assess_peaks_R(n, 
                         k = 0,
                         a, 
                         c = 0, 
                         s, 
                         R = 1,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k0_n2,
                         IM_cs = IM_c0_n2,
                         scape_reps = 200, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start,
                         start_seqs = metaseqs_n2,
                         max_steps)


# asymmetry in mutation steps between species; running the adaptive walks on the same landscapes as above, just with asymmetry in "mutation rate"
set.seed(2512)

peaks_nkcs_2011_R <- assess_peaks_R_input(n, 
                         k = 0,
                         a, 
                         c = 1, 
                         s, 
                         R = 2,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k0_n2,
                         IM_cs = IM_c1_n2, 
                         peaks_nkcs_2011[[4]],
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2111_R <- assess_peaks_R_input(n, 
                         k = 1,
                         a, 
                         c = 1, 
                         s, 
                         R = 2,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k1_n2,
                         IM_cs = IM_c1_n2,
                         peaks_nkcs_2111[[4]],
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2021_R <- assess_peaks_R_input(n, 
                         k = 0,
                         a, 
                         c = 2, 
                         s, 
                         R = 2,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k0_n2,
                         IM_cs = IM_c2_n2,
                         peaks_nkcs_2021[[4]],
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2121_R <- assess_peaks_R_input(n, 
                         k = 1,
                         a, 
                         c = 2, 
                         s, 
                         R = 2,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k1_n2,
                         IM_cs = IM_c2_n2, 
                         peaks_nkcs_2121[[4]],
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)


# randomness in mutation steps between species; running the adaptive walks on the same landscapes as above, just without fixed order in mutation sequence
set.seed(2512)

peaks_nkcs_2011_Random <- assess_peaks_R_input(n, 
                         k = 0,
                         a, 
                         c = 1, 
                         s, 
                         R = NA,
                         lambda_R, # draw the number of mutational steps/species from a poisson distribution
                         s_tot, 
                         IM_ks = IM_k0_n2,
                         IM_cs = IM_c1_n2, 
                         peaks_nkcs_2011[[4]], # running the adaptive walks with asymmetry on the same landscapes as above
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2111_Random <- assess_peaks_R_input(n, 
                         k = 1,
                         a, 
                         c = 1, 
                         s, 
                         R = NA,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k1_n2,
                         IM_cs = IM_c1_n2,
                         peaks_nkcs_2111[[4]],
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2021_Random <- assess_peaks_R_input(n, 
                         k = 0,
                         a, 
                         c = 2, 
                         s, 
                         R = NA,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k0_n2,
                         IM_cs = IM_c2_n2,
                         peaks_nkcs_2021[[4]],
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)

peaks_nkcs_2121_Random <- assess_peaks_R_input(n, 
                         k = 1,
                         a, 
                         c = 2, 
                         s, 
                         R = NA,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k1_n2,
                         IM_cs = IM_c2_n2, 
                         peaks_nkcs_2121[[4]],
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = metaseqs_n2,
                         max_steps)


## N' = 4 (static NK comparison)
set.seed(2512)


peaks_nkcs_4001 <- assess_peaks_R(n = 4, 
                         k = 0,
                         a, 
                         c = 0, 
                         s = 0, 
                         R = 1,
                         R_lambda,
                         s_tot = 1, 
                         IM_ks = IM_k0_n4,
                         IM_cs = IM_c0_n4, 
                         scape_reps = 200, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start,
                         start_seqs = metaseqs_n4, 
                         max_steps)

peaks_nkcs_4101 <- assess_peaks_R(n = 4, 
                         k = 1,
                         a, 
                         c = 0, 
                         s = 0, 
                         R = 1,
                         R_lambda,
                         s_tot, 
                         IM_ks = IM_k1_n4,
                         IM_cs = IM_c0_n4, 
                         scape_reps = 40, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start,
                         start_seqs = metaseqs_n4, 
                         max_steps)

peaks_nkcs_4201 <- assess_peaks_R(n = 4, 
                         k = 2,
                         a, 
                         c = 0, 
                         s = 0, 
                         R = 1,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k2_n4,
                         IM_cs = IM_c0_n4,
                         scape_reps = 40, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start,
                         start_seqs = metaseqs_n4,
                         max_steps)

peaks_nkcs_4301 <- assess_peaks_R(n = 4, 
                         k = 3,
                         a, 
                         c = 0, 
                         s = 0, 
                         R = 1,
                         lambda_R,
                         s_tot, 
                         IM_ks = IM_k3_n4,
                         IM_cs = IM_c0_n4,
                         scape_reps = 200, 
                         fitness_contrib, 
                         fitness_calculation,
                         fit_mean, 
                         fit_sd, 
                         walk_reps, 
                         walk_type, 
                         walk_start,
                         start_seqs = metaseqs_n4, 
                         max_steps)

peaks_total <- dplyr::bind_rows(peaks_nkcs_4001[[1]],
                                peaks_nkcs_4101[[1]],
                                peaks_nkcs_4201[[1]],
                                peaks_nkcs_4301[[1]],
                                peaks_nkcs_2121[[1]],
                                peaks_nkcs_2111[[1]],
                                peaks_nkcs_2101[[1]],
                                peaks_nkcs_2021[[1]],
                                peaks_nkcs_2011[[1]],
                                peaks_nkcs_2001[[1]]) #the bind_rows function allows me to bind dfs with different column numbers; missing values are filled with NA; this is because I want to compare the effect of variable n 

peaks_total_R <- dplyr::bind_rows(peaks_nkcs_2111_R[[1]],
                                peaks_nkcs_2011_R[[1]],
                                peaks_nkcs_2121_R[[1]],
                                peaks_nkcs_2021_R[[1]],
                                peaks_nkcs_2111_Random[[1]],
                                peaks_nkcs_2011_Random[[1]],
                                peaks_nkcs_2121_Random[[1]],
                                peaks_nkcs_2021_Random[[1]])

peaks_total$reached <- peaks_total$fitness == peaks_total$global_peak # I could also just check if rank == 1
peaks_total_R$reached <- peaks_total_R$fitness == peaks_total_R$global_peak # I could also just check if rank == 1

```

## 1.3) summarising the results
```{r}

#### I recode the ranks ranks to shift everything on the same scale (e.g., when C = 0, there are only 4 distinct fitness ranks for a species -> I shift the ranks so they cover the same scale as the 16 unique ranks possible on landscapes with C > 0)

peaks_total$re_rank <- peaks_total$rank

# in the absence of intergenomic epistasis ther are only 4 distinct fitness ranks per species
peaks_total[peaks_total$c == 0 & peaks_total$n == 2 & peaks_total$rank == 1, "re_rank"] <- 1
peaks_total[peaks_total$c == 0 & peaks_total$n == 2 & peaks_total$rank == 2, "re_rank"] <- 5
peaks_total[peaks_total$c == 0 & peaks_total$n == 2 & peaks_total$rank == 3, "re_rank"] <- 9
peaks_total[peaks_total$c == 0 & peaks_total$n == 2 & peaks_total$rank == 4, "re_rank"] <- 13

# depending on the intergenomic interaction matrix there is some neutrality/redundancy between metagenotypes and therefore less fitness ranks
peaks_total[peaks_total$c == 1 & peaks_total$rank == 2 & peaks_total$c_rep == 1, "re_rank"] <- 3
peaks_total[peaks_total$c == 1 & peaks_total$rank == 3 & peaks_total$c_rep == 1, "re_rank"] <- 5
peaks_total[peaks_total$c == 1 & peaks_total$rank == 4 & peaks_total$c_rep == 1, "re_rank"] <- 7
peaks_total[peaks_total$c == 1 & peaks_total$rank == 5 & peaks_total$c_rep == 1, "re_rank"] <- 9
peaks_total[peaks_total$c == 1 & peaks_total$rank == 6 & peaks_total$c_rep == 1, "re_rank"] <- 11
peaks_total[peaks_total$c == 1 & peaks_total$rank == 7 & peaks_total$c_rep == 1, "re_rank"] <- 13
peaks_total[peaks_total$c == 1 & peaks_total$rank == 8 & peaks_total$c_rep == 1, "re_rank"] <- 15

peaks_total[peaks_total$c == 1 & peaks_total$rank == 2 & peaks_total$c_rep == 4 & peaks_total$species == 2, "re_rank"] <- 3
peaks_total[peaks_total$c == 1 & peaks_total$rank == 3 & peaks_total$c_rep == 4 & peaks_total$species == 2, "re_rank"] <- 5
peaks_total[peaks_total$c == 1 & peaks_total$rank == 4 & peaks_total$c_rep == 4 & peaks_total$species == 2, "re_rank"] <- 7
peaks_total[peaks_total$c == 1 & peaks_total$rank == 5 & peaks_total$c_rep == 4 & peaks_total$species == 2, "re_rank"] <- 9
peaks_total[peaks_total$c == 1 & peaks_total$rank == 6 & peaks_total$c_rep == 4 & peaks_total$species == 2, "re_rank"] <- 11
peaks_total[peaks_total$c == 1 & peaks_total$rank == 7 & peaks_total$c_rep == 4 & peaks_total$species == 2, "re_rank"] <- 13
peaks_total[peaks_total$c == 1 & peaks_total$rank == 8 & peaks_total$c_rep == 4 & peaks_total$species == 2, "re_rank"] <- 15

## same for variable R
peaks_total_R$re_rank <- peaks_total_R$rank

# in the absence of intergenomic epistasis ther are only 4 distinct fitness ranks per species
peaks_total_R[peaks_total_R$c == 0 & peaks_total_R$rank == 1, "re_rank"] <- 1
peaks_total_R[peaks_total_R$c == 0 & peaks_total_R$rank == 2, "re_rank"] <- 5
peaks_total_R[peaks_total_R$c == 0 & peaks_total_R$rank == 3, "re_rank"] <- 9
peaks_total_R[peaks_total_R$c == 0 & peaks_total_R$rank == 4, "re_rank"] <- 13

# depending on the intergenomic interaction matrix there is some neutrality/redundancy between metagenotypes and therefore less fitness ranks
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 2 & peaks_total_R$c_rep == 1, "re_rank"] <- 3
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 3 & peaks_total_R$c_rep == 1, "re_rank"] <- 5
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 4 & peaks_total_R$c_rep == 1, "re_rank"] <- 7
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 5 & peaks_total_R$c_rep == 1, "re_rank"] <- 9
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 6 & peaks_total_R$c_rep == 1, "re_rank"] <- 11
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 7 & peaks_total_R$c_rep == 1, "re_rank"] <- 13
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 8 & peaks_total_R$c_rep == 1, "re_rank"] <- 15

peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 2 & peaks_total_R$c_rep == 4 & peaks_total_R$species == 2, "re_rank"] <- 3
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 3 & peaks_total_R$c_rep == 4 & peaks_total_R$species == 2, "re_rank"] <- 5
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 4 & peaks_total_R$c_rep == 4 & peaks_total_R$species == 2, "re_rank"] <- 7
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 5 & peaks_total_R$c_rep == 4 & peaks_total_R$species == 2, "re_rank"] <- 9
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 6 & peaks_total_R$c_rep == 4 & peaks_total_R$species == 2, "re_rank"] <- 11
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 7 & peaks_total_R$c_rep == 4 & peaks_total_R$species == 2, "re_rank"] <- 13
peaks_total_R[peaks_total_R$c == 1 & peaks_total_R$rank == 8 & peaks_total_R$c_rep == 4 & peaks_total_R$species == 2, "re_rank"] <- 15

## summarise
peaks_total_ranked_summarised <- as.data.frame(peaks_total[peaks_total$step < max_steps,] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walking, re_rank, species) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_cycle_summarised <- as.data.frame(peaks_total[peaks_total$step == max_steps,] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walking, species) |>
                            dplyr::summarise(cycle_count = n())) 
peaks_total_cycle_summarised$re_rank <- 17 # I assign the cycles rank "17" for plotting reasons; obviously only works for my 2 sp/2 loci setup 

peaks_total_ranked_summarised <- merge(peaks_total_ranked_summarised, 
      peaks_total_cycle_summarised, 
      all.x = TRUE, all.y = TRUE)

## calculate percentages 
peaks_total_ranked_summarised$tot_reps <- walk_reps
peaks_total_ranked_summarised$prop_rank_peaked <- peaks_total_ranked_summarised$rank_peaked/peaks_total_ranked_summarised$tot_reps
peaks_total_ranked_summarised$prop_cycle <- peaks_total_ranked_summarised$cycle_count/peaks_total_ranked_summarised$tot_reps

# repeat for simulations with different mutation rounds
peaks_total_ranked_summarised_R <- as.data.frame(peaks_total_R[peaks_total_R$step < max_steps & !is.na(peaks_total_R$R),] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walking, re_rank, species, R) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_cycle_summarised_R <- as.data.frame(peaks_total_R[peaks_total_R$step >= max_steps & !is.na(peaks_total_R$R),] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walking, species, R) |>
                            dplyr::summarise(cycle_count = n())) 
peaks_total_cycle_summarised_R$re_rank <- 17 

peaks_total_ranked_summarised_Ran <- as.data.frame(peaks_total_R[peaks_total_R$step < 1000 & is.na(peaks_total_R$R),] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walking, re_rank, species, R) |>
                            dplyr::summarise(rank_peaked = n())) 


peaks_total_ranked_summarised_R <- merge(peaks_total_ranked_summarised_R, 
      peaks_total_cycle_summarised_R,
      all.x = TRUE, all.y = TRUE)

peaks_total_ranked_summarised_R <- merge(peaks_total_ranked_summarised_R, 
      peaks_total_ranked_summarised_Ran,
      all.x = TRUE, all.y = TRUE)

## calculate percentages 
peaks_total_ranked_summarised_R$tot_reps <- walk_reps
peaks_total_ranked_summarised_R$prop_rank_peaked <- peaks_total_ranked_summarised_R$rank_peaked/peaks_total_ranked_summarised_R$tot_reps
peaks_total_ranked_summarised_R$prop_cycle <- peaks_total_ranked_summarised_R$cycle_count/peaks_total_ranked_summarised_R$tot_reps

####### above, all df have separate rows for the different species; here we combine both
# combine both species into a single data frame and give each landscape a unique ID
peaks_total_ranked2 <- as.data.frame(peaks_total[peaks_total$n == 2 &
                                                   peaks_total$step < max_steps &
                                                              peaks_total$walking == "random",] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walk_rep, re_rank, species) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_ranked2_cyc <- as.data.frame(peaks_total[peaks_total$n == 2 &
                                                   peaks_total$step >= max_steps &
                                                              peaks_total$walking == "random",] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walk_rep, re_rank, species) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_ranked2_cyc$re_rank <- 17

peaks_total_ranked2 <- bind_rows(peaks_total_ranked2, peaks_total_ranked2_cyc)

peaks_total_ranked2_comb <- peaks_total_ranked2[peaks_total_ranked2$species == 1,]

colnames(peaks_total_ranked2_comb)[9] <- "re_rank_sp1"
peaks_total_ranked2_comb$re_rank_sp2 <- peaks_total_ranked2[peaks_total_ranked2$species == 2, "re_rank"]

peaks_total_ranked2_summarised <- as.data.frame(peaks_total_ranked2_comb |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, re_rank_sp1, re_rank_sp2, species) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_ranked2_summarised$landscape_ID <- interaction(peaks_total_ranked2_summarised$n, peaks_total_ranked2_summarised$k, peaks_total_ranked2_summarised$c, peaks_total_ranked2_summarised$c_rep, peaks_total_ranked2_summarised$scape_rep)

### same but with R = 2
peaks_total_ranked2_R <- as.data.frame(peaks_total_R[peaks_total_R$n == 2 &
                                                   peaks_total_R$step < max_steps &
                                                              peaks_total_R$walking == "random",] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walk_rep, re_rank, species, R) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_ranked2_cyc_R <- as.data.frame(peaks_total_R[peaks_total_R$n == 2 &
                                                   peaks_total_R$step >= max_steps &
                                                              peaks_total_R$walking == "random",] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walk_rep, re_rank, species, R) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_ranked2_cyc_R$re_rank <- 17 

peaks_total_ranked2_R <- bind_rows(peaks_total_ranked2_R)

peaks_total_ranked2_comb_R <- peaks_total_ranked2_R[peaks_total_ranked2_R$species == 1,]

colnames(peaks_total_ranked2_comb_R)[9] <- "re_rank_sp1"
peaks_total_ranked2_comb_R$re_rank_sp2 <- peaks_total_ranked2_R[peaks_total_ranked2_R$species == 2, "re_rank"]

peaks_total_ranked2_summarised_R <- as.data.frame(peaks_total_ranked2_comb_R |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, re_rank_sp1, re_rank_sp2, species, R) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_ranked2_summarised_R$landscape_ID <- interaction(peaks_total_ranked2_summarised_R$n, peaks_total_ranked2_summarised_R$k, peaks_total_ranked2_summarised_R$c, peaks_total_ranked2_summarised_R$c_rep, peaks_total_ranked2_summarised_R$scape_rep)

```

## 1.4) Export 
```{r}
#save data
save(peaks_total, # summary output of every single replicate walk on every replicate landscape
     peaks_total_R, # summary output of every single replicate walk on every replicate landscape for R = 2
     #peaks_summarised, # this is for exploratory plotting; I grouped the results by how many species reach the global fitness peak
     #peaks_summarised_cycles, # this is for exploratory plotting; I grouped the results by how often cycling occurs
     peaks_total_ranked_summarised, # endpoints grouped by how often they occur
     peaks_total_ranked_summarised_R, # endpoints grouped by how often they occur for R = 2
     peaks_total_ranked2_summarised, # endpoints grouped by how often they occur; both species combined and only for random adaptive walks
     peaks_total_ranked2_summarised_R, # endpoints grouped by how often they occur; both species combined and only for random adaptive walks for asymmetric mutation rates
     peaks_nkcs_2121, # raw simulation output
      peaks_nkcs_2111,
      peaks_nkcs_2101,
      peaks_nkcs_2021,
      peaks_nkcs_2011,
      peaks_nkcs_2001,
     peaks_nkcs_2111_R,
     peaks_nkcs_2011_R,
     peaks_nkcs_2121_R,
     peaks_nkcs_2021_R,
     peaks_nkcs_2111_Random,
     peaks_nkcs_2011_Random,
     peaks_nkcs_2121_Random,
     peaks_nkcs_2021_Random,
     peaks_nkcs_4001,
                                peaks_nkcs_4101,
                                peaks_nkcs_4201,
                                peaks_nkcs_4301,
     file = "NKC_landscapes_final")
```



# 2.) Seascapes simulations!
## 2.1) Parameters
```{r}
set.seed(2512) # for reproducibility

# most parameters are kept the same from the NKC simulations; therefor the parameters chunk from the NKC model must be run before this
p = 0 # number of pleiotropic loci; I have not actually implemented this yet lol but I also don't need it - take it as free future inspiration
env_tot = 2 # total number of environments in the system
lambda_change = 1 # if I want to draw the number of mutational steps from a poisson distribution
max_steps = 250

# defining the starting sequences for N = 4, so I can cycle through all possible starting points
types_n4 <- gtools::permutations(a, 4, c(1:a), repeats = TRUE) # all possible metagenotypes
seqs_n4 <- split(types_n4, row(types_n4)) # break into list, where every metagenotype is an entry
seqs_n4 <- lapply(seqs_n4, as.numeric) # converting into numbers

# defining all the interaction matrices outside the simulations for more reproducibility; for this we can implement interaction patterns for k_e that follow interactions for c in the NKC model (types of interaction matrices)
IM_sea_temp <- matrix(4, 4, data = rep(0,16))

# no genetic interaction; K = 0, K_e = 0
IM_sea_k0_ke0 <- build_IMk(IM = "R",
                      4,
                      0,
                      1,
                      1) # only one possible layout

# only interactions between loci that encode for the same environment; K = 1, K_e = 0
IM_sea_k1_ke0 <- IM_sea_temp
IM_sea_k1_ke0[1:n, 1:n] <- 1; IM_sea_k1_ke0[(n+1):(2*n), (n+1):(2*n)] <- 1
IM_sea_k1_ke0 <- list(IM_sea_k1_ke0)

# only interactions between loci that encode for different environments; K = 0, K_e = 1
IM_sea_temp <- IM_sea_temp
IM_sea_temp[row(IM_sea_temp) == col(IM_sea_temp)] <- 1
IM_sea_k0_ke1 <- list()

# "symmetric" -> borrowing from NKC
# both loci interact with the same locus
IM_sea_k0_ke1[[1]] <- IM_sea_temp
IM_sea_k0_ke1[[1]][1:n, (n+1):(2*n)] <- IM_c1_n2[[1]][[1]]
IM_sea_k0_ke1[[1]][(n+1):(2*n), 1:n] <- IM_c1_n2[[1]][[2]]

# all loci interacting
IM_sea_k0_ke1[[2]] <- IM_sea_temp
IM_sea_k0_ke1[[2]][1:n, (n+1):(2*n)] <- IM_c1_n2[[2]][[1]]
IM_sea_k0_ke1[[2]][(n+1):(2*n), 1:n] <- IM_c1_n2[[2]][[2]]

# asymmetric
# all loci involved in interaction
IM_sea_k0_ke1[[3]] <- IM_sea_temp
IM_sea_k0_ke1[[3]][1:n, (n+1):(2*n)] <- IM_c1_n2[[3]][[1]]
IM_sea_k0_ke1[[3]][(n+1):(2*n), 1:n] <- IM_c1_n2[[3]][[2]]

# all loci involved in interaction for one species; only one locus for the other
IM_sea_k0_ke1[[4]] <- IM_sea_temp
IM_sea_k0_ke1[[4]][1:n, (n+1):(2*n)] <- IM_c1_n2[[4]][[1]]
IM_sea_k0_ke1[[4]][(n+1):(2*n), 1:n] <- IM_c1_n2[[4]][[2]]

# only interactions between loci that encode for different environments; K = 0, K_e = 2
IM_sea_k0_ke2 <- list(IM_sea_temp)
IM_sea_k0_ke2[[1]][1:n, (n+1):(2*n)] <- matrix(2, 2, data = rep(1,4))
IM_sea_k0_ke2[[1]][(n+1):(2*n), 1:n] <- matrix(2, 2, data = rep(1,4))

# within and between loci that encode for different environments; K = 1, K_e = 1
IM_sea_temp <- IM_sea_k1_ke0[[1]]
IM_sea_k1_ke1 <- list()

# "symmetric" -> borrowing from NKC
# both loci interact with the same locus
IM_sea_k1_ke1[[1]] <- IM_sea_temp
IM_sea_k1_ke1[[1]][1:n, (n+1):(2*n)] <- IM_c1_n2[[1]][[1]]
IM_sea_k1_ke1[[1]][(n+1):(2*n), 1:n] <- IM_c1_n2[[1]][[2]]

# all loci interacting
IM_sea_k1_ke1[[2]] <- IM_sea_temp
IM_sea_k1_ke1[[2]][1:n, (n+1):(2*n)] <- IM_c1_n2[[2]][[1]]
IM_sea_k1_ke1[[2]][(n+1):(2*n), 1:n] <- IM_c1_n2[[2]][[2]]

# asymmetric
# all loci involved in interaction
IM_sea_k1_ke1[[3]] <- IM_sea_temp
IM_sea_k1_ke1[[3]][1:n, (n+1):(2*n)] <- IM_c1_n2[[3]][[1]]
IM_sea_k1_ke1[[3]][(n+1):(2*n), 1:n] <- IM_c1_n2[[3]][[2]]

# all loci involved in interaction for one species; only one locus for the other
IM_sea_k1_ke1[[4]] <- IM_sea_temp
IM_sea_k1_ke1[[4]][1:n, (n+1):(2*n)] <- IM_c1_n2[[4]][[1]]
IM_sea_k1_ke1[[4]][(n+1):(2*n), 1:n] <- IM_c1_n2[[4]][[2]]

# fully epistatic
IM_sea_k1_ke2 <- list(matrix(4, 4, data = rep(1,16)))

```

## 2.2) Convert NKC landscapes
```{r}

scapes_nkke_400 <- NKC_to_NKsea(peaks_nkcs_2001[[4]],
             env_tot,
             k_reps = 1,
             c_reps = 1,
             scape_reps = 200,
             n = 2)

scapes_nkke_401 <- NKC_to_NKsea(peaks_nkcs_2011[[4]],
             env_tot,
             k_reps = 1,
             c_reps = 4,
             scape_reps = 50,
             n = 2)

scapes_nkke_402 <- NKC_to_NKsea(peaks_nkcs_2021[[4]],
             env_tot,
             k_reps = 1,
             c_reps = 1,
             scape_reps = 200,
             n = 2)

scapes_nkke_410 <- NKC_to_NKsea(peaks_nkcs_2101[[4]],
             env_tot,
             k_reps = 1,
             c_reps = 1,
             scape_reps = 200,
             n = 2)

scapes_nkke_411 <- NKC_to_NKsea(peaks_nkcs_2111[[4]],
             env_tot,
             k_reps = 1,
             c_reps = 4,
             scape_reps = 50,
             n = 2)

scapes_nkke_412 <- NKC_to_NKsea(peaks_nkcs_2121[[4]],
             env_tot,
             k_reps = 1,
             c_reps = 1,
             scape_reps = 200,
             n = 2)

```

## 2.3) Sail the seascapes
```{r}
set.seed(2512) # for reproducibility

# regular switching between abiotic environments
peaks_nkke_400 <- assess_peaks_sea_input(n, 
                         k = 0,
                         k_e = 0,
                         a, 
                         p,
                         change = 1,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k0_ke0,
                         scapes_nkke_400, 
                         scape_reps = 200,
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

set.seed(2512)
peaks_nkke_401 <- assess_peaks_sea_input(n, 
                         k = 0,
                         k_e = 1,
                         a, 
                         p,
                         change = 1,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k0_ke1,
                         scapes_nkke_401,
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_402 <- assess_peaks_sea_input(n, 
                         k = 0,
                         k_e = 2,
                         a, 
                         p,
                         change = 1,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k0_ke2,
                         scapes_nkke_402,
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_410 <- assess_peaks_sea_input(n, 
                         k = 1,
                         k_e = 0,
                         a, 
                         p,
                         change = 1,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k1_ke0,
                         scapes_nkke_410,
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_411 <- assess_peaks_sea_input(n, 
                         k = 1,
                         k_e = 1,
                         a, 
                         p,
                         change = 1,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k1_ke1,
                         scapes_nkke_411,
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_412 <- assess_peaks_sea_input(n, 
                         k = 1,
                         k_e = 2,
                         a, 
                         p,
                         change = 1,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k1_ke2,
                         scapes_nkke_412,
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

# asymmetric environment change (more time spent in environment 1)
set.seed(2512)

peaks_nkke_401_R <- assess_peaks_sea_input(n, 
                         k = 0,
                         k_e = 1,
                         a, 
                         p,
                         change = 2,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k0_ke1,
                         peaks_nkke_401[[3]],
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_402_R <- assess_peaks_sea_input(n, 
                         k = 0,
                         k_e = 2,
                         a, 
                         p,
                         change = 2,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k0_ke2,
                         peaks_nkke_402[[3]],
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_411_R <- assess_peaks_sea_input(n, 
                         k = 1,
                         k_e = 1,
                         a, 
                         p,
                         change = 2,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k1_ke1,
                         peaks_nkke_411[[3]],
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_412_R <- assess_peaks_sea_input(n, 
                         k = 1,
                         k_e = 2,
                         a, 
                         p,
                         change = 2,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k1_ke2,
                         peaks_nkke_412[[3]],
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)


# stochastic environment change (randomly changing between environments; mutation rounds spent in environment drawn from poisson distribution)
set.seed(2512)

peaks_nkke_401_Random <- assess_peaks_sea_input(n, 
                         k = 0,
                         k_e = 1,
                         a, 
                         p,
                         change = NA,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k0_ke1,
                         peaks_nkke_401[[3]],
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_402_Random <- assess_peaks_sea_input(n, 
                         k = 0,
                         k_e = 2,
                         a, 
                         p,
                         change = NA,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k0_ke2,
                         peaks_nkke_402[[3]],
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_411_Random <- assess_peaks_sea_input(n, 
                         k = 1,
                         k_e = 1,
                         a, 
                         p,
                         change = NA,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k1_ke1,
                         peaks_nkke_411[[3]],
                         scape_reps, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)

peaks_nkke_412_Random <- assess_peaks_sea_input(n, 
                         k = 1,
                         k_e = 2,
                         a, 
                         p,
                         change = NA,
                         lambda_change,
                         env_tot,
                         IM_seas = IM_sea_k1_ke2,
                         peaks_nkke_412[[3]],
                         scape_reps = 200, 
                         walk_reps, 
                         walk_type, 
                         walk_start, 
                         start_seqs = seqs_n4,
                         max_steps)


peaks_total_sea <- dplyr::bind_rows(peaks_nkke_400[[1]], # combine all simulations in one main data frame
                                    peaks_nkke_401[[1]],
                                    peaks_nkke_402[[1]],
                                    peaks_nkke_410[[1]],
                                    peaks_nkke_411[[1]],
                                    peaks_nkke_412[[1]]) 

# for irregular environmental change
peaks_total_sea_R <- dplyr::bind_rows(peaks_nkke_401_R[[1]],
                                    peaks_nkke_402_R[[1]],
                                    peaks_nkke_411_R[[1]],
                                    peaks_nkke_412_R[[1]],
                                    peaks_nkke_401_Random[[1]],
                                    peaks_nkke_402_Random[[1]],
                                    peaks_nkke_411_Random[[1]],
                                    peaks_nkke_412_Random[[1]]) 

peaks_total_sea$E1.reached <- peaks_total_sea$E1.fitness == peaks_total_sea$global_peak_E1 # I could also just check if rank == 1... O:-)
peaks_total_sea$E2.reached <- peaks_total_sea$E2.fitness == peaks_total_sea$global_peak_E2

peaks_total_sea_R$E1.reached <- peaks_total_sea_R$E1.fitness == peaks_total_sea_R$global_peak_E1 
peaks_total_sea_R$E2.reached <- peaks_total_sea_R$E2.fitness == peaks_total_sea_R$global_peak_E2

```

## 2.3) summarise
```{r}
#### I recode the ranks ranks to shift everything on the same scale (e.g., when C = 0, there are only 4 distinct fitness ranks for a species -> I shift the ranks so they cover the same scale as the 16 unique ranks possible on landscapes with C > 0)

peaks_total_sea$E1.re_rank <- peaks_total_sea$E1.rank
peaks_total_sea$E2.re_rank <- peaks_total_sea$E2.rank

# in the absence of intergenomic epistasis ther are only 4 distinct fitness ranks per species
peaks_total_sea[peaks_total_sea$k_e == 0 & peaks_total_sea$E1.rank == 1, "E1.re_rank"] <- 1
peaks_total_sea[peaks_total_sea$k_e == 0 & peaks_total_sea$E1.rank == 2, "E1.re_rank"] <- 5
peaks_total_sea[peaks_total_sea$k_e == 0 & peaks_total_sea$E1.rank == 3, "E1.re_rank"] <- 9
peaks_total_sea[peaks_total_sea$k_e == 0 & peaks_total_sea$E1.rank == 4, "E1.re_rank"] <- 13

peaks_total_sea[peaks_total_sea$k_e == 0 & peaks_total_sea$E2.rank == 1, "E2.re_rank"] <- 1
peaks_total_sea[peaks_total_sea$k_e == 0 & peaks_total_sea$E2.rank == 2, "E2.re_rank"] <- 5
peaks_total_sea[peaks_total_sea$k_e == 0 & peaks_total_sea$E2.rank == 3, "E2.re_rank"] <- 9
peaks_total_sea[peaks_total_sea$k_e == 0 & peaks_total_sea$E2.rank == 4, "E2.re_rank"] <- 13

# depending on the intergenomic interaction matrix there is some neutrality/redundancy between metagenotypes and therefore less fitness ranks
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E1.rank == 2 & peaks_total_sea$sea_rep == 1, "E1.re_rank"] <- 3
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E1.rank == 3 & peaks_total_sea$sea_rep == 1, "E1.re_rank"] <- 5
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E1.rank == 4 & peaks_total_sea$sea_rep == 1, "E1.re_rank"] <- 7
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E1.rank == 5 & peaks_total_sea$sea_rep == 1, "E1.re_rank"] <- 9
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E1.rank == 6 & peaks_total_sea$sea_rep == 1, "E1.re_rank"] <- 11
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E1.rank == 7 & peaks_total_sea$sea_rep == 1, "E1.re_rank"] <- 13
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E1.rank == 8 & peaks_total_sea$sea_rep == 1, "E1.re_rank"] <- 15

peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 2 & peaks_total_sea$sea_rep == 1, "E2.re_rank"] <- 3
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 3 & peaks_total_sea$sea_rep == 1, "E2.re_rank"] <- 5
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 4 & peaks_total_sea$sea_rep == 1, "E2.re_rank"] <- 7
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 5 & peaks_total_sea$sea_rep == 1, "E2.re_rank"] <- 9
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 6 & peaks_total_sea$sea_rep == 1, "E2.re_rank"] <- 11
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 7 & peaks_total_sea$sea_rep == 1, "E2.re_rank"] <- 13
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 8 & peaks_total_sea$sea_rep == 1, "E2.re_rank"] <- 15

peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 2 & peaks_total_sea$sea_rep == 4, "E2.re_rank"] <- 3
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 3 & peaks_total_sea$sea_rep == 4, "E2.re_rank"] <- 5
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 4 & peaks_total_sea$sea_rep == 4, "E2.re_rank"] <- 7
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 5 & peaks_total_sea$sea_rep == 4, "E2.re_rank"] <- 9
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 6 & peaks_total_sea$sea_rep == 4, "E2.re_rank"] <- 11
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 7 & peaks_total_sea$sea_rep == 4, "E2.re_rank"] <- 13
peaks_total_sea[peaks_total_sea$k_e == 1 & peaks_total_sea$E2.rank == 8 & peaks_total_sea$sea_rep == 4, "E2.re_rank"] <- 15

## same for variable R
peaks_total_sea_R$E1.re_rank <- peaks_total_sea_R$E1.rank
peaks_total_sea_R$E2.re_rank <- peaks_total_sea_R$E2.rank

# in the absence of intergenomic epistasis ther are only 4 distinct fitness ranks per species
peaks_total_sea_R[peaks_total_sea_R$k_e == 0 & peaks_total_sea_R$E1.rank == 1, "E1.re_rank"] <- 1
peaks_total_sea_R[peaks_total_sea_R$k_e == 0 & peaks_total_sea_R$E1.rank == 2, "E1.re_rank"] <- 5
peaks_total_sea_R[peaks_total_sea_R$k_e == 0 & peaks_total_sea_R$E1.rank == 3, "E1.re_rank"] <- 9
peaks_total_sea_R[peaks_total_sea_R$k_e == 0 & peaks_total_sea_R$E1.rank == 4, "E1.re_rank"] <- 13

peaks_total_sea_R[peaks_total_sea_R$k_e == 0 & peaks_total_sea_R$E2.rank == 1, "E2.re_rank"] <- 1
peaks_total_sea_R[peaks_total_sea_R$k_e == 0 & peaks_total_sea_R$E2.rank == 2, "E2.re_rank"] <- 5
peaks_total_sea_R[peaks_total_sea_R$k_e == 0 & peaks_total_sea_R$E2.rank == 3, "E2.re_rank"] <- 9
peaks_total_sea_R[peaks_total_sea_R$k_e == 0 & peaks_total_sea_R$E2.rank == 4, "E2.re_rank"] <- 13

# depending on the intergenomic interaction matrix there is some neutrality/redundancy between metagenotypes and therefore less fitness ranks
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E1.rank == 2 & peaks_total_sea_R$sea_rep == 1, "E1.re_rank"] <- 3
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E1.rank == 3 & peaks_total_sea_R$sea_rep == 1, "E1.re_rank"] <- 5
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E1.rank == 4 & peaks_total_sea_R$sea_rep == 1, "E1.re_rank"] <- 7
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E1.rank == 5 & peaks_total_sea_R$sea_rep == 1, "E1.re_rank"] <- 9
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E1.rank == 6 & peaks_total_sea_R$sea_rep == 1, "E1.re_rank"] <- 11
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E1.rank == 7 & peaks_total_sea_R$sea_rep == 1, "E1.re_rank"] <- 13
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E1.rank == 8 & peaks_total_sea_R$sea_rep == 1, "E1.re_rank"] <- 15

peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 2 & peaks_total_sea_R$sea_rep == 1, "E2.re_rank"] <- 3
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 3 & peaks_total_sea_R$sea_rep == 1, "E2.re_rank"] <- 5
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 4 & peaks_total_sea_R$sea_rep == 1, "E2.re_rank"] <- 7
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 5 & peaks_total_sea_R$sea_rep == 1, "E2.re_rank"] <- 9
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 6 & peaks_total_sea_R$sea_rep == 1, "E2.re_rank"] <- 11
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 7 & peaks_total_sea_R$sea_rep == 1, "E2.re_rank"] <- 13
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 8 & peaks_total_sea_R$sea_rep == 1, "E2.re_rank"] <- 15

peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 2 & peaks_total_sea_R$sea_rep == 4, "E2.re_rank"] <- 3
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 3 & peaks_total_sea_R$sea_rep == 4, "E2.re_rank"] <- 5
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 4 & peaks_total_sea_R$sea_rep == 4, "E2.re_rank"] <- 7
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 5 & peaks_total_sea_R$sea_rep == 4, "E2.re_rank"] <- 9
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 6 & peaks_total_sea_R$sea_rep == 4, "E2.re_rank"] <- 11
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 7 & peaks_total_sea_R$sea_rep == 4, "E2.re_rank"] <- 13
peaks_total_sea_R[peaks_total_sea_R$k_e == 1 & peaks_total_sea_R$E2.rank == 8 & peaks_total_sea_R$sea_rep == 4, "E2.re_rank"] <- 15


peaks_sea_ranked_summarised <- as.data.frame(peaks_total_sea[peaks_total_sea$step < max_steps,] |> 
                            dplyr::group_by(k, k_e, n, a, sea_rep, scape_rep, walking, E1.re_rank, E2.re_rank) |>
                            dplyr::summarise(rank_peaked = n())) 
peaks_sea_ranked_summarised$cycle <- "no"

peaks_sea_cycle_summarised <- as.data.frame(peaks_total_sea[peaks_total_sea$step >= max_steps,] |> 
                            dplyr::group_by(k, k_e, n, a, sea_rep, scape_rep, walking, E1.re_rank, E2.re_rank) |>
                            dplyr::summarise(cycle_count = n())) 
peaks_sea_cycle_summarised$cycle <- "yes" 
#peaks_sea_cycle_summarised$E1.re_rank <- 17 # will do this later this time
#peaks_sea_cycle_summarised$E2.re_rank <- 17 # will do this later this time

peaks_sea_ranked_summarised <- merge(peaks_sea_ranked_summarised, 
      peaks_sea_cycle_summarised, 
      all.x = TRUE, all.y = TRUE)

## calculate percentages 
peaks_sea_ranked_summarised$tot_reps <- walk_reps
peaks_sea_ranked_summarised$prop_rank_peaked <- peaks_sea_ranked_summarised$rank_peaked/peaks_sea_ranked_summarised$tot_reps
peaks_sea_ranked_summarised$prop_cycle <- peaks_sea_ranked_summarised$cycle_count/peaks_sea_ranked_summarised$tot_reps

#### same but with irregular environmental change
peaks_sea_ranked_summarised_R <- as.data.frame(peaks_total_sea_R[peaks_total_sea_R$step < max_steps,] |> 
                            dplyr::group_by(k, k_e, n, a, sea_rep, scape_rep, walking, E1.re_rank, E2.re_rank, change) |>
                            dplyr::summarise(rank_peaked = n())) 
peaks_sea_ranked_summarised_R$cycle <- "no"

peaks_sea_cycle_summarised_R <- as.data.frame(peaks_total_sea_R[peaks_total_sea_R$step >= max_steps,] |> 
                            dplyr::group_by(k, k_e, n, a, sea_rep, scape_rep, walking, E1.re_rank, E2.re_rank, change) |>
                            dplyr::summarise(cycle_count = n())) 
peaks_sea_cycle_summarised_R$cycle <- "yes" 
#peaks_sea_cycle_summarised_R$E1.re_rank <- 17 # for plotting reasons
#peaks_sea_cycle_summarised_R$E2.re_rank <- 17 # for plotting reasons

peaks_sea_ranked_summarised_R <- merge(peaks_sea_ranked_summarised_R, 
      peaks_sea_cycle_summarised_R, 
      all.x = TRUE, all.y = TRUE)

## calculate percentages 
peaks_sea_ranked_summarised_R$tot_reps <- walk_reps
peaks_sea_ranked_summarised_R$prop_rank_peaked <- peaks_sea_ranked_summarised_R$rank_peaked/peaks_sea_ranked_summarised_R$tot_reps
peaks_sea_ranked_summarised_R$prop_cycle <- peaks_sea_ranked_summarised_R$cycle_count/peaks_sea_ranked_summarised_R$tot_reps

```

## 2.4) Export :-)
```{r}
save(peaks_total_sea,
     peaks_total_sea_R,
     peaks_sea_ranked_summarised, 
     peaks_sea_ranked_summarised_R,
     peaks_nkke_400, 
                                    peaks_nkke_401,
                                    peaks_nkke_402,
                                    peaks_nkke_410,
                                    peaks_nkke_411,
                                    peaks_nkke_412,
     peaks_nkke_401_R,
                                    peaks_nkke_402_R,
                                    peaks_nkke_411_R,
                                    peaks_nkke_412_R,
     peaks_nkke_401_Random,
                                    peaks_nkke_402_Random,
                                    peaks_nkke_411_Random,
                                    peaks_nkke_412_Random,
     file = "seascapes_final")

```