---
title: "NKC_exploration"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_knit$set(root.dir = "~/OneDrive - Universitaet Bern/NKC_project/R_scripts/") # set directory
```

# Set up workspace
```{r libraries}
rm (list = ls()) # clear environment

library(ggplot2) # for plotting
library(dplyr) # for constructing the data sets
library(gghalves) # for plotting mixed boxplots with points; I only used this for the graphs I put on my poster
library(ggtext) # to get different colour axis titles

library(ggraph) # for plotting networks -> adaptive walks representation
library(igraph) # for plotting networks -> adaptive walks representation

library(ggarrow) # to plot individual cycles
library(ggpubr) # to arrange multiple figures
library(egg) # to make plot insets

library(glmmTMB) # for mixed effect models

# load NKC functions
source(knitr::purl("NKC(S).Rmd", quiet=TRUE)) # to get the landscape visualisation functions for example

# load data of simulations
load("peaks_total7") 

```

# 1.) Plots for manuscript
```{r}
# main theme for all my figures
fig_theme <- theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        )

#capabilities("cairo") # I think this was to check whether I could save my pdfs with a special unicode character; but I no longer remember... sorry :-(

```

## Fig. 3 - fitness landscape example; R^2 version
This figure shows us the two-dimensional fitness mapping for all the metagenotypes in a community -> each metagenotype can correspond to a different fitness rank for the two species
```{r}
# recoding fitness landscapes; 
## in my model the alleles are encoded as 1 and 2, but I would different alleles for the two species to better distinguish them (differences in metagenotypes should be easier to spot this way)

scape_sp1 <- peaks_nkcs_2111[[4]][[2]][[13]][[1]] # take desired landscape replicate for species 1 = "focal species"

# recode alleles for focal species 
scape_sp1[scape_sp1$F.1 == 1, "F.1"] <- "a" 
scape_sp1[scape_sp1$F.1 == 2, "F.1"] <- "A"
scape_sp1[scape_sp1$F.2 == 1, "F.2"] <- "a"
scape_sp1[scape_sp1$F.2 == 2, "F.2"] <- "A"

# recode alleles for partner species
scape_sp1[scape_sp1$P.1 == 1, "P.1"] <- "b"
scape_sp1[scape_sp1$P.1 == 2, "P.1"] <- "B"
scape_sp1[scape_sp1$P.2 == 1, "P.2"] <- "b"
scape_sp1[scape_sp1$P.2 == 2, "P.2"] <- "B"

# rename columns, so I can combine the landscapes of both species next
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

# take the corresponding fitness landscape of species 2 in the chosen species pair
scape_sp2 <- peaks_nkcs_2111[[4]][[2]][[13]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine landscaps of sp1 and sp2
scapes_combined <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(scapes_combined)[c(9,10)] <- c("fitness_sp2", "rank_sp2") # adjust column names

# get the metagenotypes, so I can plot them; this is just for text in the plot
for (i in 1:16){
  
  scapes_combined$seq[i] <- paste(paste(scapes_combined[i, c("F.1", "F.2")], collapse = ""), "-", c(paste(scapes_combined[i, c("P.1", "P.2")], collapse = "")))
  
}

scapes_combined$background <- paste0(scapes_combined$P.1, scapes_combined$P.2) # genotype of sp2
scapes_combined$gen <- paste0(scapes_combined$F.1, scapes_combined$F.2) # genotype of sp1

# now I use my function from the NKC(S) code file to infer which metagenotypes are one-mutation step neighbours
visual_test_df <- visual_landscape(scapes_combined,
                 n = 2,
                  c = 1,
                 s = 1) # this is how I get the transitions between metagenotypes

# now I plot
lanscape_Rsqrd <- ggplot(visual_test_df,
       aes(x = rank_sp1,
           y = rank_sp2)) +
  geom_line(data = visual_test_df[visual_test_df$mut == "intra",],
            aes(group = group,
                linetype = mut,
                col = background),
            linewidth = 0.75) +
  geom_line(data = visual_test_df[visual_test_df$mut == "inter",],
            aes(group = group,
                linetype = mut),
            col = "grey",
            linewidth = 0.5) +
  geom_label(label = visual_test_df$seq,
             aes(col = background),
             linewidth = 0.6, # thickness of label border in mm
             size = 4.5, # size of label in mm
             fontface = "bold" # bold font
             ) +
  scale_x_continuous(breaks = c(1:16),
                     name = "Fitness rank focal species") +
  scale_y_continuous(breaks = c(1:16),
                     name = "Fitness rank partner species") +
  scale_colour_manual(values = c("dodgerblue", "darkblue", "slategrey", "purple"))+
  scale_linetype_manual(breaks = c("intra", "inter"),
                        values = c("solid", "dashed"))+
  ylab("Fitness rank partner species") +
  theme_classic() +
  fig_theme

# to save the figure
ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 19,
       height = 17,
       filename = "lanscape_Rsqrd_NKC_211_2_13.pdf",
       plot = lanscape_Rsqrd)

## versions of this figure I used in a presentation showing how to go from one-dimensional fitness mapping to two-dimensional fitness mapping
# lanscape_Rsqrd_sp1 <- ggplot(visual_test_df[visual_test_df$background == "bb",],
#        aes(x = rank_sp1,
#            y = rank_sp2)) +
#   geom_line(data = visual_test_df[visual_test_df$mut == "intra" &
#                                     visual_test_df$background == "bb",],
#             aes(group = group,
#                 linetype = mut,
#                 col = background),
#             linewidth = 0.75) +
#   geom_line(data = visual_test_df[visual_test_df$mut == "inter" &
#                                     visual_test_df$background == "bb",],
#             aes(group = group,
#                 linetype = mut),
#             col = "grey",
#             linewidth = 0.5) +
#   geom_label(label = visual_test_df[visual_test_df$background == "bb", "seq"],
#              aes(col = background),
#              linewidth = 0.6, # thickness of label border in mm
#              size = 4.5, # size of label in mm
#              fontface = "bold" # bold font
#              ) +
#   scale_x_continuous(breaks = c(1:16),
#                      name = "Fitness rank focal species",
#                      limits = c(1,16)) +
#   scale_y_continuous(breaks = c(1:16),
#                      name = "Fitness rank partner species",
#                      limits = c(1,16)) +
#   scale_colour_manual(values = c("dodgerblue", "darkblue", "slategrey", "purple"))+
#   scale_linetype_manual(breaks = c("intra", "inter"),
#                         values = c("solid", "dashed"))+
#   ylab("Fitness rank partner species") +
#   theme_classic() +
#   fig_theme
# 
# ggplot(visual_test_df[visual_test_df$gen == "Aa",],
#        aes(x = rank_sp1,
#            y = rank_sp2)) +
#   geom_line(data = visual_test_df[visual_test_df$mut == "intra" &
#                                     visual_test_df$gen == "Aa",],
#             aes(group = group,
#                 linetype = mut,
#                 col = background),
#             linewidth = 0.75) +
#   geom_line(data = visual_test_df[visual_test_df$mut == "inter" &
#                                     visual_test_df$gen == "Aa",],
#             aes(group = group,
#                 linetype = mut),
#             col = "grey",
#             linewidth = 0.5) +
#   geom_label(label = visual_test_df[visual_test_df$gen == "Aa", "seq"],
#              aes(col = background),
#              linewidth = 0.6, # thickness of label border in mm
#              size = 4.5, # size of label in mm
#              fontface = "bold" # bold font
#              ) +
#   scale_x_continuous(breaks = c(1:16),
#                      name = "Fitness rank focal species",
#                      limits = c(1,16)) +
#   scale_y_continuous(breaks = c(1:16),
#                      name = "Fitness rank partner species",
#                      limits = c(1,16)) +
#   scale_colour_manual(values = c("dodgerblue", "darkblue", "slategrey", "purple"))+
#   scale_linetype_manual(breaks = c("intra", "inter"),
#                         values = c("solid", "dashed"))+
#   ylab("Fitness rank partner species") +
#   theme_classic() +
#   fig_theme
# 
# ggsave(path = "../Figures/",
#        device = "pdf",
#        units = c("cm"),
#        width = 19,
#        height = 17,
#        filename = "lanscape_Rsqrd_NKC_211_2_30_sp1.pdf",
#        plot = lanscape_Rsqrd_sp1)
# 
# lanscape_R_sp1 <- ggplot(visual_test_df[visual_test_df$background == "bb",],
#        aes(x = rank_sp1,
#            y = background)) +
#   geom_label(label = visual_test_df[visual_test_df$background == "bb", "gen"],
#              aes(col = background),
#              linewidth = 0.6, # thickness of label border in mm
#              size = 4.5, # size of label in mm
#              fontface = "bold" # bold font
#              ) +
#   scale_x_continuous(breaks = c(2,16),
#                      labels = c("high",  "low"),
#                      name = "Fitness focal species",
#                      limits = c(2,16)) +
#   scale_colour_manual(values = c("dodgerblue", "darkblue", "slategrey", "purple"))+
#   scale_linetype_manual(breaks = c("intra", "inter"),
#                         values = c("solid", "dashed"))+
#   ylab("") +
#   theme_classic() +
#   fig_theme +
#   theme(axis.text.y = element_blank(),
#         axis.ticks.y = element_blank())
# 
# ggsave(path = "../Figures/",
#        device = "pdf",
#        units = c("cm"),
#        width = 19,
#        height = 5,
#        filename = "lanscape_R_NKC_211_2_30_sp1.pdf",
#        plot = lanscape_R_sp1)


```

## Fig 4a - Repeatability N = 2
This is the first results figure that shows how many adaptive walks lead to the same outcome on each of our fitness landscape replicates. Here we see the number of realised outcomes of adaptation as well as how often they are repeated on the same landscape
```{r}
localrep_N2 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "random",], # only random walks in main text
        aes(y = prop_rank_peaked, # plot proportions
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_violin(aes(y = prop_cycle, # I counted the cycles separately in the data frame, so we will handle them separately as well
                  x = rank),
              col = "grey45") +
  geom_rect(data = peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 & 
                                                      peaks_total_ranked_summarised$c == 0 &
                                                  peaks_total_ranked_summarised$scape_rep == 1 &
                                                   peaks_total_ranked_summarised$rank == 1 &
                                                   peaks_total_ranked_summarised$species == 1 &
                                       peaks_total_ranked_summarised$walking == "random",], # this was the only way I was able to plot a single rectangle per facet :-(
            aes(xmin = 4.5, 
                xmax = 16.5, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80", # putting a grey rectangle over the ranks that do not exist; for C = 0, there are only four possible fitness ranks per species
            alpha = 0.5,
            inherit.aes = FALSE) +
  geom_jitter(col = "forestgreen", # for equilibrium points
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  geom_jitter(aes(y = prop_cycle,
                  x = rank),
               col = "skyblue", # for cycling points
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the mean proportion of cycling/landscape
                  x = rank),
               fun = mean,
               geom = "crossbar",
               linewidth = 0.4,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the median proportion of cycling/landscape
                  x = rank),
               fun = median,
               geom = "point",
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character; unfortunately this does not allow for italics :-(
  fig_theme

# save the figure
ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode character
       units = c("cm"),
       width = 26,
       height = 17,
       filename = "localrep_N2.pdf",
       plot = localrep_N2)

```

## Fig 4c Repeatability N' = 4
To have a refernce for comparison of the intergenomic epistasis results, we also assess adaptation on equivalent single-species landscape with N' = 4 and K' = K + C
```{r}
localrep_N4 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 4 &
                                       peaks_total_ranked_summarised$walking == "random",], # only random walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
     theme_bw() +
  geom_violin(col = "grey45") +
  geom_jitter(col = "forestgreen", # here, I only have equilibrium outcomes
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  facet_grid( ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   limits = c(0.5,17.5),
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic("K'"))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape") +
  theme(axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y = element_text(size=16),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

# save the figure
ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 37,
       height = 10,
       filename = "localrep_N4.pdf",
       plot = localrep_N4)
```


## Fig 5 - effect of interaction matrices on repeatability
Here we show how patterns of repeatability for C = 1 differ between the different interaction networks used to couple the two species
```{r}

effectIM_N2 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                         peaks_total_ranked_summarised$c == 1 &
                                       peaks_total_ranked_summarised$walking == "random",], # only random walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_rect(data = peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                                   peaks_total_ranked_summarised$c == 1 &
                                                      peaks_total_ranked_summarised$c_rep == 1 &
                                                  peaks_total_ranked_summarised$scape_rep == 1 &
                                                   peaks_total_ranked_summarised$species == 1 &
                                       peaks_total_ranked_summarised$walking == "random", ][c(1,2),], # this was the only way I was able to plot a single rectangle per facet :-(
            aes(xmin = 8.5, 
                xmax = 16.5, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80", # putting a grey rectangle over the ranks that do not exist; for IM = 1, there are only eight possible fitness ranks per species
            alpha = 0.5,
            inherit.aes = FALSE) +
  geom_rect(data = peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                                   peaks_total_ranked_summarised$c == 1 &
                                                      peaks_total_ranked_summarised$c_rep == 4 &
                                                  peaks_total_ranked_summarised$scape_rep == 1 &
                                                   peaks_total_ranked_summarised$species == 1 &
                                       peaks_total_ranked_summarised$walking == "random", ][c(1,2),], # this was the only way I was able to plot a single rectangle per facet :-(
            aes(xmin = 8.5, 
                xmax = 16.5, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80", # putting a grey rectangle over the ranks that do not exist; for IM = 1, there are only eight possible fitness ranks per species
            alpha = 0.2,
            inherit.aes = FALSE) +
  geom_violin(col = "grey45") +
  geom_violin(aes(y = prop_cycle,
                  x = rank),
              col = "grey45") +
  geom_jitter(aes(col = as.factor(c_rep)),
              size = 2.5,
              height = 0.01,
              alpha = 0.5) +
  geom_jitter(aes(y = prop_cycle,
                  x = rank),
               col = "skyblue", # cycling points
              size = 2.5,
              height = 0.01,
              alpha = 0.5) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the mean proportion of cycling/landscape
                  x = rank),
               fun = mean,
               geom = "crossbar",
               linewidth = 0.4,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the median proportion of cycling/landscape
                  x = rank),
               fun = median,
               geom = "point",
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c_rep ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic("K"))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                     limits = c(0,1)) +
  scale_color_manual(values=c("forestgreen", "limegreen", "olivedrab2", "gold")) + # different colours for the four interaction networks
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = ggtext::element_markdown(),
        axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
        legend.position = "none",
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character

# save the figure
ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 21,
       filename = "effectIM_N2.pdf",
       plot = effectIM_N2)

```

## cycle investigation
This is a little code insert to extract some meaningful properties of the cycles, such as mean fitness of the species during the cycle in order to integrate the cycle results with the equilibrium results
```{r}
# For each combination of C = 1, 2 and K = 0, 1, I extract the cycles and extract the information I'm interested in
# for N = 2, K = 0, C = 1
cycles_nkc_201 <- NULL

c_rep <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 1 & 
                     peaks_total$step == 250 & # these are the simulations that were cut off at the number of maximum steps
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "c_rep"] # I want to know how many interaction network replicates I have because this differs between C = 1 and C  = 2

for (i in unique(c_rep)){ # for each interaction network replicate
  
  scape_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 1 & 
                              peaks_total$c_rep == i &
                           peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "scape_rep"]
  
  for (j in unique(scape_reps)) { # for each fitness landscape replicate
    
    walk_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 1 & 
                              peaks_total$c_rep == i &
                               peaks_total$scape_rep == j &
                           peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "walk_rep"]
    
    for (l in unique(walk_reps)) { # for each adaptive walk
      
      ranks_sp1 <- unique(peaks_nkcs_2011[[5]][[i]][[j]][[2]][[l]][[1]][c(230:250), "rank"]) # check how many unique metagenotypes there are during the last 20 steps of the adaptive walk
      ranks_sp2 <- unique(peaks_nkcs_2011[[5]][[i]][[j]][[2]][[l]][[2]][c(230:250), "rank"])
      
      # extract my information
      summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              walk_rep = l,
                              nb_in_cycle_sp1 = length(ranks_sp1), # length of cycle
                              nb_in_cycle_sp2 = length(ranks_sp2), 
                              high_rank_sp1 = min(ranks_sp1), # max fitness rank during cycle
                              high_rank_sp2 = min(ranks_sp2),
                              low_rank_sp1 = max(ranks_sp1), # min fitness rank during cycle
                              low_rank_sp2 = max(ranks_sp2),
                              var_rank_sp1 = var(ranks_sp1), # variation in fitness rank during cycle
                              var_rank_sp2 = var(ranks_sp2),
                              mean_rank_sp1 = mean(ranks_sp1), # mean fitness rank during cycle
                              mean_rank_sp2 = mean(ranks_sp2),
                           landscape_ID = interaction(2, 0, 1, i, j))
      
      cycles_nkc_201 <- rbind(cycles_nkc_201, summary_temp)
      
    }
    
  }
  
}

# repeat for all other combinations...
# for N = 2, K = 1, C = 1
cycles_nkc_211 <- NULL

c_rep <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 1 & 
                     peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "c_rep"]

for (i in unique(c_rep)){ # IM replicates
  
  scape_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 1 & 
                              peaks_total$c_rep == i &
                           peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "scape_rep"]
  
  for (j in unique(scape_reps)) { # fitness landscape replicates
    
    walk_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 1 & 
                              peaks_total$c_rep == i &
                               peaks_total$scape_rep == j &
                           peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "walk_rep"]
    
    for (l in unique(walk_reps)) {
      
      ranks_sp1 <- unique(peaks_nkcs_2111[[5]][[i]][[j]][[2]][[l]][[1]][c(230:250), "rank"])
      ranks_sp2 <- unique(peaks_nkcs_2111[[5]][[i]][[j]][[2]][[l]][[2]][c(230:250), "rank"])
      
      summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              walk_rep = l,
                              nb_in_cycle_sp1 = length(ranks_sp1), 
                              nb_in_cycle_sp2 = length(ranks_sp2), 
                              high_rank_sp1 = min(ranks_sp1),
                              high_rank_sp2 = min(ranks_sp2),
                              low_rank_sp1 = max(ranks_sp1),
                              low_rank_sp2 = max(ranks_sp2),
                              var_rank_sp1 = var(ranks_sp1),
                              var_rank_sp2 = var(ranks_sp2),
                              mean_rank_sp1 = mean(ranks_sp1),
                              mean_rank_sp2 = mean(ranks_sp2),
                           landscape_ID = interaction(2, 1, 1, i, j))
      
      cycles_nkc_211 <- rbind(cycles_nkc_211, summary_temp)
      
    }
    
  }
  
}

# for N = 2, K = 0, C = 2
cycles_nkc_202 <- NULL

c_rep <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 2 & 
                     peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "c_rep"]

for (i in unique(c_rep)){ # IM replicates
  
  scape_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 2 & 
                              peaks_total$c_rep == i &
                           peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "scape_rep"]
  
  for (j in unique(scape_reps)) { # fitness landscape replicates
    
    walk_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 0 & peaks_total$c == 2 & 
                              peaks_total$c_rep == i &
                               peaks_total$scape_rep == j &
                           peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "walk_rep"]
    
    for (l in unique(walk_reps)) {
      
      ranks_sp1 <- unique(peaks_nkcs_2021[[5]][[i]][[j]][[2]][[l]][[1]][c(230:250), "rank"])
      ranks_sp2 <- unique(peaks_nkcs_2021[[5]][[i]][[j]][[2]][[l]][[2]][c(230:250), "rank"])
      
      summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 2,
                              c_rep = i,
                              scape_rep = j,
                              walk_rep = l,
                              nb_in_cycle_sp1 = length(ranks_sp1), 
                              nb_in_cycle_sp2 = length(ranks_sp2), 
                              high_rank_sp1 = min(ranks_sp1),
                              high_rank_sp2 = min(ranks_sp2),
                              low_rank_sp1 = max(ranks_sp1),
                              low_rank_sp2 = max(ranks_sp2),
                              var_rank_sp1 = var(ranks_sp1),
                              var_rank_sp2 = var(ranks_sp2),
                              mean_rank_sp1 = mean(ranks_sp1),
                              mean_rank_sp2 = mean(ranks_sp2),
                           landscape_ID = interaction(2, 0, 2, i, j))
      
      cycles_nkc_202 <- rbind(cycles_nkc_202, summary_temp)
      
    }
    
  }
  
}

# for N = 2, K = 1, C = 2
cycles_nkc_212 <- NULL

c_rep <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 2 & 
                     peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "c_rep"]

for (i in unique(c_rep)){ # IM replicates
  
  scape_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 2 & 
                              peaks_total$c_rep == i &
                           peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "scape_rep"]
  
  for (j in unique(scape_reps)) { # fitness landscape replicates
    
    walk_reps <- peaks_total[peaks_total$n == 2 & peaks_total$k == 1 & peaks_total$c == 2 & 
                              peaks_total$c_rep == i &
                               peaks_total$scape_rep == j &
                           peaks_total$step == 250 & 
                       peaks_total$walking == "random" &
                       peaks_total$species == 1, "walk_rep"]
    
    for (l in unique(walk_reps)) {
      
      ranks_sp1 <- unique(peaks_nkcs_2121[[5]][[i]][[j]][[2]][[l]][[1]][c(230:250), "rank"])
      ranks_sp2 <- unique(peaks_nkcs_2121[[5]][[i]][[j]][[2]][[l]][[2]][c(230:250), "rank"])
      
      summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 2,
                              c_rep = i,
                              scape_rep = j,
                              walk_rep = l,
                              nb_in_cycle_sp1 = length(ranks_sp1), 
                              nb_in_cycle_sp2 = length(ranks_sp2), 
                              high_rank_sp1 = min(ranks_sp1),
                              high_rank_sp2 = min(ranks_sp2),
                              low_rank_sp1 = max(ranks_sp1),
                              low_rank_sp2 = max(ranks_sp2),
                              var_rank_sp1 = var(ranks_sp1),
                              var_rank_sp2 = var(ranks_sp2),
                              mean_rank_sp1 = mean(ranks_sp1),
                              mean_rank_sp2 = mean(ranks_sp2),
                           landscape_ID = interaction(2, 1, 2, i, j))
      
      cycles_nkc_212 <- rbind(cycles_nkc_212, summary_temp)
      
    }
    
  }
  
}

# combine the information of all individual cycles
cycles_df <- rbind(cycles_nkc_201, cycles_nkc_211, cycles_nkc_212, cycles_nkc_202)

# give the cycles IDs so I can group identical cycles together
cycles_df$cycle_ID <- interaction(cycles_df[, c("high_rank_sp1", "high_rank_sp2", "low_rank_sp1", "low_rank_sp2")])

# for if I want to look at unique cycles (it is possible to have multiple cycles on a landscape)
summary_cycles <-  NULL

for (scape_ID in unique(cycles_df$landscape_ID)){
  
  for (cycle_ID in unique(cycles_df[cycles_df$landscape_ID == scape_ID, "cycle_ID"])) {
    
    temp_df <- cycles_df[cycles_df$landscape_ID == scape_ID &
                                              cycles_df$cycle_ID == cycle_ID, ]
    
    summary_temp <- data.frame(n = 2,
                              k = unique(temp_df$k),
                              c = unique(temp_df$c),
                              c_rep = unique(temp_df$c_rep),
                              scape_ID = scape_ID,
                              cycle_ID = cycle_ID,
                              nb_in_cycle_sp1 = mean(temp_df$nb_in_cycle_sp1),
                              nb_in_cycle_sp2 = mean(temp_df$nb_in_cycle_sp2), 
                              high_rank_sp1 = unique(temp_df$high_rank_sp1),
                              high_rank_sp2 = unique(temp_df$high_rank_sp2),
                              low_rank_sp1 = unique(temp_df$low_rank_sp1),
                              low_rank_sp2 = unique(temp_df$low_rank_sp2),
                              var_rank_sp1 = mean(temp_df$var_rank_sp1),
                              var_rank_sp2 = mean(temp_df$var_rank_sp2),
                              mean_rank_sp1 = mean(temp_df$mean_rank_sp1),
                              mean_rank_sp2 = mean(temp_df$mean_rank_sp2),
                              appeared = nrow(temp_df))
    
    summary_cycles <- rbind(summary_cycles, summary_temp)
    
  }
  
}

```

## Fig. 6 - fitness cost/interaction matrices C = 1
```{r}
df_cycles_sp1 <- data.frame(k = summary_cycles$k,
                              c = summary_cycles$c,
                              n = summary_cycles$n,
                              a = rep(2, nrow(summary_cycles)),
                              k_rep = rep(1, nrow(summary_cycles)),
                              c_rep = summary_cycles$c_rep,
                            scape_rep = rep(NA, nrow(summary_cycles)),
                            walking = rep("random", nrow(summary_cycles)),
                            rank = round(summary_cycles$mean_rank_sp1, 0),
                            species = rep(1, nrow(summary_cycles)),
                            rank_peaked = summary_cycles$appeared,
                            cycle_count = rep(NA, nrow(summary_cycles)),
                            tot_reps = rep(80, nrow(summary_cycles)),
                            prop_rank_peaked = summary_cycles$appeared/80,
                            prop_cycle = rep(NA, nrow(summary_cycles)),
                            cycle = rep("yes", nrow(summary_cycles)))

df_cycles_sp2 <- data.frame(k = summary_cycles$k,
                              c = summary_cycles$c,
                              n = summary_cycles$n,
                              a = rep(2, nrow(summary_cycles)),
                              k_rep = rep(1, nrow(summary_cycles)),
                              c_rep = summary_cycles$c_rep,
                            scape_rep = rep(NA, nrow(summary_cycles)),
                            walking = rep("random", nrow(summary_cycles)),
                            rank = round(summary_cycles$mean_rank_sp2, 0),
                            species = rep(2, nrow(summary_cycles)),
                            rank_peaked = summary_cycles$appeared,
                            cycle_count = rep(NA, nrow(summary_cycles)),
                            tot_reps = rep(80, nrow(summary_cycles)),
                            prop_rank_peaked = summary_cycles$appeared/80,
                            prop_cycle = rep(NA, nrow(summary_cycles)),
                            cycle = rep("yes", nrow(summary_cycles)))


peaks_total_ranked_w_cycles <- peaks_total_ranked_summarised[peaks_total_ranked_summarised$rank != 17,]
peaks_total_ranked_w_cycles$cycle <- "no"
peaks_total_ranked_w_cycles <- rbind(peaks_total_ranked_w_cycles, df_cycles_sp1, df_cycles_sp2)

prop_peaks_cycle <- peaks_total_ranked_w_cycles %>%
  group_by(n, k, c, rank, walking, species, c_rep) %>%
  summarise(count = sum(rank_peaked)) %>%
  group_by(n, k, c, walking, c_rep, species) %>%
  mutate(tot = sum(count)) %>%
  mutate(prop = count/tot)

IM_fitness_species <- ggplot(prop_peaks_cycle[prop_peaks_cycle$n == 2 &
                                         prop_peaks_cycle$c == 1 &
                                           prop_peaks_cycle$species == 1 &
                                       prop_peaks_cycle$walking == "random",], # only random walks in main text
        aes(y = prop,
            x = rank,
            group = rank)) +
  geom_rect(data = prop_peaks_cycle[prop_peaks_cycle$n == 2 &
                                                      prop_peaks_cycle$c == 1 &
                                      prop_peaks_cycle$rank == 1 &
                                                   prop_peaks_cycle$species == 1 &
                                                   prop_peaks_cycle$c_rep == 1 &
                                       prop_peaks_cycle$walking == "random",][c(1,2),],
            aes(xmin = 8.5, 
                xmax = Inf, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80",  # putting a grey rectangle over the ranks that do not exist; for IM = 1, there are only eight possible fitness ranks per species
            alpha = 0.5) +
  geom_rect(data = prop_peaks_cycle[prop_peaks_cycle$n == 2 &
                                                      prop_peaks_cycle$c == 1 &
                                      prop_peaks_cycle$rank == 1 &
                                                   prop_peaks_cycle$species == 1 &
                                                   prop_peaks_cycle$c_rep == 4 &
                                       prop_peaks_cycle$walking == "random",][c(1,2),],
            aes(xmin = 8.5, 
                xmax = Inf, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80",  # putting a grey rectangle over the ranks that do not exist; for IM = 1, there are only eight possible fitness ranks per species
            alpha = 0.2) +
  geom_col(aes(group = species,
               fill = as.factor(species),
               x = rank-0.2),
           width = 0.4) + 
  geom_col(data = prop_peaks_cycle[prop_peaks_cycle$n == 2 &
                                     prop_peaks_cycle$c == 1 &
                            prop_peaks_cycle$species == 2 &
                          prop_peaks_cycle$walking == "random",],
           aes(group = species,
               fill = as.factor(species),
               x = rank+0.2),
           width = 0.4) +
     theme_bw() +
  facet_grid(c_rep ~ k) +
  scale_x_continuous(labels = c("0","1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15"), 
                     breaks = c(1:16),
                     limits = c(0.5,16.5),
                   name = "Fitness load (rank difference to global peak)",
                   sec.axis = sec_axis(~ . , name = "intragenomic epistasis, K", breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                     limits = c(0,1)) +
  scale_fill_manual(values=c("palevioletred4","lavenderblush3"),
                    breaks = c("1", "2"),
                    labels = c("Focal species", "Partner species")) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
        legend.text = element_text(size = 13),
        legend.position = c(0.9,0.93),
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_blank(),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 21,
       filename = "effectIM_fit_N2_sp.pdf",
       plot = IM_fitness_species)

```

## fitness load - cycles vs. equilibrium + species vs community
```{r}
peaks_total_ranked_w_cycles$community <- "no"


prop_peaks <- peaks_total_ranked_w_cycles %>%
  group_by(n, k, c, cycle, rank, walking, community) %>%
  summarise(count = sum(rank_peaked)) %>%
  group_by(n, k, c, walking, community) %>%
  mutate(tot = sum(count)) %>%
  mutate(prop = count/tot)

# community
df_cycles_community <- data.frame(k = summary_cycles$k,
                              c = summary_cycles$c,
                              n = summary_cycles$n,
                              a = rep(2, nrow(summary_cycles)),
                              k_rep = rep(1, nrow(summary_cycles)),
                              c_rep = summary_cycles$c_rep,
                            scape_rep = rep(NA, nrow(summary_cycles)),
                            rank_sp1 = round(summary_cycles$mean_rank_sp1, 0),
                            rank_sp2 = round(summary_cycles$mean_rank_sp2, 0),
                            community = rep("yes", nrow(summary_cycles)),
                            rank_peaked = summary_cycles$appeared,
                            landscape_ID = summary_cycles$scape_ID,
                            corr_rank = rep(NA, nrow(summary_cycles)),
                            cycle = rep("yes", nrow(summary_cycles)))

community_ranked_w_cycles <- peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$rank_sp1 != 17, !names(peaks_total_ranked2_summarised) %in% c("species")]
community_ranked_w_cycles$cycle <- "no"
community_ranked_w_cycles$community <- "yes"
community_ranked_w_cycles <- rbind(community_ranked_w_cycles, df_cycles_community)

prop_community_cycle <- community_ranked_w_cycles %>%
  group_by(n, k, c, rank_sp1, rank_sp2, community, cycle) %>%
  summarise(count = sum(rank_peaked)) %>%
  group_by(n, k, c, community) %>%
  mutate(tot = sum(count)) %>%
  mutate(prop = count/tot)

fitness_species <- ggplot(prop_peaks[prop_peaks$n == 2 &
                                       prop_peaks$c != 0 &
                            prop_peaks$cycle == "no" &
                          prop_peaks$walking == "random",],
       aes(x = rank,
           y = prop,
           group = rank)) +
  geom_col(data = prop_community_cycle[prop_community_cycle$n == 2 &
                                         prop_community_cycle$cycle == "no" &
                                         prop_community_cycle$c != 0,],
           aes(x = (rank_sp1 + rank_sp2)/2-0.125,
               group = (rank_sp1 + rank_sp2)/2,
               y = -prop,
               fill = interaction(community, cycle)),
           width = 0.25) +
  geom_col(data = prop_community_cycle[prop_community_cycle$n == 2 &
                                         prop_community_cycle$cycle == "yes",],
           aes(x = (rank_sp1 + rank_sp2)/2+0.125,
               group = (rank_sp1 + rank_sp2)/2,
               y = -prop,
               fill = interaction(community, cycle)),
           width = 0.25) +
  geom_col(aes(group = cycle,
               fill = interaction(community, cycle),
               x = rank-0.125),
           width = 0.25) + 
  geom_col(data = prop_peaks[prop_peaks$n == 2 &
                            prop_peaks$cycle == "yes" &
                          prop_peaks$walking == "random",],
           aes(group = cycle,
               fill = interaction(community, cycle),
               x = rank+0.125),
           width = 0.25) + 
  geom_hline(yintercept=0,
             linewidth = 0.65,
             col = "grey50") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_fill_manual(values=c("forestgreen", "skyblue", "darkseagreen", "steelblue"),
                    breaks = c("no.no", "no.yes", "yes.no", "yes.yes"),
                    labels = c("Equilibrium", "Cycle", "Equilibrium", "Cycle")) +
  scale_x_continuous(labels = c("0","1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15"), 
                     breaks = c(1:16),
                     limits = c(0.5,16.5),
                   name = "Fitness load (rank difference to global peak)",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                     limits = c(-0.3, 0.32),
                     breaks = c(-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3),
                     labels = c("0.3", "0.2", "0.1", "0.0", "0.1", "0.2", "0.3"),
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
        legend.text = element_text(size = 13),
        legend.position = c(0.86,0.87),
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_blank(),
        text = element_text(family = "Arial Unicode MS")) 

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode character
       units = c("cm"),
       width = 26,
       height = 15,
       filename = "fitnessload.pdf",
       plot = fitness_species)

```


## Fig 7 - correlation-fitness relationship
Next, we show how the correlation of fitness ranks between the species can reveal some trends on how lare the expected fitnes cost of a species is
```{r}

# for this I first need to calculate the correlation of fitness ranks for all fitness landscapes with different combinations of C and K; but I'm only interested in cases with C > 0

# N = 2, K = 0, C = 1
## prep dataframes 
combined_scapes_nkc_201 <- list() # here I store the combined landscapes and the correlation of their fitness ranks
summary_cors_nkc_201 <- NULL # and this is to keep track of the summaries (correlation for each landscape)

for (i in 1:4){ # for each interaction matrix
  
  combined_scapes_nkc_201[[i]] <- list() # prep entry in list for storage
  
for (j in 1:50){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2011[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2011[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 0, 1, i, j))

summary_cors_nkc_201 <- rbind(summary_cors_nkc_201, summary_temp) # combine all stats

combined_scapes_nkc_201[[i]][[j]] <- test_df # save combined fitness landscape; why? not sure tbh
  
}
}

### now repeat for all others

# N = 2, K = 0, C = 2
combined_scapes_nkc_202 <- list()
combined_scapes_nkc_202[[1]] <- list()
summary_cors_nkc_202 <- NULL

for (j in 1:200){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2021[[4]][[1]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2021[[4]][[1]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 2,
                              c_rep = 1,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 0, 2, 1, j))

summary_cors_nkc_202 <- rbind(summary_cors_nkc_202, summary_temp)

combined_scapes_nkc_202[[1]][[j]] <- test_df
  
}

###
combined_scapes_nkc_211 <- list()
summary_cors_nkc_211 <- NULL

for (i in 1:4){ # for each interaction matrix
  
  combined_scapes_nkc_211[[i]] <- list()
  
for (j in 1:50){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2111[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2111[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 1, 1, i, j))

summary_cors_nkc_211 <- rbind(summary_cors_nkc_211, summary_temp)

combined_scapes_nkc_211[[i]][[j]] <- test_df
  
}
}

###
combined_scapes_nkc_212 <- list()
combined_scapes_nkc_212[[1]] <- list()
summary_cors_nkc_212 <- NULL

for (j in 1:200){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2121[[4]][[1]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2121[[4]][[1]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 2,
                              c_rep = 1,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 1, 2, 1, j))

summary_cors_nkc_212 <- rbind(summary_cors_nkc_212, summary_temp)

combined_scapes_nkc_212[[1]][[j]] <- test_df
  
}


#############

# now I combine all the stats across all landscapes into one big data frame
summary_cors <- rbind(summary_cors_nkc_201, summary_cors_nkc_202, summary_cors_nkc_211, summary_cors_nkc_212)

# and I want to link the correlations I just calculated to my results; so I add it so my dataframe, where the adaptive outcomes of both species are combined 

# I'm sure this could be done with an apply function, but alas I am using a for loop
for (i in 1:nrow(peaks_total_ranked2_summarised)){
  
  ID <- peaks_total_ranked2_summarised[i, "landscape_ID" ]
  
  if (ID %in% summary_cors$landscape_ID){
    
    peaks_total_ranked2_summarised[i, "corr_rank" ] <- unique(summary_cors[as.character(summary_cors$landscape_ID) == as.character(ID), "corr"])
    
  }

}


for (i in 1:nrow(community_ranked_w_cycles)){
  
  ID <- community_ranked_w_cycles[i, "landscape_ID" ]
  
  if (ID %in% summary_cors$landscape_ID){
    
    community_ranked_w_cycles[i, "corr_rank" ] <- unique(summary_cors[as.character(summary_cors$landscape_ID) == as.character(ID), "corr"])
    
  }

}

# now, let's plot; since this type of figure is difficult to interpret we only show one of them in the main text and the rest can be found in the supplementary material

# we combine three plots; (i) the results for N = 2, K = 0, C = 1, (ii) an empty plot; here I add our expectations and the categorisation of win/win, Lose/lose, win/lose and cycling in post using Adobe illustrator, and (iii) a distance plot to show the second important feater we observe - how the difference in fitness ranks depends on the fitness rank correlation

# first plot
eco_outcome <- ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank) &
                                                       peaks_total_ranked2_summarised$k == 0 &
                                                       peaks_total_ranked2_summarised$c == 1 &
                                                       peaks_total_ranked2_summarised$rank_sp1 != 17,],
       aes(x = corr_rank,
           y = rank_sp1)) +
  geom_hline(yintercept = 1,
             col = "grey") +
   geom_segment(aes(x = corr_rank, 
      y = rank_sp1, 
      xend = corr_rank, 
      yend = rank_sp2,
      alpha = rank_peaked/80),
      col = "grey40") +
  geom_segment(data = summary_cycles[summary_cycles$k == 0 & 
                                   summary_cycles$c == 1,],
               aes(x = corr_rank, 
      y = mean_rank_sp1, 
      xend = corr_rank, 
      yend = mean_rank_sp2,
      alpha = appeared/80),
      col = "grey40") +
  geom_point(size = 2.5,
             aes(alpha = rank_peaked/80,
                 col = "Equilibrium")) +
  geom_point(aes(x = corr_rank,
                 y = rank_sp2,
                 alpha = rank_peaked/80,
                 col = "Equilibrium"),
             size = 2.5) +
  geom_point(data = summary_cycles[summary_cycles$k == 0 & 
                                   summary_cycles$c == 1,],
             aes(x = corr_rank,
                 y = mean_rank_sp1,
                 alpha = appeared/80,
                 col = "Cycle"),
             size = 2.5) +
  geom_point(data = summary_cycles[summary_cycles$k == 0 & 
                                   summary_cycles$c == 1,],
             aes(x = corr_rank,
                 y = mean_rank_sp2,
                 alpha = appeared/80,
                 col = "Cycle"),
             size = 2.5) +
  scale_colour_manual(values=c("forestgreen", "skyblue"),
                      breaks = c("Equilibrium", "Cycle"),
                      name = "") +
  guides(alpha = "none") +
  scale_y_continuous(labels = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15"), 
                     breaks = c(1:16),
                     limits = c(1,16),
                   name = "Species fitness load") +
  scale_x_continuous(name = "rank correlation(F, P)",
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = c(0.08,0.95),
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        legend.text = element_text(size=15),
        legend.background = element_rect(fill = "transparent"))


# second plot
blank <- ggplot(community_ranked_w_cycles[community_ranked_w_cycles$k == 0 &
                                                       community_ranked_w_cycles$c == 1,],
       aes(x = corr_rank,
           y = rank_sp1)) +
  scale_y_continuous(labels = c("0", "3", "6", "9", "12", "15"), 
                     breaks = seq(1, 16, 3),
                     limits = c(1,16),
                   name = "") +
  scale_x_continuous(name = "  ",
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        axis.title.y = element_text(size=17),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.background = element_blank()) 

# combine 1 and 2
panel_a <- eco_outcome + 
  annotation_custom(ggplotGrob(blank),
                                xmin = 0.4,
                                xmax = 1,
                                ymin = 10,
                                ymax = 16.5)


# third plot
library(car)

model_diff <- glmmTMB::glmmTMB(abs(rank_sp1-rank_sp2) ~ corr_rank + (1 | landscape_ID) ,
               data = community_ranked_w_cycles[community_ranked_w_cycles$k == 0 &
                                                       community_ranked_w_cycles$c == 1,],
               family = poisson,
               weights = rank_peaked)


model_diff3 <- glmmTMB::glmmTMB(abs(rank_sp1-rank_sp2) ~ corr_rank + c + k + cycle,
               data = community_ranked_w_cycles[community_ranked_w_cycles$c != 0,],
               family = poisson,
               weights = rank_peaked)


car::Anova(model_diff3)
#anova(model_diff, model_diff2, model_diff3, model_diff4, model_diff_all, test = "Chisq")

#effects_k0 <- effects::effect(term= "corr_rank", 
#                              mod= model_diff_all,
#                              xlevels = 50)
#effects_k0_df <- as.data.frame(effects_k0)

#create a new dataframe: names should match those of the originary dataframe
#new_community_df = expand.grid(corr_rank = seq(-1,1,0.05),
#                     c = c(1,2),
#                     k = c(0,1),
#                     cycle = c("yes", "no"))

community_ranked_w_cycles_tst <- community_ranked_w_cycles[community_ranked_w_cycles$c != 0,]
 
#add preditions
community_ranked_w_cycles_tst$predict = predict(model_diff3, 
                                                type = "response", 
                                                newdata = community_ranked_w_cycles_tst)


distance_plot <- ggplot(community_ranked_w_cycles_tst[community_ranked_w_cycles_tst$k == 0 &
                                                       community_ranked_w_cycles_tst$c == 1,],
       aes(x = corr_rank,
           y = abs(rank_sp1-rank_sp2))) +
  geom_hline(yintercept = 0,
             col = "grey") +
  geom_point(aes(alpha = rank_peaked/80,
                 col = cycle),
             size = 2.5) +
  geom_line(aes(x = corr_rank, 
                y = predict,
                col = interaction(cycle, n)),
            linewidth = 1.5) +
  scale_colour_manual(values=c("forestgreen", "skyblue", "darkgreen","turquoise3"),
                    breaks = c("no", "yes", "no.2", "yes.2")) +
  scale_y_continuous(labels = c("0", "2", "4", "6", "8", "10", "12", "14"),
                     breaks = seq(0,14,2),
                     limits = c(0,15),
                   name = "Difference in fitness rank") +
  scale_x_continuous(name = "rank correlation(F, P)",
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        axis.title.y = element_text(size=17),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5)) 

# fourth plot
model_mean <- glmmTMB::glmmTMB((rank_sp1+rank_sp2)/2 ~ corr_rank + (1 | landscape_ID) ,
               data = community_ranked_w_cycles[community_ranked_w_cycles$k == 0 &
                                                       community_ranked_w_cycles$c == 1,],
               family = poisson,
               weights = rank_peaked)

model_mean3 <- glmmTMB::glmmTMB((rank_sp1+rank_sp2)/2 ~ corr_rank + c + k + cycle,
               data = community_ranked_w_cycles[community_ranked_w_cycles$c != 0,],
               family = poisson,
               weights = rank_peaked)

community_ranked_w_cycles_tst$predict_mean = predict(model_mean3, 
                                                type = "response", 
                                                newdata = community_ranked_w_cycles_tst)


#effects_k0_mean <- effects::effect(term= "corr_rank", 
#                              mod= model_mean,
#                              xlevels = 50)
#effects_k0_mean_df <- as.data.frame(effects_k0_mean)

mean_plot <- ggplot(community_ranked_w_cycles_tst[community_ranked_w_cycles_tst$k == 0 &
                                                       community_ranked_w_cycles_tst$c == 1,],
       aes(x = corr_rank,
           y = (rank_sp1+rank_sp2)/2)) +
  geom_hline(yintercept = 1,
             col = "grey") +
  geom_point(aes(alpha = rank_peaked/80,
                 col = cycle),
             size = 2.5) +
  geom_line(aes(x = corr_rank, 
                y = predict_mean,
                col = interaction(cycle, n)),
            linewidth = 1.5) +
  scale_colour_manual(values=c("forestgreen", "skyblue", "darkgreen","turquoise3"),
                    breaks = c("no", "yes", "no.2", "yes.2")) +
  scale_y_continuous(labels = c("0", "2", "4", "6", "8", "10", "12", "14"),
                     breaks = seq(1,15,2),
                     limits = c(1,16),
                   name = "Community fitness load") +
  scale_x_continuous(name = "rank correlation(F, P)",
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        axis.title.y = element_text(size=17),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5)) 

# combined plots
fig_test <- ggpubr::ggarrange(panel_a, NULL, # to have some extra space :-)
                  ggpubr::ggarrange(distance_plot, mean_plot, ncol = 2),
                  nrow = 3,
                     heights = c(1.7, 0.1, 1))

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 25,
       filename = "eco_fig.pdf",
       plot = fig_test)

```


# 3.) Supplementary figures
## fitness distribution -random
Here we show which fitness outcomes are the most common, which gives us the expected fitness distribution for each combination of K and C; this figure also shows the cycling probability
```{r}
peaks_total_ranked_fixed <- peaks_total_ranked_summarised
peaks_total_ranked_fixed[is.na(peaks_total_ranked_fixed$rank_peaked), "rank_peaked"] <- peaks_total_ranked_fixed[is.na(peaks_total_ranked_fixed$rank_peaked), "cycle_count"]

prop_peaks <- peaks_total_ranked_fixed %>%
  group_by(n, k, c, rank, walking) %>%
  summarise(count = sum(rank_peaked)) %>%
  group_by(n, k, c, walking) %>%
  mutate(tot = sum(count)) %>%
  mutate(prop = count/tot)

fitness_dis_N2 <- ggplot(prop_peaks[prop_peaks$n == 2 &
                                       prop_peaks$walking == "random" &
                                      prop_peaks$rank != 17,], # only random walks 
        aes(y = prop,
            x = rank,
            group = rank)) +
  geom_rect(data = prop_peaks[prop_peaks$n == 2 &
                                                      prop_peaks$c == 0 &
                                                   prop_peaks$rank == 1 &
                                       prop_peaks$walking == "random",], # this was the only way I was able to plot a single rectangle per facet :-(
            aes(xmin = 4.5, 
                xmax = 16.5, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80", # putting a grey rectangle over the ranks that do not exist; for C = 0, there are only four possible fitness ranks per species
            alpha = 0.5,
            inherit.aes = FALSE) +
  geom_col(fill = "forestgreen") +
  geom_col(data = prop_peaks[prop_peaks$n == 2 &
                                       prop_peaks$walking == "random" &
                                      prop_peaks$rank == 17,],
           fill = "skyblue") + 
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26, # 30
       height = 17, # 15
       filename = "fitness_dis_N2.pdf",
       plot = fitness_dis_N2)

```

## N = 4 fitness distribution
```{r}
fitness_dis_N4 <- ggplot(prop_peaks[prop_peaks$n == 4 &
                                       prop_peaks$walking == "random",], # only random walks in main text
        aes(y = prop,
            x = rank,
            group = rank)) +
  geom_col(fill = "forestgreen") +
     theme_bw() +
  facet_grid( ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   limits = c(0.5,17.5),
                   sec.axis = sec_axis(~ . , name = "K'", breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                     limits = c(0,1)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 45,
       height = 15,
       filename = "fitness_dis_N4.pdf",
       plot = fitness_dis_N4)
```

## Ruggedness - roughness to slope 
```{r}
## calculate roughness to slope ratio
# fit a linear regression to gentoype - fitness 

r <- NULL
s <- NULL

# fully additive 
for (i in 1:200) { # for each landscape replicate
  
  temp_landscape <- peaks_nkcs_2001[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_200_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:200,
                            r = r,
                            s = s,
                            rugg = r/s)

# intragenomic epistasis
r <- NULL
s <- NULL

for (i in 1:200) {
  
  temp_landscape <- peaks_nkcs_2101[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_210_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:200,
                            r = r,
                            s = s,
                            rugg = r/s)

# intergenomic epistasis
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2011[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_201_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 2
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2011[[4]][[2]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_201_2_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(2, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 3
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2011[[4]][[3]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_201_3_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(3, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 4
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2011[[4]][[4]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_201_4_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(4, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# C = 2
r <- NULL
s <- NULL

for (i in 1:200) {
  
  temp_landscape <- peaks_nkcs_2021[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_202_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(0, length(r)),
                            c = rep(2, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:200,
                            r = r,
                            s = s,
                            rugg = r/s)


# inter + intragenomic epistasis
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2111[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_211_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 2
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2111[[4]][[2]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_211_2_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(2, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 3
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2111[[4]][[3]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_211_3_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(3, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# interaction matrix 4
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_2111[[4]][[4]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_211_4_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(1, length(r)),
                            IM_rep = rep(4, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# fully epistatic
r <- NULL
s <- NULL

for (i in 1:200) {
  
  temp_landscape <- peaks_nkcs_2121[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$P.1 + temp_landscape$P.2)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_212_1_1 <- data.frame(n = rep(2, length(r)),
                            k = rep(1, length(r)),
                            c = rep(2, length(r)),
                            IM_rep = rep(1, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:200,
                            r = r,
                            s = s,
                            rugg = r/s)

# N = 4, K = 1
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_4101[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$F.3 + temp_landscape$F.4)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_410_1_1 <- data.frame(n = rep(4, length(r)),
                            k = rep(1, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(5, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)


# N = 4, K = 2
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_4201[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$F.3 + temp_landscape$F.4)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_420_1_1 <- data.frame(n = rep(4, length(r)),
                            k = rep(2, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(5, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

# N = 4, K = 3
# interaction matrix 1
r <- NULL
s <- NULL

for (i in 1:50) {
  
  temp_landscape <- peaks_nkcs_4301[[4]][[1]][[i]][[1]]
  linear_model <- lm(temp_landscape$fitness ~ temp_landscape$F.1 + temp_landscape$F.2 + temp_landscape$F.3 + temp_landscape$F.4)
  
  r <- c(r, var(linear_model$residuals))
  s <- c(s, mean(linear_model$coefficients[-1]))

}

ruggedness_nkc_rep_sp_430_1_1 <- data.frame(n = rep(4, length(r)),
                            k = rep(3, length(r)),
                            c = rep(0, length(r)),
                            IM_rep = rep(5, length(r)),
                            sp = rep(1, length(r)),
                            scape_rep = 1:50,
                            r = r,
                            s = s,
                            rugg = r/s)

ruggedness_df <- rbind(ruggedness_nkc_rep_sp_200_1_1[1:50,], ruggedness_nkc_rep_sp_201_1_1, ruggedness_nkc_rep_sp_202_1_1[1:50,], ruggedness_nkc_rep_sp_210_1_1[1:50,], ruggedness_nkc_rep_sp_211_1_1, ruggedness_nkc_rep_sp_212_1_1[1:50,], ruggedness_nkc_rep_sp_410_1_1, ruggedness_nkc_rep_sp_420_1_1, ruggedness_nkc_rep_sp_430_1_1)

ruggedness_df$rugg <- abs(ruggedness_df$rugg)
ruggedness_df$rugg <- round(ruggedness_df$rugg, 4)

ruggedness <- ggplot(ruggedness_df,
       aes(x = interaction(k, c, n),
           y = rugg,
           group = interaction(k, c, n))) +
  geom_violin(col = "grey45") +
  geom_jitter(col = "forestgreen",
              alpha = 0.4,
              width = 0.2,
              size = 4) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 4,
               col = "black") +
  scale_y_log10() + 
  scale_x_discrete(labels=c("0.0.2" = "2-0-0", 
                            "1.0.2" = "2-1-0",
                            "0.1.2" = "2-0-1",
                            "1.1.2" = "2-1-1",
                            "0.2.2" = "2-0-2",
                            "1.2.2" = "2-1-2",
                            "1.0.4" = "4-1-0",
                            "2.0.4" = "4-2-0",
                            "3.0.4" = "4-3-0")) +
  xlab("N-K-C") +
  ylab(substitute(paste(log[10], "(roughness/slope)")))+
  theme_bw() +
  fig_theme +
  theme(panel.grid.major.x = element_blank())

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 10,
       filename = "ruggedness.pdf",
       plot = ruggedness)

```

## ruggedness C = 1
```{r}

ruggedness_df_c1 <- rbind(ruggedness_nkc_rep_sp_201_1_1, ruggedness_nkc_rep_sp_201_2_1, ruggedness_nkc_rep_sp_201_3_1,
                          ruggedness_nkc_rep_sp_201_4_1, ruggedness_nkc_rep_sp_211_1_1, ruggedness_nkc_rep_sp_211_2_1,
                          ruggedness_nkc_rep_sp_211_3_1, ruggedness_nkc_rep_sp_211_4_1)

ruggedness_df_c1$rugg <- abs(ruggedness_df_c1$rugg)

ruggedness_c1 <- ggplot(ruggedness_df_c1,
       aes(x = interaction(IM_rep, k, c, n),
           y = rugg,
           group = interaction(IM_rep, k, c, n))) +
  geom_violin(col = "grey45") +
  geom_jitter(aes(col = as.factor(IM_rep)),
              alpha = 0.4,
              width = 0.2,
              size = 4) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 4,
               col = "black") +
  scale_color_manual(values=c("forestgreen", "limegreen", "olivedrab2", "gold")) +
  scale_y_log10() + 
  scale_x_discrete(labels=c("2-0-1", "2-1-1"),
                   breaks = c("2.0.1.2", "2.1.1.2")) +
  xlab("N-K-C") +
  ylab(substitute(paste(log[10], "(roughness/slope)")))+
  theme_bw() +
  fig_theme +
  theme(panel.grid.major.x = element_blank())

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 20,
       height = 10,
       filename = "ruggedness_c1.pdf",
       plot = ruggedness_c1)

```

## Assessing the number of outcomes
```{r}
# how many outcomes are there on the same landscape?
true_only_summed2 <- as.data.frame(peaks_total_ranked2_summarised |> 
                            dplyr::group_by(k, c, n, c_rep, k_rep, landscape_ID, ) |>
                            dplyr::summarise(outcomes = n())) 

# K = 1, C = 0
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 1 & 
                            true_only_summed2$c == 0 &
                            true_only_summed2$outcomes > 1,]) # tot = 200

# K = 1, C = 1
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 1 & 
                            true_only_summed2$c == 1 &
                            true_only_summed2$outcomes > 1,]) # tot = 200

# K = 0, C = 1
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 0 & 
                            true_only_summed2$c == 1 &
                            true_only_summed2$outcomes > 1,]) # tot = 200

# K = 0, C = 2
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 0 & 
                            true_only_summed2$c == 2 &
                            true_only_summed2$outcomes > 1,]) # tot = 200


# K = 1, C = 2
mult_peak2 <- nrow(true_only_summed2[true_only_summed2$k == 1 & 
                            true_only_summed2$c == 2 &
                            true_only_summed2$outcomes > 1,]) # tot = 200

### N' = 4
peaks_total_ranked2_N4 <- as.data.frame(peaks_total[peaks_total$n == 4 &
                                                              peaks_total$walking == "random",] |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, walk_rep, rank, species) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_ranked2_N4_comb <- peaks_total_ranked2_N4[peaks_total_ranked2_N4$species == 1,]

colnames(peaks_total_ranked2_N4_comb)[9] <- "rank_sp1"
#peaks_total_ranked2_N4_comb$rank_sp2 <- peaks_total_ranked2_N4[peaks_total_ranked2_N4$species == 2, "rank"]

peaks_total_ranked2_sN4_ummarised <- as.data.frame(peaks_total_ranked2_N4_comb |> 
                            dplyr::group_by(k, c, n, a, k_rep, c_rep, scape_rep, rank_sp1, species) |>
                            dplyr::summarise(rank_peaked = n())) 

peaks_total_ranked2_sN4_ummarised$landscape_ID <- interaction(peaks_total_ranked2_sN4_ummarised$n, peaks_total_ranked2_sN4_ummarised$k, peaks_total_ranked2_sN4_ummarised$c, peaks_total_ranked2_sN4_ummarised$k_rep, peaks_total_ranked2_sN4_ummarised$scape_rep)

# how many outcomes are there on the same landscape?
true_only_summedN4 <- as.data.frame(peaks_total_ranked2_sN4_ummarised |> 
                            dplyr::group_by(k, c, n, c_rep, k_rep, landscape_ID, ) |>
                            dplyr::summarise(outcomes = n())) 

# K' = 1, C = 0
mult_peak4 <- nrow(true_only_summedN4[true_only_summedN4$k == 1 & 
                            true_only_summedN4$c == 0 &
                            true_only_summedN4$outcomes > 1,]) # tot = 250


no_outcomes_df <- rbind(true_only_summed2, true_only_summedN4)

no_outcomes <- ggplot(no_outcomes_df,
       aes(y = outcomes,
           x = interaction(k,c,n),
           group = interaction(k,c,n))) +
  geom_violin() +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  scale_y_continuous(name = "Outcomes/landscape",
                     limits = c(0,8),
                     breaks = c(1:8)) +
   scale_x_discrete(labels=c("0.0.2" = "2-0-0", 
                            "1.0.2" = "2-1-0",
                            "0.1.2" = "2-0-1",
                            "1.1.2" = "2-1-1",
                            "0.2.2" = "2-0-2",
                            "1.2.2" = "2-1-2",
                            "1.0.4" = "4-1-0",
                            "2.0.4" = "4-2-0",
                            "3.0.4" = "4-3-0")) +
  xlab("N-K-C") +
  theme_bw() +
  fig_theme

ggsave(path = "../Figures/",
       units = c("cm"),
       width = 19,
       height = 12,
       filename = "no_outcomes.pdf",
       plot = no_outcomes)

no_outcomes_IM <- ggplot(true_only_summed2[true_only_summed2$c == 1,],
       aes(y = outcomes,
           x = c_rep,
           group = c_rep)) +
  geom_violin(aes(col = as.factor(c_rep))) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  scale_y_continuous(name = "No. of realised outcomes",
                      limits = c(0,5)) +
  facet_grid(~k) +
  xlab("N-K-C") +
  theme_bw() +
  fig_theme

## same but with R = 2
# how many outcomes are there on the same landscape?
prop_only_summed2_R <- as.data.frame(peaks_total_ranked2_summarised_R |> 
                            dplyr::group_by(k, c, n, landscape_ID, ) |>
                            dplyr::summarise(outcomes = n())) 

# K = 1, C = 1
mult_peak2 <- nrow(prop_only_summed2_R[prop_only_summed2_R$k == 1 & 
                            prop_only_summed2_R$c == 1 &
                            prop_only_summed2_R$outcomes > 1,]) # tot = 200

# K = 0, C = 1
mult_peak2 <- nrow(prop_only_summed2_R[prop_only_summed2_R$k == 0 & 
                            prop_only_summed2_R$c == 1 &
                            prop_only_summed2_R$outcomes > 1,]) # tot = 200

```

## effect IM N' = 4
```{r}

effectIM_N4 <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 4 &
                                         peaks_total_ranked_summarised$k != 3 &
                                       peaks_total_ranked_summarised$walking == "random",], # only random walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_jitter(aes(col = as.factor(k_rep)),
              size = 2.5,
              height = 0.01,
              alpha = 0.5) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(k_rep ~ k,
             labeller = labeller(k_rep = 
    c("1" = "Random",
      "2" = "Modular",
      "3" = "Nearest neighbour",
      "4" = "Preferential",
      "5" = "Hierarchical"))) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :-)
                     breaks = c(1:17),
                     limits = c(1,17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic("K'"))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                     limits = c(0,1)) +
  scale_color_manual(values=c("forestgreen", "limegreen", "darkseagreen","olivedrab2", "gold")) + # different colours for the four interaction networks
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 0, vjust = 0.5),
        axis.title.y.left = ggtext::element_markdown(),
        axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 12, angle = 90),
        legend.position = "none",
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 21,
       filename = "effectIM_N4.pdf",
       plot = effectIM_N4)

```

## Greedy Repeatability N = 2
```{r}
localrep_N2_greedy <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "greedy",], # only random walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_violin(aes(y = prop_cycle,
                  x = rank),
              col = "grey45") +
  geom_rect(data = peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                                      peaks_total_ranked_summarised$c == 0 &
                                                  peaks_total_ranked_summarised$scape_rep == 1 &
                                                   peaks_total_ranked_summarised$rank == 1 &
                                                   peaks_total_ranked_summarised$species == 1 &
                                       peaks_total_ranked_summarised$walking == "greedy",], # this was the only way I was able to plot a single rectangle per facet :-(
            aes(xmin = 4.5, 
                xmax = 16.5, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80", # putting a grey rectangle over the ranks that do not exist; for C = 0, there are only four possible fitness ranks per species
            alpha = 0.5,
            inherit.aes = FALSE) +
  geom_jitter(col = "forestgreen",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  geom_jitter(aes(y = prop_cycle,
                  x = rank),
               col = "skyblue",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the mean proportion of cycling/landscape
                  x = rank),
               fun = mean,
               geom = "crossbar",
               linewidth = 0.4,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the median proportion of cycling/landscape
                  x = rank),
               fun = median,
               geom = "point",
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 17,
       filename = "localrep_N2_greedy.pdf",
       plot = localrep_N2_greedy)

```

## True Repeatability N = 2
```{r}
localrep_N2_true <- ggplot(peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                       peaks_total_ranked_summarised$walking == "prop",], # only random walks in main text
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_violin(aes(y = prop_cycle,
                  x = rank),
              col = "grey45") +
  geom_rect(data = peaks_total_ranked_summarised[peaks_total_ranked_summarised$n == 2 &
                                                      peaks_total_ranked_summarised$c == 0 &
                                                  peaks_total_ranked_summarised$scape_rep == 1 &
                                                   peaks_total_ranked_summarised$rank == 1 &
                                                   peaks_total_ranked_summarised$species == 1 &
                                       peaks_total_ranked_summarised$walking == "prop",], # this was the only way I was able to plot a single rectangle per facet :-(
            aes(xmin = 4.5, 
                xmax = 16.5, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80", # putting a grey rectangle over the ranks that do not exist; for C = 0, there are only four possible fitness ranks per species
            alpha = 0.5,
            inherit.aes = FALSE) +
  geom_jitter(col = "forestgreen",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  geom_jitter(aes(y = prop_cycle,
                  x = rank),
               col = "skyblue",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the mean proportion of cycling/landscape
                  x = rank),
               fun = mean,
               geom = "crossbar",
               linewidth = 0.4,
               col = "black") +
  stat_summary(aes(y = prop_cycle, # adds the median proportion of cycling/landscape
                  x = rank),
               fun = median,
               geom = "point",
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 17,
       filename = "localrep_N2_true.pdf",
       plot = localrep_N2_true)

```

## fitness distribution - greedy
```{r}
fitness_dis_N2_greedy <- ggplot(prop_peaks[prop_peaks$n == 2 &
                                       prop_peaks$walking == "greedy" &
                                      prop_peaks$rank != 17,], 
        aes(y = prop,
            x = rank,
            group = rank)) +
  geom_rect(data = prop_peaks[prop_peaks$n == 2 &
                                                      prop_peaks$c == 0 &
                                                   prop_peaks$rank == 1 &
                                       prop_peaks$walking == "greedy",], # this was the only way I was able to plot a single rectangle per facet :-(
            aes(xmin = 4.5, 
                xmax = 16.5, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80", # putting a grey rectangle over the ranks that do not exist; for C = 0, there are only four possible fitness ranks per species
            alpha = 0.5,
            inherit.aes = FALSE) +
  geom_col(fill = "forestgreen") +
  geom_col(data = prop_peaks[prop_peaks$n == 2 &
                                       prop_peaks$walking == "random" &
                                      prop_peaks$rank == 17,],
           fill = "skyblue") + 
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26, # 30
       height = 17, # 15
       filename = "fitness_dis_N2_greedy.pdf",
       plot = fitness_dis_N2_greedy)

```

## fitness distribution - true
```{r}
fitness_dis_N2_true <- ggplot(prop_peaks[prop_peaks$n == 2 &
                                       prop_peaks$walking == "prop" &
                                      prop_peaks$rank != 17,], 
        aes(y = prop,
            x = rank,
            group = rank)) +
  geom_rect(data = prop_peaks[prop_peaks$n == 2 &
                                                      prop_peaks$c == 0 &
                                                   prop_peaks$rank == 1 &
                                       prop_peaks$walking == "prop",], # this was the only way I was able to plot a single rectangle per facet :-(
            aes(xmin = 4.5, 
                xmax = 16.5, 
                ymin = 0, 
                ymax = 1), 
            fill = "grey80", # putting a grey rectangle over the ranks that do not exist; for C = 0, there are only four possible fitness ranks per species
            alpha = 0.5,
            inherit.aes = FALSE) +
  geom_col(fill = "forestgreen") +
  geom_col(data = prop_peaks[prop_peaks$n == 2 &
                                       prop_peaks$walking == "random" &
                                      prop_peaks$rank == 17,],
           fill = "skyblue") + 
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26, # 30
       height = 17, # 15
       filename = "fitness_dis_N2_true.pdf",
       plot = fitness_dis_N2_true)

```

## R = 2
```{r}
localrep_N2_R <- ggplot(peaks_total_ranked_summarised_R[peaks_total_ranked_summarised_R$n == 2 &
                                       peaks_total_ranked_summarised_R$walking == "random",], # only random walks 
        aes(y = prop_rank_peaked,
            x = rank,
            group = rank)) +
  geom_violin(col = "grey45") +
  geom_jitter(col = "forestgreen",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :)
                     breaks = c(1:17),
                     limits = c(0.5,17.5),
                   name = "Fitness rank focal species",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 15,
       filename = "localrep_N2_R.pdf",
       plot = localrep_N2_R)
```

## R = 2 - fitness distribution
```{r}
prop_peaksR <- peaks_total_ranked_summarised_R %>%
  group_by(n, k, c, rank, walking) %>%
  summarise(count = sum(rank_peaked)) %>%
  group_by(n, k, c, walking) %>%
  mutate(tot = sum(count)) %>%
  mutate(prop = count/tot)

fitness_dis_N2_R <- ggplot(prop_peaksR[prop_peaksR$walking == "random",], # only random walks 
        aes(y = prop,
            x = rank,
            group = rank)) +
  geom_col(fill = "forestgreen") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                     limits = c(1,17),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of overall outcomes",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL),
                   limits = c(0,1)) +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26, # 30
       height = 17, # 15
       filename = "fitness_dis_N2_R.pdf",
       plot = fitness_dis_N2_R)

```

## correlation - fitness outcomes -> full figure
```{r}
eco_outcomes <- ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank) &
                                                        peaks_total_ranked2_summarised$rank_sp1 != 17,],
   aes(x = corr_rank,
           y = rank_sp1)) +
  geom_hline(yintercept = 1,
             col = "grey") +
   geom_segment(aes(x = corr_rank, 
      y = rank_sp1, 
      xend = corr_rank, 
      yend = rank_sp2,
      alpha = rank_peaked/80),
      col = "grey40") +
  geom_segment(data = summary_cycles,
               aes(x = corr_rank, 
      y = mean_rank_sp1, 
      xend = corr_rank, 
      yend = mean_rank_sp2,
      alpha = appeared/80),
      col = "grey40") +
  geom_point(col = "forestgreen",
             size = 2.5,
             aes(alpha = rank_peaked/80)) +
  geom_point(aes(x = corr_rank,
                 y = rank_sp2,
                 alpha = rank_peaked/80),
                 col = "forestgreen",
             size = 2.5) +
  geom_point(data = summary_cycles,
             aes(x = corr_rank,
                 y = mean_rank_sp1,
                 alpha = appeared/80),
             col = "skyblue",
             size = 2.5) +
  geom_point(data = summary_cycles,
             aes(x = corr_rank,
                 y = mean_rank_sp2,
                 alpha = appeared/80),
             col = "skyblue",
             size = 2.5) +
  facet_grid(c ~ k) +
  scale_y_continuous(labels = c("0", "2", "4", "6", "8", "10", "12", "14"), 
                     breaks = seq(1, 15, 2),
                   name = "Species fitness load",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL),
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "eco_outcomes.pdf",
       plot = eco_outcomes)

```

## correlation - difference in fitness
```{r}

eco_dis <- ggplot(community_ranked_w_cycles_tst[community_ranked_w_cycles_tst$c != 0,],
       aes(x = corr_rank,
           y = abs(rank_sp1-rank_sp2))) +
  geom_hline(yintercept = 0,
             col = "grey") +
  geom_point(aes(alpha = rank_peaked/80,
                 col = cycle),
             size = 2.5) +
  geom_line(aes(x = corr_rank, 
                y = predict,
                group = cycle,
                col = interaction(cycle, n)), # doing this so I can give the lines other colours
            linewidth = 1) +
  facet_grid(c~k) +
  scale_colour_manual(values=c("forestgreen", "skyblue", "darkgreen", "turquoise3"),
                    breaks = c("no", "yes", "no.2", "yes.2")) +
  scale_y_continuous(labels = c("0", "2", "4", "6", "8", "10", "12", "14"),
                     breaks = seq(0,14,2),
                     limits = c(0,15),
                   name = "Difference in fitness rank",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   limits = c(-1,1),
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        axis.title.y = element_text(size=17),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) 

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "eco_dis.pdf",
       plot = eco_dis)
```

## correlation - community fitness
```{r}
community_load <- ggplot(community_ranked_w_cycles_tst[community_ranked_w_cycles_tst$c != 0,],
       aes(x = corr_rank,
           y = (rank_sp1+rank_sp2)/2)) +
  geom_hline(yintercept = 1,
             col = "grey") +
  geom_point(aes(alpha = rank_peaked/80,
                 col = cycle),
             size = 2.5) +
  geom_line(aes(x = corr_rank, 
                y = predict_mean,
                group = cycle,
                col = interaction(cycle, n)), # doing this so I can give the lines other colours
            linewidth = 1) +
  facet_grid(c~k) +
  scale_colour_manual(values=c("forestgreen", "skyblue", "darkgreen", "turquoise3"),
                    breaks = c("no", "yes", "no.2", "yes.2")) +
  scale_y_continuous(labels = c("0", "2", "4", "6", "8", "10", "12", "14"),
                     breaks = seq(1,15,2),
                     limits = c(1,15),
                   name = "Community fitness load",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   limits = c(-1,1),
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
        axis.title.y = element_text(size=17),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) 

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "community_load.pdf",
       plot = community_load)
```

## R = 2 -  correlation - fitness outcomes 
```{r}
## same but for R = 2
combined_scapes_nkc_201_R <- list()
summary_cors_nkc_201_R <- NULL

for (i in 1:4){ # for each interaction matrix
  
  combined_scapes_nkc_201_R[[i]] <- list()
  
for (j in 1:50){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2011_R[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2011_R[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 0, 1, i, j))

summary_cors_nkc_201_R <- rbind(summary_cors_nkc_201_R, summary_temp)

combined_scapes_nkc_201_R[[i]][[j]] <- test_df
  
}
}

###
combined_scapes_nkc_211_R <- list()
summary_cors_nkc_211_R <- NULL

for (i in 1:4){ # for each interaction matrix
  
  combined_scapes_nkc_211_R[[i]] <- list()
  
for (j in 1:50){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2111_R[[4]][[i]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2111_R[[4]][[i]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 1,
                              c_rep = i,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 1, 1, i, j))

summary_cors_nkc_211_R <- rbind(summary_cors_nkc_211_R, summary_temp)

combined_scapes_nkc_211_R[[i]][[j]] <- test_df
  
}
}

###
combined_scapes_nkc_202_R <- list()
summary_cors_nkc_202_R <- NULL

combined_scapes_nkc_202_R[[1]] <- list()
  
for (j in 1:200){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2021_R[[4]][[1]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2021_R[[4]][[1]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 0,
                              c = 2,
                              c_rep = 1,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 0, 2, 1, j))

summary_cors_nkc_202_R <- rbind(summary_cors_nkc_202_R, summary_temp)

combined_scapes_nkc_202_R[[1]][[j]] <- test_df
  
}

###
combined_scapes_nkc_212_R <- list()
summary_cors_nkc_212_R <- NULL

combined_scapes_nkc_212_R[[1]] <- list()
  
for (j in 1:200){ # for each landscape replicate
  
  scape_sp1 <- peaks_nkcs_2121_R[[4]][[1]][[j]][[1]]

# rename columns, so I can combine the landscapes of both species
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

scape_sp2 <- peaks_nkcs_2121_R[[4]][[1]][[j]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine sp1 and sp2
test_df <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(test_df)[c(9,10)] <- c("fitness_sp2", "rank_sp2")

summary_temp <- data.frame(n = 2,
                              k = 1,
                              c = 2,
                              c_rep = 1,
                              scape_rep = j,
                              corr = cor(test_df$rank_sp1, test_df$rank_sp2),
                           landscape_ID = interaction(2, 1, 2, 1, j))

summary_cors_nkc_212_R <- rbind(summary_cors_nkc_212_R, summary_temp)

combined_scapes_nkc_212_R[[1]][[j]] <- test_df
  
}


######
summary_cors_R <- rbind(summary_cors_nkc_211_R, summary_cors_nkc_201_R, summary_cors_nkc_202_R, summary_cors_nkc_212_R)

for (i in 1:nrow(peaks_total_ranked2_summarised_R[, ])){
  
  ID <- peaks_total_ranked2_summarised_R[i, "landscape_ID" ]
  
  if (ID %in% summary_cors_R$landscape_ID){
    
    peaks_total_ranked2_summarised_R[i, "corr_rank" ] <- summary_cors_R[as.character(summary_cors_R$landscape_ID) == ID, "corr"]
    
  }

}

eco_outcomes_R <- ggplot(peaks_total_ranked2_summarised_R,
   aes(x = corr_rank,
           y = rank_sp1)) +
  geom_hline(yintercept = 1,
             col = "grey") +
   geom_segment(aes(x = corr_rank, 
      y = rank_sp1, 
      xend = corr_rank, 
      yend = rank_sp2,
      alpha = rank_peaked/80),
      col = "grey40") +
  geom_point(col = "forestgreen",
             size = 2.5,
             aes(alpha = rank_peaked/80)) +
  geom_point(aes(x = corr_rank,
                 y = rank_sp2,
                 alpha = rank_peaked/80),
                 col = "forestgreen",
             size = 2.5) +
  facet_grid(c ~ k) +
  scale_y_continuous(labels = c("0", "2", "4", "6", "8", "10", "12", "14"), 
                     breaks = seq(1, 15, 2),
                   name = "Species fitness load",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                                       breaks = NULL, labels = NULL),
                   limits = c(-1,1)) +
  theme_bw() +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=24),
                      legend.position = "none",
                      strip.text.x = element_text(size = 15),
                      strip.text.y = element_text(size = 15, angle = 0),
                   panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) # font family to display the unicode character


ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "eco_outcomes_R.pdf",
       plot = eco_outcomes_R)

```

## Ruggedness - repeatability
```{r}
complete_ruggedness_df <- rbind(ruggedness_nkc_rep_sp_201_1_1, ruggedness_nkc_rep_sp_201_2_1, ruggedness_nkc_rep_sp_201_3_1,
                          ruggedness_nkc_rep_sp_201_4_1, ruggedness_nkc_rep_sp_211_1_1, ruggedness_nkc_rep_sp_211_2_1,
                          ruggedness_nkc_rep_sp_211_3_1, ruggedness_nkc_rep_sp_211_4_1, ruggedness_nkc_rep_sp_200_1_1,
                          ruggedness_nkc_rep_sp_210_1_1, ruggedness_nkc_rep_sp_212_1_1, ruggedness_nkc_rep_sp_202_1_1)

complete_ruggedness_df$rugg <- abs(complete_ruggedness_df$rugg)
complete_ruggedness_df$landscape_ID <- interaction(complete_ruggedness_df$n, complete_ruggedness_df$k, complete_ruggedness_df$c, complete_ruggedness_df$IM_rep, complete_ruggedness_df$scape_rep)

for (i in 1:nrow(peaks_total_ranked2_summarised[, ])){
  
  ID <- peaks_total_ranked2_summarised[i, "landscape_ID" ]
  
  if (ID %in% complete_ruggedness_df$landscape_ID){
    
    peaks_total_ranked2_summarised[i, "rugg" ] <- complete_ruggedness_df[as.character(complete_ruggedness_df$landscape_ID) == as.character(ID), "rugg"]
    
  }

}

rug_rep <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$n == 2 &
                                        peaks_total_ranked2_summarised$c > 0,],
       aes(x = rugg,
           y = rank_peaked/80)) +
  geom_point(col = "forestgreen",
             size = 2,
             alpha = 0.8) +
  facet_grid(c ~ k) +
   scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "log(roughness/slope)",
                     transform = "log10",
       sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                           breaks = NULL, labels = NULL)) +
  theme_bw() +
  theme(axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) +
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "rug_rep.pdf",
       plot = rug_rep)

```

## ruggedness - outcome
```{r}
rug_out <- ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = rugg,
           y = rank_sp1)) +
   geom_segment(aes(x = rugg, 
      y = rank_sp1, 
      xend = rugg, 
      yend = rank_sp2),
      col = "grey40",
      alpha = 0.8) +
  geom_point(col = "forestgreen",
             size = 2,
             aes(alpha = rank_peaked/80)) +
  geom_point(aes(x = rugg,
                 y = rank_sp2,
                 alpha = rank_peaked/80),
                 col = "forestgreen",
             size = 2) +
  facet_grid(c ~ k) +
   scale_y_continuous(labels = c("1", "3", "5", "7", "9", "11", "13", "15", "\u21BB"), # the unicode character is not essential and could be replaced by "cycle" - I just like this :-)
                     breaks = seq(1, 17, 2),
                   name = "Fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "log(roughness/slope)",
                     transform = "log10",
       sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                           breaks = NULL, labels = NULL)) +
  theme_bw() +
  theme(axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) +
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 30,
       height = 17,
       filename = "rug_out.pdf",
       plot = rug_out)

```


## Repeatability predicted by interaction type (fitness correlation)?
```{r}

eco_rep <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$rank_sp1 != 17 &
                                        !is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = corr_rank,
           y = rank_peaked/80)) +
  geom_point(col = "forestgreen") +
  facet_grid(c ~ k) +
  xlim(c(-1,1)) +
  scale_y_continuous(limits = c(0,1),
                   name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = substitute(paste("intergenomic epistasis, ", italic(C))), 
                                       breaks = NULL, labels = NULL)) +
  scale_x_continuous(name = "rank correlation(F, P)",
       sec.axis = sec_axis(~ . , name = substitute(paste("intragenomic epistasis, ", italic(K))), 
                           breaks = NULL, labels = NULL)) +
  xlab("rank correlation(F, P)") +
  theme_bw() +
  theme(axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

ggsave(path = "../Figures/",
       device = cairo_pdf, # to save pdf with unicode
       units = c("cm"),
       width = 26,
       height = 15,
       filename = "eco_rep_N2.pdf",
       plot = eco_rep)
```


# 4.) Additional figures
## Fitness landscape example; "classic" version
```{r}
example_scape_fig <- visualise_system(peaks_nkcs_2011[[4]][[1]][[13]], # I recode the alleles into as and bs in Adobe Illustrator O:-)
                 n = 2,
                 c = 1,
                 s = 1,
                 s_tot = 2) +
  theme(axis.text.x.bottom = element_text(size=16),
                        axis.text.y = element_text(size=15),
                        axis.title = element_text(size=25 ),
        strip.text.x = element_text(size=25))

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 35,
       height = 14,
       filename = "scapes_NKC_201_1_13.pdf",
       plot = example_scape_fig)
```

```{r}
# recoding fitness landscapes; 
## in my model the alleles are encoded as 1 and 2, but I would different alleles for the two species to better distinguish them (differences in metagenotypes should be easier to spot this way)

scape_sp1 <- peaks_nkcs_2011[[4]][[1]][[13]][[1]] # take desired landscape replicate for species 1 = "focal species"

# recode alleles for focal species 
scape_sp1[scape_sp1$F.1 == 1, "F.1"] <- "a" 
scape_sp1[scape_sp1$F.1 == 2, "F.1"] <- "A"
scape_sp1[scape_sp1$F.2 == 1, "F.2"] <- "a"
scape_sp1[scape_sp1$F.2 == 2, "F.2"] <- "A"

# recode alleles for partner species
scape_sp1[scape_sp1$P.1 == 1, "P.1"] <- "b"
scape_sp1[scape_sp1$P.1 == 2, "P.1"] <- "B"
scape_sp1[scape_sp1$P.2 == 1, "P.2"] <- "b"
scape_sp1[scape_sp1$P.2 == 2, "P.2"] <- "B"

# rename columns, so I can combine the landscapes of both species next
colnames(scape_sp1)[c(7,8)] <- c("fitness_sp1", "rank_sp1")

# take the corresponding fitness landscape of species 2 in the chosen species pair
scape_sp2 <- peaks_nkcs_2011[[4]][[1]][[13]][[2]]
scape_sp2 <- scape_sp2[with(scape_sp2, order(P.1, P.2, F.1, F.2)), ] # reordering the loci, so they are in the same order as for sp 1

# combine landscaps of sp1 and sp2
scapes_combined <- cbind(scape_sp1, scape_sp2[,c(7,8)])
colnames(scapes_combined)[c(9,10)] <- c("fitness_sp2", "rank_sp2") # adjust column names

# get the metagenotypes, so I can plot them; this is just for text in the plot
for (i in 1:16){
  
  scapes_combined$seq[i] <- paste(paste(scapes_combined[i, c("F.1", "F.2")], collapse = ""), "-", c(paste(scapes_combined[i, c("P.1", "P.2")], collapse = "")))
  
}

scapes_combined$background <- paste0(scapes_combined$P.1, scapes_combined$P.2) # genotype of sp2
scapes_combined$gen <- paste0(scapes_combined$F.1, scapes_combined$F.2) # genotype of sp1

# now I use my function from the NKC(S) code file to infer which metagenotypes are one-mutation step neighbours
visual_test_df <- visual_landscape(scapes_combined,
                 n = 2,
                  c = 1,
                 s = 1) # this is how I get the transitions between metagenotypes

parallel_scape <- ggplot(visual_test_df,
       aes(x = mutations,
           y = fitness)) +
  geom_line(data = visual_test_df,
            aes(group = group,
                linetype = mut),
            color="grey70",
            linewidth = 1) +
  geom_label(label = visual_test_df$seq,
             aes(col = background),
             linewidth = 0.6, # thickness of label border in mm
             size = 4.5, # size of label in mm
             fontface = "bold" # bold font
             ) +
  scale_linetype_manual(breaks = c("intra", "inter"),
                        values = c("solid", "dashed"))+
  xlab("Hamming distance from reference metagenotype") +
  ylab("Fitness") +
    facet_wrap(~species,
               labeller = labeller(species = 
    c("1" = "Focal species",
      "2" = "Partner species"))) +
  theme_bw() +
  theme(legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(linewidth = 0.8, linetype = 2),
        panel.grid.minor.x = element_blank(),
        text = element_text(size = 15),
        axis.text = element_text(size = 13))


```

## Network representation of adaptive walks
```{r}
# Making an adjacency matrix (which metagenotypes can mutate into each other?)
x <- as.data.frame(gtools::permutations(2, 4, c(1:2), repeats = TRUE))
x$ID <- 1:16

adj_mat <- matrix(16, 16, data = rep(0, 16^2))

for (i in 1:16) {
  
  adj_mat[i,findNeighbours(x, i, 4)$ID] <- 1
  
}


# translating my adaptive walks into something I can use here
# I need to extract the transitions from my adaptive walks -> format: from - to - in how many replicates of walk

walks_dfs <- NULL
for (i in 1:48){
  
 temp_df <- peaks_nkcs_2011[[5]][[1]][[26]][[3]][[i]] # true walk
 
 IDs <- NULL
 
 for (j in 0:max(temp_df[[1]][,"step"])) {
   
    metagenotype <- temp_df[[1]][temp_df[[1]]$step == j, c("F.1", "F.2", "P.1", "P.2")]
 ID_temp <- x[rowSums(mapply(`==`, x[, c("V1", "V2", "V3", "V4")], metagenotype)) == 4, "ID"] # extract the ID of the metagenotype that matches my adjacency matrix IDs
 
 IDs <- c(IDs, ID_temp)
   
 }
 
 from_IDs <- IDs[1:(length(IDs)-1)]
 to_IDs <- IDs[2:length(IDs)]
 
 temp_df <- data.frame(from = from_IDs,
                       to = to_IDs,
                      step = temp_df[[1]][c(2:nrow(temp_df[[1]])),"step"],
                       focal = temp_df[[1]][c(2:nrow(temp_df[[1]])),"focal"],
                       walk = i)
 
 walks_dfs <- rbind(walks_dfs, temp_df)
  
}

walks_dfs_summed <- as.data.frame(walks_dfs |> 
                            dplyr::group_by(from, to, focal, walk) |>
                            dplyr::summarise(step_count = n()))

walks_dfs_summed2 <- as.data.frame(walks_dfs_summed |> 
                            dplyr::group_by(from, to, focal) |>
                            dplyr::summarise(rep_count = n())) # this gives me in how many replicates certain steps were taken from x to y given a certain focal species


g <- igraph::graph_from_data_frame(walks_dfs_summed2, 
                           directed = TRUE)

# add metadata to the nodes in the network (here "averaged per node")
igraph::V(g)$count <- ave(walks_dfs_summed2$rep_count, walks_dfs_summed2$from, FUN = max)[match(V(g)$name, walks_dfs_summed2$from)]

ranks_sp1 <- peaks_nkcs_2011[[4]][[1]][[26]][[1]]$rank
test_df <- peaks_nkcs_2011[[4]][[1]][[26]][[2]]
ranks_sp2 <- test_df[order(test_df$P.1, test_df$P.2, test_df$F.1, test_df$F.2), "rank"]

igraph::V(g)$rank_sp1 <- ranks_sp1
igraph::V(g)$rank_sp2 <- ranks_sp2


graph <- ggraph::ggraph(g,
               layout = "stress") +
  geom_edge_fan(aes(linetype = as.factor(focal)), # different edge color for the different steps based on focal species
                 end_cap = circle(5, "mm"), # buffer between node and arrow
                colour = "grey40") + 
  geom_edge_fan(arrow = arrow(type = "closed", # make arrow heads separately so they all have solid outlines
                              angle = 20, # "width" of arrow tip
                              length = unit(4, "mm")), # length of arrow tip
                edge_width = 0,
                 end_cap = circle(5, "mm"), # buffer between node and arrow
                colour = "grey40") + 
  geom_edge_loop(aes(linetype = as.factor(focal),
                     strength = (3*focal/4)), # to make non-overlapping loops
                 end_cap = circle(4, "mm"),
                colour = "grey40") +
  geom_edge_loop(aes(strength = (3*focal/4)), # make arrow heads separately so they all have solid outlines
                 arrow = arrow(type = "closed",
                               angle = 20,
                 length = unit(4, "mm")),
                 edge_width = 0,
                 end_cap = circle(4, "mm"),
                colour = "grey40") +
  geom_node_arc_bar(aes(x0 = x,
                        y0 = y,
                        r0 = 0, 
                        r = count/300 + 0.1,
                       start = pi, 
                       end = 2*pi,
                       fill = rank_sp1),
                       colour = "white") + # left semicircle
  geom_node_arc_bar(aes(x0 = x,
                        y0 = y,
                        r0 = 0, 
                        r = count/300 + 0.1, 
                        start = 0, 
                        end = pi,
                       fill = rank_sp2),
                       colour = "white") + # right semicircle
  #geom_node_text(aes(label = name)) +                   # "name" is automatically generated from the node IDs in the edges; then adjust r0 o read text
  scale_size(range = c(5, 15),
             guide = "none") +
  scale_edge_linetype_manual(values = c("solid", "dashed"),
                             name = "focal species") +
  scale_fill_gradient2(name = "fitness rank",
                         low = "#5d36f7",
                         high = "#f9db45",
                         mid = "#f274f0",
                         midpoint = mean(ranks_sp1), # to adjust midpoint for landscapes with more or less peaks
                         guide = "colourbar",
                         aesthetics = "fill",
                         transform = "reverse",
                       breaks = c(1, 4, 8, 12, 16)) +
  theme_void() +
  guides(edge_linetype = guide_legend(position = "top"))


# ggsave(path = "../Figures/",
#        device = "pdf",
#        units = c("cm"),
#        width = 15,
#        height = 12,
#        filename = "graph_NKC_201_4_17.pdf",
#        plot = graph)


```

## Community patterns
```{r}

community_rep <- ggplot(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$n == 2 &
                                                         peaks_total_ranked2_summarised$rank_sp1 != 17,], 
        aes(y = rank_peaked/80,
            x = (rank_sp1 + rank_sp2)/2,
            group = (rank_sp1 + rank_sp2)/2)) +
  geom_violin(col = "grey45") +
  geom_jitter(col = "forestgreen",
              size = 2.5,
              height = 0.01,
              alpha = 0.3) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
     theme_bw() +
  facet_grid(c ~ k) +
  scale_x_continuous(labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "\u21BB"), # the unicode character is not essential and could be replace by "cycle" - I just like this :-)
                     breaks = c(1:17),
                   name = "Community fitness rank at the end of adaptive walk",
                   sec.axis = sec_axis(~ . , name = "intragenomic epistasis, K", breaks = NULL, labels = NULL)) +
  scale_y_continuous(name = "Proportion of adaptive walks/landscape",
                   sec.axis = sec_axis(~ . , name = "intergenomic epistasis, C", breaks = NULL, labels = NULL)) +
  theme(axis.title.y.right = element_text(angle = 90, vjust = 0.5),
        axis.title.y.left = element_markdown(),
        text = element_text(family = "Arial Unicode MS")) + # font family to display the unicode character
  fig_theme

for (ID in unique(summary_cycles$scape_ID)){
  
  if (ID %in% summary_cycles$scape_ID) {
    
    summary_cycles[summary_cycles$scape_ID == ID, "corr_rank"] <- unique(peaks_total_ranked2_summarised[peaks_total_ranked2_summarised$landscape_ID == ID, "corr_rank"])
    
  }
  
  
}

```

## Visualising cycles
```{r}
# walk example 
cycle_walk <- peaks_nkcs_2011[[5]][[4]][[  ]][[1]][[1]]

cycle_df <- data.frame(rank_sp1 = cycle_walk[[1]][,"rank"],
                         rank_sp2 = cycle_walk[[2]][,"rank"],
                         step = cycle_walk[[1]][,"step"])

cycle <- ggplot(cycle_df,
       aes(x = rank_sp1,
           y = rank_sp2)) + 
  geom_point(size = 3,
             col = "forestgreen") +
  geom_arrow_chain() +  geom_arrow_chain() +
  scale_x_continuous(breaks = c(1:16),
                     limits = c(1,16),
                     name = "Fitness rank focal species") +
  scale_y_continuous(breaks = c(1:16),
                     limits = c(1,16),
                     name = "Fitness rank partner species") +
  theme_classic() +
  fig_theme

ggsave(path = "../Figures/",
       device = "pdf",
       units = c("cm"),
       width = 15,
       height = 13,
       filename = "cycle_NKC_201_4_17.pdf",
       plot = cycle)

```


# cycle summary stats
```{r}

# steps in adaptive walk
ggplot(peaks_total[peaks_total$walking == "random" &
                     peaks_total$species == 1,], # to reduce redundancy - only one point per simulation
       aes(x = interaction(k, c, n),
           y = step)) +
  geom_jitter(col = "forestgreen",
              alpha = 0.6,
              size = 2.5) +
  scale_x_discrete(labels=c("0.0.2" = "2-0-0", 
                            "1.0.2" = "2-1-0",
                            "0.1.2" = "2-0-1",
                            "1.1.2" = "2-1-1",
                            "0.2.2" = "2-0-2",
                            "1.2.2" = "2-1-2",
                            "1.0.4" = "4-1-0",
                            "2.0.4" = "4-2-0",
                            "3.0.4" = "4-3-0")) +
  xlab("N-K-C") +
  ylab("Steps in adaptive walk") +
  theme_bw() +
  fig_theme


walks_steps <- ggplot(peaks_total[peaks_total$species == 1,], # to reduce redundancy - only one point per simulation
       aes(x = interaction(k, c, n),
           y = step)) +
  geom_jitter(aes(col = walking),
              alpha = 0.5,
              size = 2.5) +
  scale_color_manual(values=c("grey60", "grey", "forestgreen")) +
  facet_grid(walking~.,
             labeller = labeller(walking = 
    c("greedy" = "greedy",
      "prop" = "true",
      "random" = "random"))) +
  scale_x_discrete(labels=c("0.0.2" = "2-0-0", 
                            "1.0.2" = "2-1-0",
                            "0.1.2" = "2-0-1",
                            "1.1.2" = "2-1-1",
                            "0.2.2" = "2-0-2",
                            "1.2.2" = "2-1-2",
                            "1.0.4" = "4-1-0",
                            "2.0.4" = "4-2-0",
                            "3.0.4" = "4-3-0")) +
  xlab("N-K-C") +
  ylab("Steps in adaptive walk") +
  theme_bw() +
  theme(strip.text.y.right = element_text(angle = 90)) +
  fig_theme

ggsave(path = "../Figures/",
       units = c("cm"),
       width = 19,
       height = 17,
       filename = "walks_steps.pdf",
       plot = walks_steps)

# size of cycles
cycle_size <- ggplot(cycles_df,
       aes(y = nb_in_cycle_sp1,
           x = interaction(k,c,n),
           group = interaction(k,c,n))) +
  geom_violin() +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  scale_y_continuous(name = "Meteganotypes in cycle",
                      limits = c(0,16),
                      breaks = seq(0,16,2)) +
   scale_x_discrete(labels=c("0.0.2" = "2-0-0", 
                            "1.0.2" = "2-1-0",
                            "0.1.2" = "2-0-1",
                            "1.1.2" = "2-1-1",
                            "0.2.2" = "2-0-2",
                            "1.2.2" = "2-1-2",
                            "1.0.4" = "4-1-0",
                            "2.0.4" = "4-2-0",
                            "3.0.4" = "4-3-0")) +
  xlab("N-K-C") +
  theme_bw() +
  fig_theme

ggsave(path = "../Figures/",
       units = c("cm"),
       width = 19,
       height = 12,
       filename = "cycle_size.pdf",
       plot = cycle_size)




library(reshape2)
df <- melt(summary_cycles[, c("n", "k", "c", "cycle_ID", "scape_ID", "high_rank_sp1", "high_rank_sp2", "low_rank_sp1", "low_rank_sp2")],  
           id.vars = c("n", "k", "c", "cycle_ID", "scape_ID"), 
           variable.name = 'ranks')

ggplot(df,
       aes(x = interaction(n,k,c),
           y = value,
           group = interaction(n,k,c,ranks))) +
  geom_violin(position = position_dodge(0.7),
              aes(col = ranks)) +
  geom_jitter(aes(col = ranks),
              position = position_jitterdodge(0.3)) +
  theme_bw() +
  scale_color_manual(values=c("slateblue", "slateblue", "orange", "orange")) +
  scale_y_continuous(name = "fitness rank",
                     limits = c(1,16),
                     breaks = seq(1,16,2)) +
  xlab("N-K-C") +
  fig_theme



ggplot(summary_cycles,
       aes(x = interaction(n,k,c),
           y = mean_rank_sp1)) +
  geom_violin() +
  geom_jitter(col = "forestgreen",
              size = 2,
              alpha = 0.6) +
  stat_summary(fun = mean,
               geom = "crossbar", # adds the mean proportion for each rank/landscape
               linewidth = 0.4,
               col = "black") +
  stat_summary(fun = median,
               geom = "point", # adds the median proportion for each rank/landscape
               shape = 18,
               size = 3,
               col = "black") +
  theme_bw() +
  xlab("N-K-C") +
  scale_y_continuous(name = "mean fitness rank",
                     limits = c(1,16),
                     breaks = seq(1,16,2)) +
  xlab("N-K-C") +
  fig_theme

```



```{r}

ggplot(peaks_total_ranked2_summarised[!is.na(peaks_total_ranked2_summarised$corr_rank),],
       aes(x = rugg,
           y = corr_rank)) +
  geom_point() +
  scale_x_continuous(name = "log(roughness/slope)",
                     transform = "log10",
       sec.axis = sec_axis(~ . , name = "K", breaks = NULL, labels = NULL)) +
  theme_classic()

```